### 2023-04-11 analyses.Rmd
- initalize repo

---
title: "Analyses"
bibliography: 
  - [bibliography/references.bib]
output: 
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
---

```{r setup, include=F}
knitr::opts_chunk$set(
  cache = TRUE, 
  warning = FALSE, 
  echo = TRUE, 
  error = FALSE, 
  message = FALSE, 
  prompt = FALSE, 
  tidy = TRUE, 
  fig.height = 6, 
  fig.width = 8
  )

options(
  digits = 3, 
  width = 120
  )
```

In what follows, you can find the analyses for the results reported in the paper. To see the underlying code, click on the button "code".

# Setup
## Packages

```{r results='hide', cache=F}
# install github packages
# devtools::install_github("tdienlin/td@v.0.0.2.3")  # uncomment to install
# devtools::install_github("yrosseel/lavaan")

# define packages
packages <- 
  c(
    "brms", 
    "cowplot", 
    "devtools", 
    "english", 
    "faoutlier", 
    "GGally", 
    "gganimate",
    "kableExtra", 
    "knitr", 
    "lavaan", 
    "magrittr",
    "marginaleffects",
    "MVN", 
    # "psych", 
    "pwr", 
    "quanteda", 
    "semTools", 
    "tidyverse", 
    "td"
    )

# load packages
lapply(
  packages, 
  library, 
  character.only = TRUE, 
  quietly = TRUE
  )

# If not wanting to compute all transformations etc., simply load workspace
# load("data/workspace.RData")
```

## Custom Functions

```{r}
# define function to silence result output
# needed for brms
hush <- 
  function(
    code
    ){
    sink("/dev/null") # use /dev/null in UNIX
    tmp = code
    sink()
    return(tmp)
    }

# plot distributions of items
plot_dist <-
  function(
    item,
    n_rows = 1
    ) {
    ggplot(
      gather(
        select(
          d, 
          starts_with(
            item
            )
          )
        ), 
      mapping = aes(
        x = value
        )
      ) +
      geom_bar() +
      facet_wrap(
        ~key, 
        nrow = n_rows
        ) + 
      theme_bw()
  }

get_desc <- 
  function(
    item,
    name
  ) {
    desc <- 
      select(
        d, 
        starts_with(
          item
          )
        ) %>% 
      apply(
        1, 
        mean, 
        na.rm = TRUE
        ) %>% 
      as.data.frame() %>% 
      summarise(
        m = mean(., na.rm = TRUE), 
        sd = sd(., na.rm = TRUE)
        )
    assign(
      paste0(
        "des_",
        name
      ),
      desc,
      envir = .GlobalEnv
    )
  }

# Function to display diagnostics of fitted hurdle models
model_diagnostics <- 
  function(
    model
  ){
  plot_grid(
    pp_check(
      model,
      type = "dens_overlay",
      nsamples = 100
    ),
    pp_check(
      model,
      type = "loo_pit_qq",
      nsamples = 100
    ),
    pp_check(
      model,
      type = "stat",
      stat = "median",
      nsamples = 100
    ),
    pp_check(
      model,
      type = "stat",
      stat = "mean",
      nsamples = 100
    ),
    labels = c("Density overlay", "LOO-PIT QQ", "Predicted medians", "Predicted means"),
    ncol = 2,
    label_size = 8,
    hjust = 0,
    vjust = 0,
    label_x = 0,
    label_y = 0.93
  )
  }

# wrapper function that runs relevant analyses for hurdle models
run_hurdles <- 
  function(
    object,
    name,
    outcome,
    predictor,
    x_lab,
    y_lab,
    plot = FALSE,
    ...
    ){

    # define define general model
    formula_mdl <- 
      formula(
        paste0(
          outcome,
          " ~ 1 + age + male + edu +",
          predictor
        )
    )

    # define hurdle model
    formula_hrdl <- 
      formula(
        paste0(
          "hu ~ 1 + age + male + edu +",
          predictor
        )
    )

    # fit model
    fit <- 
      hush(
        brm(
          bf(
            formula_mdl, 
            formula_hrdl
            ), 
          data = object, 
          family = hurdle_gamma(),
          silent = TRUE,
          refresh = 0
          )
      )

    # export fit
    assign(
      paste0(
        "fit_",
        name),
      fit,
      envir = .GlobalEnv
    )

    # plot model
    if(
      isTRUE(plot
             )) {
      plot(fit, ask = FALSE)
      }

    # run diagnostics
    fit_diagnostics <- 
      model_diagnostics(fit)
    plot(fit_diagnostics)

    # print summary
    fit_summary <- 
      summary(fit)
    print(fit_summary)

    # calculate slopes
    slopes <-
      cbind(
        Outcome = outcome,
        avg_slopes(fit)
      )

    # print slopes
    cat("\nResults of marginal effects:\n")
    print(slopes)

    # export as object to environment
    assign(
      paste0(
        "slopes_",
        name
        ),
      slopes,
      envir = .GlobalEnv
    )

    # make figure
    fig_res <- 
      conditional_effects(
        fit
        , ask = FALSE
      )

    # make figure
    fig <- 
      plot(
        fig_res,
        plot = FALSE
      )[[predictor]] +
      labs(
        x = x_lab,
        y = y_lab
        )

    # plot figure
    print(fig)

    # export as object to environment
    assign(
      paste0(
        "fig_",
        name
      ),
      fig,
      envir = .GlobalEnv
    )
}
```

## Data-Wrangling

```{r results='hide', cache=F}
# load data
# please note that in a prior step several different data sets were merged using information such as case_taken or IP-addresses. To guarantee the privacy of the participants, these data were deleted after merging.
d_raw <- read_csv("data/data_raw.csv")

# recode variables
d <- 
  d_raw %>% 
  dplyr::rename(
    "male" = "SD01", 
    "age" = "SD02_01", 
    "state" = "SD03", 
    "edu_fac" = "SD04",
    "TR02_01" = "TR01_01",
    "TR02_02" = "TR01_05",
    "TR02_03" = "TR01_09",
    "TR01_01" = "TR01_02",
    "TR01_02" = "TR01_03",
    "TR01_03" = "TR01_04",
    "TR01_04" = "TR01_06",
    "TR01_05" = "TR01_07",
    "TR01_06" = "TR01_08",
    "TR01_07" = "TR01_10",
    "TR01_08" = "TR01_11",
    "TR01_09" = "TR01_12"
    ) %>% 
  mutate(

    #general
    version = factor(
      VE01_01, 
      labels = c(
        "Control", 
        "Like", 
        "Like & Dislike"
        )
      ),
    version_lkdslk = factor(
      version, 
      levels = c(
        "Like & Dislike", 
        "Like", 
        "Control"
        )
      ),
    version_no = recode(
      version, 
      "Control" = 1, 
      "Like" = 2, 
      "Like & Dislike" = 3
      ),
    male = replace_na(
      male, 
      "[3]") %>% 
      dplyr::recode(
        "männlich [1]" = 1, 
        "weiblich [2]" = 0
        ),
    age_grp = cut(
      age, 
      breaks = c(0, 29, 39, 49, 59, 100), 
      labels = c("<30", "30-39", "40-49", "50-59", ">59")
      ),

    # contrasts
    like = recode(
      version, 
      "Control" = 0, 
      "Like" = 1, 
      "Like & Dislike" = 0
      ),
    likedislike = recode(
      version, 
      "Control" = 0, 
      "Like" = 0, 
      "Like & Dislike" = 1
      ),
    control = recode(
      version, 
      "Control" = 1, 
      "Like" = 0, 
      "Like & Dislike" = 0
      ),

    # recode
    edu = recode(
      edu_fac, 
      "Hauptschulabschluss/Volksschulabschluss" = 1, 
      "Noch Schüler" = 1,
      "Realschulabschluss (Mittlere Reife)" = 1,
      "Abschluss Polytechnische Oberschule 10. Klasse (vor 1965: 8. Klasse)" = 1,
      "Anderer Schulabschluss:" = 1,
      "Fachhochschulreife (Abschluss einer Fachoberschule)" = 2,
      "Abitur, allgemeine oder fachgebundene Hochschulreife (Gymnasium bzw. EOS)" = 2,
                 "Hochschulabschluss" = 3),
    PC01_03 = 8 - PC01_03, 
    SE01_05 = 8 - SE01_05, 
    SE01_06 = 8 - SE01_06,

    # behavioral data
    words = replace_na(
      words, 
      0
      ),
    self_dis = words + (reactions * 2),
    time_read_MIN = time_read / 60,
    time_sum_min_t2 = TIME_SUM_t2 / 60,

    # take logarithm
    words_log = log1p(words)
  )

# variable labels
var_names <- c(
  "Privacy concerns", 
  "General gratifications", 
  "Specific gratifications",
  "Privacy deliberation", 
  "Self-efficacy", 
  "General trust", 
  "Specific trust",
  "Words log"
  )

var_names_breaks <- c(
  "Privacy\nconcerns", 
  "General\ngratifications", 
  "Specific\ngratifications",
  "Privacy\ndeliberation", 
  "Self-\nefficacy", 
  "General\ntrust", 
  "Specific\ntrust",
  "Words (log)"
  )

# Extract sample characteristics and descriptives.
# sample descriptives t1
n_t1 <- nrow(d)
age_t1_m <- mean(d$age, na.rm = TRUE)
male_t1_m <- mean(d$male, na.rm = TRUE)
college_t1_m <- table(d$edu)[3] / n_t1

# sample descriptives t2
# participants
n_t2 <- 
  filter(
    d, 
    !is.na(
      id_survey_t2
      )
    ) %>% 
  nrow()

# age
age_t2_m <- 
  filter(
    d, 
    !is.na(
      id_survey_t2
      )
    ) %>% 
  select(
    age
    ) %>% 
  mean()

# gender
male_t2_m <- 
  filter(
    d, 
    !is.na(
      id_survey_t2
      )
    ) %>% 
  select(
    male
    ) %>% 
  mean(
    na.rm = TRUE
    )

# education
college_t2_m <- 
  filter(
    d, 
    !is.na(
      id_survey_t2
      )
    ) %>% 
  select(
    edu
    ) %>% 
  table() %>% 
  .[3] / n_t2

# descriptives users
n_users <- 
  filter(
    d, 
    !is.na(
      post_count
      )
    ) %>% 
  nrow()

# characteristics of posts
n_comments <- 
  sum(
    d$post_count, 
    na.rm = TRUE
    )

n_words <- 
  sum(
    d$words, 
    na.rm = TRUE
    )

n_time <- 
  sum(
    d$time_read_MIN, 
    na.rm = TRUE
    )

n_posts <- 
  sum(
    d$post_count, 
    na.rm = TRUE
    )

# filter unmatched cases, use only completes
d <- 
  filter(
    d, 
    !is.na(
      post_count
      ) & !is.na(
        id_survey_t2
        )
    )

n_matched <- nrow(d)

# save data file with all participants to compare results
d_all <- d
```

# Filter Participants

We filtered participants who answered the questionnaire in less than three minutes, which we considered to be unreasonably fast.

```{r cache=F}
# filter speeders
time_crit <- 3 # minimum time on survey

# count number of speeders
n_speeding <- 
  nrow(
    filter(
      d, 
      time_sum_min_t2 < time_crit
      )
    )

# Deletion of fast respondents
d <- 
  filter(
    d, 
    time_sum_min_t2 >= time_crit
    )
```

We inspected the data manually for cases with obvious response patterns. The following cases show extreme response patterns (alongside fast response times), and were hence removed.

```{r cache=F}
# identify response patterns
resp_pattern <- c(
  "ANIEVLK9F2SW", 
  "BN4MAOWZO7W2"  # clear response pattern
  )

n_resp_pattern <- 
  length(
    resp_pattern
    )

# infl_cases_tokens <- infl_cases_tokens[!infl_cases_tokens %in% resp_pattern]

d %>% 
  filter(
    case_token %in% resp_pattern
    ) %>% 
  select(
    case_token, 
    GR01_01:SE01_06, 
    topics_entered:reactions, 
    -SO01_01, 
    TIME_SUM_t1, 
    TIME_SUM_t2
    ) %>% 
  kable() %>% 
  kable_styling("striped") %>% 
  scroll_box(width = "100%")

d %<>% 
  filter(
    !case_token %in% resp_pattern
    )

# sample descriptives final data set
n_final <- nrow(d)
age_final_m <- mean(d$age)
male_final_m <- mean(d$male, na.rm = TRUE)
college_final_m <- table(d$edu)[[3]] / n_final
```

# Measures
## Privacy concerns
### Items

Using the participation platform I had ...

 1. ... concerns about what happens to my data.
 2. ... concerns about disclosing information about myself.
 3. ... no concerns. (reversed)
 4. ... concerns that others could discover my real identity (i.e. my last and first name).
 5. ... concerns that information about myself could fall into wrong hands.
 6. ... concerns that others could discover what my political views are.
 7. ... concerns about my privacy.

### Distributions

```{r fig.height = 3}
# plot distribution
plot_dist(
  item = "PC01"
)

# extract results
get_desc(
  item = "PC01",
  name = "pricon"
)
```

### CFA

```{r}
name <- "pricon"
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_03 + PC01_04 + PC01_05 + PC01_06 + PC01_07
"
fit <- 
  lavaan::sem(
    model = model, 
    data = d, 
    estimator = "MLR", 
    missing = "ML"
    )
```

Model fit:

```{r}
facval <- 
  fit_tab(
    fit, 
    reliability = TRUE, 
    scaled = TRUE
    ) %T>%
  print()

# export factor validity
assign(
  paste0(
    name, 
    "_facval"
    ), 
  facval
  )
```

Factor loadings:

```{r}
inspect(
  fit,
  what = "std") %$% 
    lambda
```

Shows that PC01_03 doesn't load well. As it's an inverted item that's not surprising. Also from a theoretic perspective it's suboptimal, because it doesn't explicitly focus on privacy, but just concerns in general. Will be deleted.

### CFA 2

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
"
fit <-
  lavaan::sem(
    model = model,
    data = d,
    estimator = "MLR",
    missing = "ML"
    )
```

Model fit:

```{r}
facval <- 
  fit_tab(
    fit, 
    reliability = TRUE, 
    scaled = TRUE
    ) %T>% 
  print()

assign(
  paste0(
    name, 
    "_facval"
    ), 
  facval
  )
```

Factor loadings:

```{r}
inspect(
  fit,
  what = "std"
  ) %$% 
  lambda
```

Updated version shows good fit.

## Gratifications general
### Items

Using the participation platform ...

 1.	... had many benefits for me.
 2.	... has paid off for me.
 3.	... was worthwhile.
 4.	... was fun.
 5.	... has brought me further regarding content.

### Distributions

```{r fig.height = 3}
plot_dist(
  item = "GR02"
)

get_desc(
  item = "GR02",
  name = "gratsgen"
)
```

### CFA

```{r}
name <- "gratsgen"
model <- "
  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
"
fit <- 
  lavaan::sem(
    model = model, 
    data = d, 
    estimator = "MLR", 
    missing = "ML"
    )
```

Model fit:

```{r}
facval <- 
  fit_tab(
    fit, 
    reliability = TRUE, 
    scaled = TRUE
    ) %T>%
  print()

assign(
  paste0(
    name, 
    "_facval"
    ), 
  facval
  )
```

Factor loadings:

```{r}
inspect(
  fit,
  what = "std"
  ) %$% 
  lambda
```

## Gratifications specific
### Items

Using the participation platform it has been possible for me ...

_Information_

 1.	... to learn things I would not otherwise have noticed.
 2.	... to hear the opinion of others.
 3.	... to learn how other people tick.

_Relevance_

 4.	... to react to a subject that is very dear to me.
 5.	... to react to a subject that is important to me.
 6.	... to react to a subject that I am affected by.

_Political participation_

 7.	... to engage politically.
 8.	... to discuss political issues.
 9.	... to pursue my political interest.

_Idealism_

 10. ... to try to improve society.
 11. ... to advocate to something meaningful.
 12. ... to serve a good purpose.

_Extrinsic benefits_

 13. ... to do the responsible persons a favor.
 14. ... to soothe my guilty consciences.
 15. ... to fulfil my civic duty.

### Distributions

```{r}
plot_dist(
  item = "GR01",
  n_rows = 2
)

get_desc(
  item = "GR01",
  name = "gratsspec"
)
```

### CFA

```{r}
name <- "gratsspec"
model <- "
  grats_inf =~ GR01_01 + GR01_02 + GR01_03 
  grats_rel =~ GR01_04 + GR01_05 + GR01_06 
  grats_par =~ GR01_07 + GR01_08 + GR01_09
  grats_ide =~ GR01_10 + GR01_11 + GR01_12 
  grats_ext =~ GR01_13 + GR01_14 + GR01_15
  grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
"
fit <- lavaan::sem(
  model = model, 
  data = d, 
  estimator = "MLR", 
  missing = "ML"
  )
```

Model fit:

```{r}
facval <- 
  fit_tab(
    fit, 
    reliability = TRUE, 
    scaled = TRUE
    ) %T>%
  print()

assign(
  paste0(
    name, 
    "_facval"
    ), 
  facval
  )
```

Factor loadings:

```{r}
inspect(
  fit,
  what = "std"
  ) %$% 
  lambda
```

## Privacy deliberation
### Items

Using the participation platform ...

 1. ... I have considered whether I could be disadvantaged by writing a comment.
 2. ... I have considered whether I could be advantaged by writing a comment.
 3. ... I have weighed up the advantages and disadvantages of writing a comment.
 4. ... I have thought about consequences of a possible comment.
 5. ... I have considered whether I should write a comment or not.

### Distributions

```{r fig.height = 3}
plot_dist(
  item = "PD01"
)

get_desc(
  item = "PD01",
  name = "pridel"
)
```

### CFA

```{r}
name <- "pridel"
model <- "
  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
"
fit <- lavaan::sem(
  model = model, 
  data = d, 
  estimator = "MLR", 
  missing = "ML"
  )
```

Model fit:

```{r}
facval <- 
  fit_tab(
    fit, 
    reliability = TRUE, 
    scaled = TRUE
    ) %T>%
  print()

assign(
  paste0(
    name, 
    "_facval"), 
  facval
  )
```

Factor loadings:

```{r}
inspect(
  fit,
  what = "std"
  ) %$%
  lambda
```

## Trust general
### Items

&nbsp;&nbsp;&nbsp;1. The other users seemed trustworthy.  
&nbsp;&nbsp;&nbsp;2. The operators of the participation platform seemed trustworthy.  
&nbsp;&nbsp;&nbsp;3. The website seemed trustworthy.

### Distributions

```{r fig.height = 3}
plot_dist(
  item = "TR02"
)
get_desc(
  item = "TR02",
  name = "trustgen"
)
```

### CFA

```{r}
name <- "trustgen"
model <- "
trust =~ TR02_01 + a*TR02_02 + a*TR02_03
"
fit <- 
  lavaan::sem(
    model = model, 
    data = d, 
    estimator = "MLR", 
    missing = "ML"
    )
```

Model fit:

```{r}
facval <- 
  fit_tab(
    fit, 
    reliability = TRUE, 
    scaled = TRUE
    ) %T>%
  print()

assign(
  paste0(
    name, 
    "_facval"
    ), 
  facval
  )
```

Factor loadings:

```{r}
inspect(
  fit,
  what = "std"
  ) %$%
  lambda
```

Note that we constrained Items 5 and Item 9 to be equal. Explanation: First, they are theoretically related. Second, not constraining would yield to just-identified model, for which model fit cannot be interpreted meaningfully.

## Trust specific
### Items

_Community_

 1.	The comments of other users were useful.
 2.	The other users had good intentions.
 3.	I could rely on the statements of other users.

_Provider_

 4.	The operators of the participation platform have done a good job.
 5.	It was important to the operators that the users are satisfied with the participation platform.
 6.	I could rely on the statements of the operators of the participation platform.

_Information System_

 7.	The website worked well.
 8.	I had the impression that my data was necessary for the use of the website.
 9.	I found the website useful.

### Distributions

```{r}
plot_dist(
  item = "TR01",
  n_rows = 2
)
get_desc(
  item = "TR01",
  name = "trustspec"
)
```

### CFA

```{r}
name <- "trust_spec"
model <- "
  trust_community =~ TR01_01 + TR01_02 + TR01_03
  trust_provider =~ TR01_04 + TR01_05 + TR01_06
  trust_system =~ TR01_07 + TR01_08 + TR01_09

  trust =~ trust_community + trust_provider + trust_system
"
fit <- lavaan::sem(
  model = model, 
  data = d, 
  estimator = "MLR", 
  missing = "ML"
  )
```

Model fit:

```{r warning=T}
facval <- 
  fit_tab(
    fit, 
    reliability = TRUE, 
    scaled = TRUE
    ) %T>% 
  print()

assign(
  paste0(
    name, 
    "_facval"
    ), 
  facval
  )
```

Factor loadings:

```{r}
inspect(
  fit,
  what = "std") %$%
  lambda
```

### CFA 2

Because there was Heywoodcase, we now also run a model in which the subdimensions `provider` and `system` are combined.

```{r}
name <- "trustspec"
model <- "
  trust_community =~ TR01_01 + TR01_02 + TR01_03
  trust_provider =~ TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09
  trust_spec =~ b*trust_community + b*trust_provider
"
fit <- lavaan::sem(
  model = model, 
  data = d, 
  estimator = "MLR", 
  missing = "ML"
  )
```

Model fit:

```{r}
facval <- 
  fit_tab(
    fit, 
    reliability = TRUE, 
    scaled = TRUE
    ) %T>%
  print()

assign(
  paste0(
    name, 
    "_facval"
    ), 
  facval
  )
```

Factor loadings:

```{r}
inspect(
  fit,
  what = "std"
  ) %$%
  lambda
```
Warning disappears, results show adequate fit.

## Self-efficacy
### Items

 1. In principle, I felt able to write a comment.
 2. I felt technically competent enough to write a comment.
 3. In terms of the topic, I felt competent enough to express my opinion.
 4. I found it easy to express my opinion regarding the topic.
 5. I found it complicated to write a comment. (reversed)
 6. I was overburdened to write a comment. (reversed)

### Distributions

```{r fig.height = 3}
plot_dist(
  item = "SE01"
)
get_desc(
  item = "SE01",
  name = "selfeff"
)
```

### CFA

```{r}
name <- "self-eff"
model <- "
  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04 + SE01_05 + SE01_06
"
fit <- 
  lavaan::sem(
    model = model, 
    data = d, 
    estimator = "MLR", 
    missing = "ML"
    )
```

Model fit:

```{r}
facval <- 
  fit_tab(
    fit, 
    reliability = TRUE, 
    scaled = TRUE
    ) %T>%
  print()

assign(
  paste0(
    name, 
    "_facval"
    ), 
  facval
  )
```

Factor loadings:

```{r}
inspect(
  fit,
  what = "std") %$%
  lambda
```

Shows significant misfit. We will delete inverted items, while allowing covariations between Items 1 and 2 (tech-oriented) and Items 3 and 4 (topic-oriented).

### CFA 2

```{r}
name <- "selfeff"
model <- "
  self_eff_pos =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
"
fit <- 
  lavaan::sem(
    model = model, 
    data = d, 
    estimator = "MLR", 
    missing = "ML"
    )
```

Model fit:

```{r}
facval <- 
  fit_tab(
    fit, 
    reliability = TRUE, 
    scaled = TRUE
    ) %T>% 
  print()

assign(
  paste0(
    name, 
    "_facval"
    ), 
  facval
  )
```

Factor loadings:

```{r}
inspect(
  fit, 
  what = "std") %$%
  lambda
```

Adapted version shows better and adequate fit.

## Communication
### Density plot

```{r fig.height = 3}
ggplot(
  gather(
    select(
      d, 
      words
      )
    ), 
  mapping = aes(
    x = value
    )
  ) +
  geom_density() +
  facet_wrap(
    ~key, 
    nrow = 1
    ) + 
  theme_bw()
```

We see that Communication is severely skewed. Let's calculate how many participants actually commented.

```{r}
no_words_perc <- 
  d %>% 
  select(words) %>% 
  table() %>% 
  prop.table() %>% 
  .[1] %>% 
  unlist()

words_m <- 
  mean(
    d$words, 
    na.rm = TRUE
    )
```

Will hence be log-scaled for SEMs.

## Communication Logged

```{r}
ggplot(
  gather(
    select(
      d, 
      words_log
      )
    ), 
  mapping = aes(
    x = value
    )
  ) +
  geom_density() +
  facet_wrap(
    ~key, 
    nrow = 1
    ) + 
  theme_bw()
```

## Baseline model

In what follows, please find the results of all variables combined in one model. This model will be used to extract factor scores.

```{r cache=F}
model_baseline <- "
  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
  grats_inf =~ GR01_01 + GR01_02 + GR01_03 
  grats_rel =~ GR01_04 + GR01_05 + GR01_06 
  grats_par =~ GR01_07 + GR01_08 + GR01_09
  grats_ide =~ GR01_10 + GR01_11 + GR01_12 
  grats_ext =~ GR01_13 + GR01_14 + GR01_15
  grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
  trust_gen =~ TR02_01 + TR02_02 + TR02_03
  trust_community =~ TR01_01 + TR01_02 + TR01_03
  trust_provider =~ TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09
  trust_spec =~ b*trust_community + b*trust_provider
  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
    SE01_01 ~~ x*SE01_02
    SE01_03 ~~ x*SE01_04
  Words_log =~ words_log

  Words_log ~~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec + f1*trust_gen + g1*grats_spec
"

fit_baseline <- 
  lavaan::sem(
    model_baseline, 
    data = d, 
    missing = "ML"
    )

summary(
  fit_baseline, 
  standardized = TRUE, 
  fit.measures = TRUE
  )
```

# Descriptive analyses

We first report the factor validity of all variables combined.

```{r cache=F}
# extract model factor scores / predicted values for items & calc means
d_fs <- 
  lavPredict(
    fit_baseline, 
    type = "ov"
    ) %>% 
  as.data.frame() %>% 
  mutate(
    version = d$version, 
    grats_gen_fs = rowMeans(select(., starts_with("GR02"))),
    grats_spec_fs = rowMeans(select(., starts_with("GR01"))), 
    pri_con_fs = rowMeans(select(., starts_with("PC01"))),
    trust_gen_fs = rowMeans(select(., starts_with("TR02"))),
    trust_spec_fs = rowMeans(select(., starts_with("TR01"))),
    pri_del_fs = rowMeans(select(., starts_with("PD01"))),
    self_eff_fs = rowMeans(select(., starts_with("SE01")))) %>%
  select(
    version, 
    pri_con_fs, 
    grats_gen_fs, 
    grats_spec_fs, 
    pri_del_fs, 
    self_eff_fs, 
    trust_gen_fs, 
    trust_spec_fs, 
    words_log
    )

# combine d with d factor scores
d %<>% 
  cbind(
    select(
      d_fs, 
      -version, 
      -words_log
      )
    )

# add centered predictors for interaction analyses later
d %<>%
  mutate(
    pri_con_fs_c = scale(pri_con_fs, scale = FALSE),
    grats_spec_fs_c = scale(grats_spec_fs, scale = FALSE),
    pri_del_fs_c = scale(pri_del_fs, scale = FALSE),
    trust_gen_fs_c = scale(trust_gen_fs, scale = FALSE),
    self_eff_fs_c = scale(self_eff_fs, scale = FALSE),
    male_c = scale(male, scale = FALSE),
    edu_c = scale(edu, scale = FALSE),
    age_c = scale(age, scale = FALSE),
    con_x_del = pri_con_fs_c * pri_del_fs_c,
    grats_x_del = grats_spec_fs_c * pri_del_fs_c
    )

# rename for plotting
d_fs %<>% 
  set_names(
    c(
      "version", 
      var_names_breaks
      )
    )

# means of model predicted values
des <- 
  rbind(
    des_pricon,
    des_gratsgen,
    des_gratsspec,
    des_pridel,
    des_trustgen,
    des_trustspec,
    des_selfeff
    )

facval_tab <- 
  rbind(
    pricon_facval,
    gratsgen_facval,
    gratsspec_facval,
    pridel_facval,
    selfeff_facval,
    trustgen_facval,
    trustspec_facval
    ) %$%
  cbind(
    des[-c(8), ],
    .
    ) %>%
  set_rownames(
    var_names[-c(8)]
    )

facval_tab %>% 
  kable() %>% 
  kable_styling("striped") %>% 
  scroll_box(width = "100%")
```

In what follows, we report zero-order correlations, distributions, and scatterplots of the variables' factor scores.

```{r fig.height=9, fig.width=9}
corr_plot <- 
  ggpairs(
    select(d_fs, -version),
    upper = list(
      continuous = cor_plot
      ),
    lower = list(
      continuous = wrap(
        td::scat_plot, 
        coords = c(1, 7, 0, 7)
        )
      )
    ) + 
  theme_bw()
print(corr_plot)
ggsave("figures/results/cor_plot.png")
```

# Power analyses

In what follows, we report power analyses for our study. Please note that we conduct a rudimentary power-analysis, assuming bivariate correlations. To explain, at the time we were not yet aware of the existence of power analyses for multivariate structural equation models.

```{r include=F}
# define pwr-criteria
z_crit <- 1.96
alpha <- .05
power_desired <- .95
r_sesoi <- .10
```

We first estimate the sample size necessary to find small effects in 95% of all cases.

```{r}
# estimate pwr-samplesize
pwr.r.test(
  r = r_sesoi, 
  sig.level = alpha, 
  power = power_desired, 
  alternative = "greater"
  ) %T>%
  print %$% 
  n %>% 
  round(0) ->
  n_desired
```

We then compute the power we have achieved with our finale sample size to detect small effects.

```{r}
# compute pwr-achieved
pwr.r.test(
  n = n_final, 
  r = r_sesoi, 
  sig.level = alpha, 
  alternative = "greater"
  ) %T>%
  print %$% 
  power %>% 
  round(2) ->
  power_achieved
```

We finally compute what effect size we are likely to find in 95% of all cases given our final sample size.

```{r}
# estimate pwr-sensitivity
pwr.r.test(
  n = n_final, 
  power = power_desired, 
  sig.level = alpha, 
  alternative = "greater"
  ) %T>%
  print %$% 
  r %>% 
  round(2) ->
  r_sensitive
```

# Assumptions
## Multivariate normal distribution

```{r}
# create subset of data with all items that were used
items_used <- 
  c(
    "words", 
    "GR02_01", "GR02_02", "GR02_03", "GR02_04", "GR02_05", 
    "PC01_01", "PC01_02", "PC01_04", "PC01_05", "PC01_06", "PC01_07", 
    "TR01_01", "TR01_02", "TR01_03", "TR01_04", "TR01_05", "TR01_06", "TR01_07", "TR01_08", "TR01_09",
    "TR02_01", "TR02_02", "TR02_03", 
    "PD01_01", "PD01_02", "PD01_03", "PD01_04", "PD01_05", 
    "SE01_01", "SE01_02", "SE01_03", "SE01_04", 
    "male", "age", "edu"
    )
d_sub <- d[, items_used]

# test multivariate normal distribution
mvn_result <- mvn(d_sub, mvnTest = "mardia")
mvn_result$multivariateNormality
```

Shows that multivariate normal distribution is violated. We hence use maximum likelihood estimation with robust standard errors and a Satorra-Bentler scaled test statistic.

## Influential cases

[Note: These lines stopped working after some time, potentially due to changes in package.]

In what follows we test for influential cases in the baseline model, to detect potentially corrupt data (e.g., people who provided response patterns). Specifically, we compute Cook's distance.

```{r eval=F}
cooks_dis <- 
  gCD(
    d, 
    model_baseline
    ) %T>% 
  plot()
```

The following ten cases have a particularly strong influence on the baseline model.

```{r eval=F}
infl_cases <- 
  invisible(
    rownames(
      print(
        cooks_dis
        )
      )
    )
```

Let's inspect these cases.

```{r eval=F}
infl_cases_tokens <- 
  d[infl_cases, "case_token"] %>% 
  as_vector()

d %>% 
  filter(
    case_token %in% infl_cases_tokens
    ) %>% 
  select(
    case_token, 
    GR01_01:SE01_06, 
    topics_entered:reactions, 
    -SO01_01, 
    TIME_SUM_t1, 
    TIME_SUM_t2
    ) %>% 
  kable() %>% 
  kable_styling("striped") %>% 
  scroll_box(width = "100%")
```

These data do not reveal potential cases of response patterns. Indeed, answer times suggest that respondents were diligent.

# Results
## Preregistered
### Privacy calculus

```{r}
model <- "
  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
  trust_community =~ TR01_01 + TR01_02 + TR01_03
  trust_provider =~ TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09
  trust_spec =~ b*trust_community + b*trust_provider

words_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec

# Covariates
words_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_02 + TR01_03 + TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu

# Covariances
male ~~ age + edu
age ~~ edu
"

fit_prereg <- 
  lavaan::sem(
    model, 
    data = d, 
    estimator = "MLR", 
    missing = "ML"
    )

summary(
  fit_prereg, 
  fit = TRUE, 
  std = TRUE
  )

rsquare_fit_prereg <- 
  inspect(
    fit_prereg, 
    what = "rsquare"
    )["words"]
```

Results show that there's only one significant predictor of Communication, being self-efficacy. The other predictors are in the direction as planned, albeit not significant. Trust, however, shows the inverse relation as effect, that is, more trust, less communication.

### Effects of popularity cues
#### Confidence intervals

The easiest way to assess the effect of the experimental manipulation on the variables is by visualizing their means. If 83% confidence intervals don't overlap, the variables differ significantly across the conditions. One can quickly see that there aren't any major effects.

```{r}
# violin plot
fig_fs_m <- 
  ggplot(
    gather(
      d_fs, 
      variable, 
      value, 
      -version) %>% 
      mutate(
        variable = factor(
          variable, 
          levels = var_names_breaks
          )
        ),
    aes(
      x = version, 
      y = value, 
      fill = version
      )
    ) +
  geom_violin(
    trim = TRUE
    ) +
  stat_summary(
    fun.y = mean, 
    geom = "point"
    ) +
  stat_summary(
    fun.data = mean_se, 
    fun.args = list(mult = 1.39), 
    geom = "errorbar", 
    width = .5
    ) + 
  facet_wrap(
    ~ variable, 
    nrow = 2
    ) + 
  theme_bw() +
  theme(
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    plot.title = element_text(hjust = .5),
    panel.spacing = unit(.9, "lines"),
    text = element_text(size = 12),
    legend.position="none",
    legend.title = element_blank()) +
  coord_cartesian(
    ylim = c(0, 7)
    ) +
  scale_fill_brewer(
    palette = "Greys"
    )
ggsave(
  "figures/results/violin_plot.png", 
  width = 8, 
  height = 6
  )
fig_fs_m
```

#### SEM

In what follows, we also report explicit statistical tests of the differences between the conditions using contrasts.

**Like & Like-Dislike vs. Control**

```{r}
model <- "
  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
  trust_community =~ TR01_01 + TR01_02 + TR01_03
  trust_provider =~ TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09
  trust_spec =~ b*trust_community + b*trust_provider

  pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ like + likedislike
  words ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*like + g*likedislike

# Covariates
words + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_02 + TR01_03 + TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"

fit_lik_ctrl <- 
  lavaan::sem(
    model = model, 
    data = d, 
    estimator = "MLR", 
    missing = "ML", 
    fixed.x = FALSE
    )

summary(
  fit_lik_ctrl, 
  fit = TRUE, 
  std = TRUE
  )
```

No significant effects of popularity cues on privacy calculus.

**Like-Dislike & Control vs. Like**

```{r}
model <- "
  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
  trust_community =~ TR01_01 + TR01_02 + TR01_03
  trust_provider =~ TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09
  trust_spec =~ b*trust_community + b*trust_provider

  pri_con + grats_gen + pri_delib + self_eff + trust_spec + words ~ likedislike + control

# Covariates
words + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_02 + TR01_03 + TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_lik_ctrl <- 
  lavaan::sem(
    model = model, 
    data = d, 
    estimator = "MLR", 
    missing = "ML")

summary(
  fit_lik_ctrl, 
  fit = TRUE, 
  std = TRUE
  )
```

No significant effects of popularity cues on privacy calculus.

## Exploratory analyses

The bivariate relations showed several strong correlations. 
People who trusted the providers more also experienced more gratifications (_r_ = .79).
In multiple regression, we analze the potential effect of one variable on the outcome while holding all others constant. 
In this case, I tested whether trust increases communication while holding constant gratifications, privacy concerns, privacy deliberations, and self-efficacy. 
Given the close theoretical and empirical interrelations between the predictors, this creates an unlikely and artifical scenario. 
If people say loose trust in a provider, they will likely experience more concerns and less benefits. 
But it is not even necessary to control for these mediating factors. 
When trying to analyze the causal effect, it is necessary to control for counfounding variables, but importantly not for mediators [@rohrerThinkingClearlyCorrelations2018].
Confunding variables impact both the independent variable and the outcome. 
Sociodemographic variables are often ideal candidates for confounders.
For example, men are generally less concerned about their privacy and post more online.
Hence, controlling for gender hence helps isolate the actual causal effect. 
As a result, I reran the analyses controlling for confounding variables that are not mediators.

### Experimental Factors
#### Words

We first compare likes and likes plus dislikes to the control condition.

```{r}
run_hurdles(
  object = d,
  name = "wrds_ctrl",
  outcome = "words", 
  predictor = "version",
  y_lab = "Words",
  x_lab = "Experimental conditions"
  )
```

Let's find out by how much people in like and like plus dislike condition wrote fewer words.

```{r}
words_m_ctrl <- 
  fig_wrds_ctrl$data %>% 
  filter(effect1__ == "Control") %>% 
  select(estimate__)

words_m_lk <- 
  fig_wrds_ctrl$data %>% 
  filter(effect1__ == "Like") %>% 
  select(estimate__)

words_m_lkdslk <- 
  fig_wrds_ctrl$data %>% 
  filter(effect1__ == "Like & Dislike") %>% 
  select(estimate__)

effect_lk_wrds <- words_m_ctrl - words_m_lk
effect_lkdslk_wrds <- words_m_ctrl - words_m_lkdslk

effect_lk_prcnt <- 
  (effect_lk_wrds / words_m_ctrl) * 100 %>% 
  round()
effect_lkdlk_prcnt <- 
  (effect_lkdslk_wrds / words_m_ctrl) * 100 %>% 
  round()
```

Compared to the control condition, participants wrote `r effect_lkdlk_prcnt` percent fewer words on the platform with likes and dislikes.

We then compare likes and likes plus dislikes to the control condition.

```{r}
run_hurdles(
  object = d, 
  name = "wrds_lkdslk",
  outcome = "words", 
  predictor = "version_lkdslk",
  y_lab = "Words",
  x_lab = "Experimental conditions"
  )
```

#### Privacy Concerns

We first compare likes and likes plus dislikes to the control condition.

```{r}
run_hurdles(
  object = d,
  name = "pricon_ctrl",
  outcome = "pri_con_fs", 
  predictor = "version",
  y_lab = "Privacy concerns",
  x_lab = "Experimental conditions"
  )
```

We then compare likes and likes plus dislikes to the control condition.

```{r}
run_hurdles(
  object = d, 
  name = "pricon_lkdslk",
  outcome = "pri_con_fs", 
  predictor = "version_lkdslk",
  y_lab = "Privacy concerns",
  x_lab = "Experimental conditions"
  )
```

#### Expected Gratifications

We first compare likes and likes plus dislikes to the control condition.

```{r}
run_hurdles(
  object = d,
  name = "grats_ctrl",
  outcome = "grats_gen_fs", 
  predictor = "version",
  y_lab = "Gratifications",
  x_lab = "Experimental conditions"
  )
```

We then compare likes and likes plus dislikes to the control condition.

```{r}
run_hurdles(
  object = d, 
  name = "grats_lkdslk",
  outcome = "grats_gen_fs", 
  predictor = "version_lkdslk",
  y_lab = "Gratifications",
  x_lab = "Experimental conditions"
  )
```

#### Privacy Deliberation

We first compare likes and likes plus dislikes to the control condition.

```{r}
run_hurdles(
  object = d,
  name = "pridel_ctrl",
  outcome = "pri_del_fs", 
  predictor = "version",
  y_lab = "Privacy deliberation",
  x_lab = "Experimental conditions"
  )
```

We then compare likes and likes plus dislikes to the control condition.

```{r}
run_hurdles(
  object = d, 
  name = "pridel_lkdslk",
  outcome = "pri_del_fs", 
  predictor = "version_lkdslk",
  y_lab = "Privacy deliberation",
  x_lab = "Experimental conditions"
  )
```

#### Trust

We first compare likes and likes plus dislikes to the control condition.

```{r}
run_hurdles(
  object = d,
  name = "trust_ctrl",
  outcome = "trust_gen_fs", 
  predictor = "version",
  y_lab = "Trust",
  x_lab = "Experimental conditions"
  )
```

We then compare likes and likes plus dislikes to the control condition.

```{r}
run_hurdles(
  object = d, 
  name = "trust_lkdslk",
  outcome = "trust_gen_fs", 
  predictor = "version_lkdslk",
  y_lab = "Trust",
  x_lab = "Experimental conditions"
  )
```

#### Self-Efficacy

We first compare likes and likes plus dislikes to the control condition.

```{r}
run_hurdles(
  object = d,
  name = "selfeff_ctrl",
  outcome = "self_eff_fs", 
  predictor = "version",
  y_lab = "Self-efficacy",
  x_lab = "Experimental conditions"
  )
```

We then compare likes and likes plus dislikes to the control condition.

```{r}
run_hurdles(
  object = d, 
  name = "selfeff_lkdslk",
  outcome = "self_eff_fs", 
  predictor = "version_lkdslk",
  y_lab = "Self-efficacy",
  x_lab = "Experimental conditions"
  )
```

### Words
#### Privacy Concerns

```{r}
run_hurdles(
  object = d, 
  name = "wrds_pricon",
  outcome = "words", 
  predictor = "pri_con_fs",
  y_lab = "Words",
  x_lab = "Privacy concerns"
  )
```

Let's explore  how number of communicated words differ for people very much concerned versus not concerned at all.

```{r}
# let's extract effects for 1
wrds_pricon_1 <- 
  fig_wrds_pricon %$%
  data %>% 
  filter(
    pri_con_fs ==
      min(.$pri_con_fs)
  ) %$%
  estimate__ %>% 
  round(0)

# let's extract effects for 7
wrds_pricon_7 <- 
  fig_wrds_pricon %$%
  data %>% 
  filter(
    pri_con_fs ==
      max(.$pri_con_fs)
  ) %$%
  estimate__ %>% 
  round(0)
```

People who were not concerned at all communicated on average `r wrds_pricon_1 %>% round(0) %>% abs()` words, whereas people strongly concerned communicated on average `r wrds_pricon_7 %>% round(0)` words.

#### Expected Gratifications

```{r}
run_hurdles(
  object = d, 
  name = "wrds_grats",
  outcome = "words", 
  predictor = "grats_gen_fs",
  y_lab = "Words",
  x_lab = "Expected gratifications"
  )
```

#### Privacy Deliberation

```{r}
run_hurdles(
  object = d, 
  name = "wrds_pridel",
  outcome = "words", 
  predictor = "pri_del_fs",
  y_lab = "Words",
  x_lab = "Privacy deliberation"
  )
```

#### Trust

```{r}
run_hurdles(
  object = d, 
  name = "wrds_trust",
  outcome = "words", 
  predictor = "trust_gen_fs",
  y_lab = "Words",
  x_lab = "Trust"
  )
```

#### Self-Efficacy

```{r}
run_hurdles(
  object = d, 
  name = "wrds_selfeff",
  outcome = "words", 
  predictor = "self_eff_fs",
  y_lab = "Words",
  x_lab = "Self-Efficacy"
  )
```

The effects is markedly exponential. Let's inspect the changes across values in self-efficacy.

```{r}
effects_wrds_selfeff <- 
  slopes(
    fit_wrds_selfeff, 
    newdata = datagrid(
      self_eff_fs = c(1, 6, 7)
      ), 
   grid_type = "counterfactual"
    ) %>%
  filter(
    term == "self_eff_fs"
    ) %T>%
  print()

# let's extract effects for 1
effects_wrds_selfeff_12 <- 
  effects_wrds_selfeff %>% 
  filter(
    self_eff_fs == 1 &
      term == "self_eff_fs") %>% 
  select(estimate)

# let's extract effects for 7
effects_wrds_selfeff_67 <- 
  effects_wrds_selfeff %>% 
  filter(
    self_eff_fs == 6 &
      term == "self_eff_fs") %>% 
  select(estimate)

```

Whereas a change in self-efficacy from 1 to 2 led to an increase of `r effects_wrds_selfeff_12 %>% round(0)` words, a change from 6 to 7 led to an increase of `r effects_wrds_selfeff_67 %>% round(0)` words.

Let's explore  how number of communicated words differ for people very much self-efficacious versus not self-efficacious at all.

```{r}
# let's extract effects for 1
wrds_selfeff_1 <- 
  fig_wrds_selfeff %$%
  data %>% 
  filter(
    self_eff_fs ==
      min(.$self_eff_fs)
  ) %$%
  estimate__ %>% 
  round(0)

# let's extract effects for 7
wrds_selfeff_7 <- 
  fig_wrds_selfeff %$%
  data %>% 
  filter(
    self_eff_fs ==
      max(.$self_eff_fs)
  ) %$%
  estimate__ %>% 
  round(0)
```

People who reported no self-efficacy at all communicated on average `r wrds_selfeff_1 %>% round(0) %>% abs()` words, whereas people with very high self-efficacy communicated on average `r wrds_selfeff_7 %>% round(0)` words.

## Visualization

```{r}
fig_results <- 
  plot_grid(
    fig_wrds_pricon, 
    fig_wrds_grats, 
    fig_wrds_pridel, 
    fig_wrds_trust, 
    fig_wrds_selfeff,
    fig_wrds_ctrl
    ) %T>% 
  print()

ggsave("figures/results/effects.pdf")
ggsave("figures/results/effects.png")
```

## Table

Make table of slopes

```{r}
tab_slopes <- 
  rbind(
    slopes_wrds_pricon,
    slopes_wrds_grats,
    slopes_wrds_pridel,
    slopes_wrds_trust,
    slopes_wrds_selfeff,
    slopes_wrds_ctrl,
    slopes_wrds_lkdslk,
    slopes_pricon_ctrl,
    slopes_pricon_lkdslk,
    slopes_grats_ctrl,
    slopes_grats_lkdslk,
    slopes_pridel_ctrl,
    slopes_pridel_lkdslk,
    slopes_trust_ctrl,
    slopes_trust_lkdslk,
    slopes_selfeff_ctrl,
    slopes_selfeff_lkdslk
    ) %>% 
  as.data.frame() %>% 
  mutate(
    term = ifelse(
      .$contrast == "Like - Control", 
      "Like - Control",
      ifelse(
        .$contrast == "Like & Dislike - Control", 
        "Like & Dislike - Control",
        ifelse(
          .$contrast == "Like - Like & Dislike", 
          "Like - Like & Dislike", 
          .$term
          )
        )
      ),
    Predictor = recode(
      term, 
      "Like - Control" = "Like vs.control",
      "Like & Dislike - Control" = "Like & dislike vs.control",
      "Like - Like & Dislike" = "Like vs.like & dislike",
      "pri_con_fs" = "Privacy concerns",
      "pri_del_fs" = "Privacy deliberation",
      "grats_gen_fs" = "Expected gratifications",
      "trust_gen_fs" = "Trust",
      "self_eff_fs" = "Self-efficacy"
    ),
    Outcome = recode(
      Outcome,
      "pri_con_fs" = "Privacy concerns",
      "pri_del_fs" = "Privacy deliberation",
      "grats_gen_fs" = "Expected gratifications",
      "trust_gen_fs" = "Trust",
      "self_eff_fs" = "Self-efficacy"
    )
  ) %>% 
  filter(
    Predictor %in% c(
      "Like vs.control",
      "Like & dislike vs.control",
      "Like vs.like & dislike",
      "Privacy concerns",
      "Privacy deliberation",
      "Expected gratifications",
      "Trust",
      "Self-efficacy")
  ) %>% 
  mutate(
    Predictor = factor(Predictor, levels = c(
      "Self-efficacy",
      "Trust",
      "Privacy deliberation",
      "Expected gratifications",
      "Privacy concerns",
      "Like vs.like & dislike",
      "Like & dislike vs.control",
      "Like vs.control"
      )
    ),
    Estimate = 
      ifelse(
        Outcome == "words",
        round(estimate),
        estimate
      ),
    LL = 
      ifelse(
        Outcome == "words",
        round(conf.low),
        conf.low
      ),
    UL = 
      ifelse(
        Outcome == "words",
        round(conf.high),
        conf.high
      ),
  ) %>% 
  select(
    Outcome,
    Predictor, 
    Estimate,
    LL, 
    UL
    )

tab_slopes %>% 
  kable() %>% 
  kable_styling("striped") %>% 
  scroll_box(width = "100%")
```

```{r SaveData, include=F, cache=F}
write.csv(
  d, 
  file = "data/data.csv", 
  row.names = FALSE
  )

save.image(
  file = "data/workspace_full.RData"
)

save(
  d_raw, d_all, d_fs, d
  , fit_baseline, fit_prereg
  # , fig_fs_m, fig_fs_cor, fig_coeffs
  , des_pridel
  , facval_tab
  , n_comments, n_desired, n_posts, n_speeding, n_time, n_words
  , n_users, n_final
  # , infl_cases, infl_cases_tokens
  , resp_pattern, n_resp_pattern
  , n_t1, age_t1_m, male_t1_m, college_t1_m
  , n_t2, age_t2_m, male_t2_m, college_t2_m
  , n_matched, n_final, age_final_m, male_final_m, college_final_m, words_m
  , r_sesoi, r_sensitive, power_achieved
  , no_words_perc
  , effects_wrds_selfeff_12, effects_wrds_selfeff_67, effect_lkdlk_prcnt
  , wrds_pricon_7, wrds_pricon_1, wrds_selfeff_1, wrds_selfeff_7
  , tab_slopes
  , file = "data/workspace.RData"
)
```

### 2023-04-11 analyses_explorations.Rmd
- initalize repo

 Explorations

### Model "Adapted"

Building on the preregistered model, instead of general gratifications and specific trust, we now use specific gratifications and general trust.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_gen =~ TR01_01 + TR01_05 + TR01_09

COMM_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen

# Covariates
COMM_log  + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 + TR01_01 + TR01_05 + TR01_09 ~ male + age + edu

# Covariances
male ~~ age + edu
age ~~ edu
"
fit_adapted <- lavaan::sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_adapted, fit = TRUE, std = TRUE)
rsquare_fit_adapted <- inspect(fit_adapted, what = "rsquare")["comm"]
```

Effects become a bit larger and significant, which seems to make sense. However, this also includes trust, which is a significant negative predictor of communication.

### Model "Adapted 2"

Building on the preregistered model, instead of general gratifications and specific trust, we now use specific gratifications and general trust.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_gen =~ TR01_01 + TR01_05 + TR01_09

COMM_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_gen

# Covariates
COMM_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 + TR01_01 + TR01_05 + TR01_09 ~ male + age + edu

# Covariances
male ~~ age + edu
age ~~ edu
"
fit_adapted_2 <- lavaan::sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_adapted_2, fit = TRUE, std = TRUE)
rsquare_fit_adapted_2 <- inspect(fit_adapted_2, what = "rsquare")["comm"]
```

### Model "Simple"

We now use only two variables, namely specific gratifications and privacy concerns.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext

COMM_log ~ a1*pri_con + b1*grats_spec

# Covariates
COMM_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu

# Covariances
male ~~ age + edu
age ~~ edu
"
fit_simple <- lavaan::sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_simple, fit = TRUE, std = TRUE)
rsquare_fit_simple <- inspect(fit_simple, what = "rsquare")["comm"]
```

Works as hypothesized.

### Model "Interaction complex"

We now estimate an interaction model, as suggested by an anonymous reviewer. To estimate the interaction we'll use factor scores.

```{r}
model <- "
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_gen =~ TR01_01 + TR01_05 + TR01_09

COMM_log ~ a1*pri_con_fs_c + b1*grats_spec_fs_c + c1*pri_del_fs_c + con_x_del + grats_x_del + d1*self_eff + e1*trust_gen

# Covariates
COMM_log + SE01_01 + SE01_02 + SE01_03 + SE01_04 + TR01_01 + TR01_05 + TR01_09 + pri_con_fs_c + grats_spec_fs_c + pri_del_fs_c + con_x_del ~ male + age + edu

# Covariances
pri_con_fs_c ~~ grats_spec_fs_c + pri_del_fs_c + con_x_del + grats_x_del + self_eff + trust_gen
grats_spec_fs_c ~~ pri_del_fs_c + con_x_del + grats_x_del + self_eff + trust_gen
pri_del_fs_c ~~ con_x_del + grats_x_del + self_eff + trust_gen
con_x_del ~~ grats_x_del + self_eff + trust_gen
grats_x_del ~~ self_eff + trust_gen
self_eff ~~ trust_gen
male ~~ age + edu
age ~~ edu
"

fit_inter <- lavaan::sem(model, data = d, estimator = "MLR", missing = "ML", missing = "ML")
summary(fit_inter, fit = TRUE, std = TRUE)
rsquare_fit_inter <- inspect(fit_inter, what = "rsquare")["comm"]
```

Results are interesting. Both interaction effects are significant. If Deliberation increases, the effect of concerns on communication increase (net effect). If Deliberation increases, the effect of gratifications on communication decrease. Hence, could imply that if people think more, concerns more relevant than benefits.

### Model "Interaction simple"

We now estimate an interaction model, as suggested by an anonymous reviewer. To estimate the interaction we'll use factor scores.

```{r}
model <- "
COMM_log ~ a1*pri_con_fs_c + b1*grats_spec_fs_c + c1*pri_del_fs_c + con_x_del + grats_x_del

# Covariates
COMM_log + pri_con_fs_c + grats_spec_fs_c + pri_del_fs_c + con_x_del ~ male + age + edu

# Covariances
pri_con_fs_c ~~ grats_spec_fs_c + pri_del_fs_c + con_x_del + grats_x_del
grats_spec_fs_c ~~ pri_del_fs_c + con_x_del + grats_x_del
pri_del_fs_c ~~ con_x_del + grats_x_del
con_x_del ~~ grats_x_del
male ~~ age + edu
age ~~ edu
"

fit_inter_simple <- lavaan::sem(model, data = d, estimator = "MLR", missing = "ML", missing = "ML")
summary(fit_inter_simple, fit = TRUE, std = TRUE)
rsquare_fit_inter_simple <- inspect(fit_inter_simple, what = "rsquare")["comm"]
```

Results are interesting. Both interaction effects are significant. If Deliberation increases, the effect of concerns on communication increase (net effect). If Deliberation increases, the effect of gratifications on communication decrease. Hence, could imply that if people think more, concerns more relevant than benefits.

### Model Comparisons

```{r}
model_comp_tab <- data.frame(
  preregistered = fitmeasures(fit_prereg, c("BIC", "AIC")),
  adapted = fitmeasures(fit_adapted, c("BIC", "AIC")),
  simple = fitmeasures(fit_simple, c("BIC", "AIC"))) %>% 
  t() %T>%
  print()
```

### Model "BRMS"

Because the dependent variable is a zero-inflated Poisson distribution, we'll also run Bayesian models, which can explicitly account for this distribution.

#### Adapted Model

```{r}
fit_brms <- brm(COMM ~ pri_con_fs + grats_gen_fs + pri_del_fs + self_eff_fs + trust_gen_fs + age + male + edu, data = d, family = zero_inflated_poisson())
d_predicted <- predict(fit_brms) %>% as.data.frame()
summary(fit_brms)
```

Shows very similar results compared to SEM. Again, trust a negative predictor.

Let's also look at how values are predicted to see how model performs.

```{r}
d_predicted <- predict(fit_brms) %>% as.data.frame()
ggplot(d_predicted, aes(Estimate)) + 
  geom_density()
```

Let's also plot actual values.

```{r}
# plot actual values
ggplot(d, aes(COMM)) + 
  geom_density()
```

Model-predicted values don't closely match actual values.

#### Without Trust

Because trust has a negative coefficient, which seems generally implausible, we also run a model without trust.

```{r}
fit_brms <- 
  brm(
    COMM ~ pri_con_fs + grats_spec_fs + pri_del_fs + self_eff_fs + age + male + edu, 
    data = d, 
    family = zero_inflated_poisson()
    )
d_predicted <- 
  predict(fit_brms) %>% 
  as.data.frame()
summary(fit_brms)
```

Also doesn't make much sense, privacy concern now positive predictor. Self-Efficacy a strong predictor of behavior.

#### Simple model

```{r}
fit_brms_simple <- brm(COMM ~ pri_con_fs + grats_spec_fs + age + male + edu, data = d, family = zero_inflated_poisson())
summary(fit_brms_simple)
```

Also works, showing somewhat stronger effects.

#### Preregistered

```{r}
fit_brms_hrdl_prereg <- 
  brm(
    bf(
      COMM ~ 
        1 + 
        pri_con_fs + 
        grats_spec_fs + 
        pri_del_fs + 
        trust_gen_fs +
        self_eff_fs +
        age + 
        male + 
        edu, 
      hu ~ 
        1 + 
        pri_con_fs + 
        grats_spec_fs + 
        pri_del_fs + 
        trust_gen_fs +
        self_eff_fs +
        age + 
        male + 
        edu
    ), 
    data = d, 
    family = hurdle_gamma()
  )

```

```{r}
plot(fit_brms_hrdl_prereg, ask = FALSE)
```

```{r}
model_diagnostics(fit_brms_hrdl_prereg)
```

```{r}
summary(fit_brms_hrdl_prereg)
```

```{r}
conditional_effects(fit_brms_hrdl_prereg, ask = FALSE)
```

#### Adapted

```{r}
fit_brms_hrdl_adapted <- 
  brm(
    bf(
      COMM ~ 
        1 + 
        pri_con_fs + 
        grats_spec_fs + 
        pri_del_fs + 
        self_eff_fs +
        age + 
        male + 
        edu, 
      hu ~ 
        1 + 
        pri_con_fs + 
        grats_spec_fs + 
        pri_del_fs + 
        self_eff_fs +
        age + 
        male + 
        edu
    ), 
    data = d, 
    family = hurdle_gamma()
  )

```

```{r}
plot(fit_brms_hrdl_adapted, ask = FALSE)
```

```{r}
model_diagnostics(fit_brms_hrdl_adapted)
```

```{r}
summary(fit_brms_hrdl_adapted)
```

```{r}
conditional_effects(fit_brms_hrdl_adapted, ask = FALSE)
```

#### 3-way Interaction

```{r}
fit_brms_hrdl_inter <- 
  brm(
    bf(
      COMM ~ 
        1 + 
        pri_con_fs_c * 
        grats_spec_fs_c * 
        pri_del_fs_c + 
        self_eff_fs_c +
        age_c + 
        male_c + 
        edu_c, 
      hu ~ 
        1 + 
        pri_con_fs_c * 
        grats_spec_fs_c * 
        pri_del_fs_c + 
        self_eff_fs_c +
        age_c + 
        male_c + 
        edu_c
    ), 
    data = d, 
    family = hurdle_gamma()
  )

```

```{r}
plot(fit_brms_hrdl_inter, ask = FALSE)
```

```{r}
model_diagnostics(fit_brms_hrdl_inter)
```

```{r}
summary(fit_brms_hrdl_inter)
```

```{r}
conditional_effects(fit_brms_hrdl_inter, ask = FALSE)
```

#### Simple hurdle model

```{r}
fit_brms_simple_hurdle <- 
  brm(
    bf(
      COMM ~ 
        1 + 
        pri_con_fs + 
        grats_spec_fs + 
        age + 
        male + 
        edu, 
      hu ~ 
        1 + 
        pri_con_fs + 
        grats_spec_fs + 
        age + 
        male + 
        edu
    ), 
    data = d, 
    family = hurdle_gamma()
  )
```

```{r}
plot(fit_brms_simple_hurdle, ask = FALSE)
```

```{r}
model_diagnostics(fit_brms_simple_hurdle)
```

```{r}
summary(fit_brms_simple_hurdle)
```

```{r}
conditional_effects(fit_brms_simple_hurdle, ask = FALSE)
```

#### Interaction model

#### Simple hurdle model

```{r}
fit_brms_hurdle_inter <- 
  brm(
    bf(
      COMM ~ 
        1 + 
        pri_con_fs_c * 
        grats_spec_fs_c *
        pri_del_fs_c +
        age + 
        male + 
        edu, 
      hu ~ 
        pri_con_fs_c * 
        grats_spec_fs_c *
        pri_del_fs_c +
        age + 
        male + 
        edu
    ), 
    data = d, 
    family = hurdle_gamma()
  )
```

```{r}
plot(fit_brms_hurdle_inter, ask = FALSE)
```

```{r}
model_diagnostics(fit_brms_hurdle_inter)
```

```{r}
summary(fit_brms_hurdle_inter)
```

```{r}
conditional_effects(fit_brms_hurdle_inter, ask = FALSE)
```

#### Interaction model including deliberation

```{r}
fit_brms <- brm(COMM ~ pri_con_fs_c * grats_spec_fs_c + pri_con_fs_c * pri_del_fs_c + grats_spec_fs_c * pri_del_fs_c + age + male + edu, data = d, family = zero_inflated_poisson())
summary(fit_brms)
```

### 2023-04-11 index.Rmd
- initalize repo

---
title: "Privacy Calculus Experiment"
---

On this website, you can find the companion material for the paper _Like or Dislike, Gratifications or Concerns? Analyzing Popularity Cues and Privacy Calculus in Online Communication_.

You can either read the paper [in your browser](manuscript.html) or download it as [pdf](manuscript.pdf). You can also find the detailed code and summaries of the [analyses](analyses.html) reported in the paper, as well as [additional analyses](analyses_additional.html) not reported in the paper.

This website is produced directly from the project's [github repository](https://github.com/tdienlin/privacy_calc_exp). You can download the material and the data, file an issue, or submit a pull request.

![](figures/website/website_translated.png)

### 2023-04-11 manuscript.RmD
- initalize repo

---
title             : "Likes or Dislikes, Gratifications or Concerns? Analyzing Popularity Cues and Privacy Calculus in Online Communication"

shorttitle        : "Popularity cues & privacy calculus"

abstract: |
    According to the privacy calculus model, online communication is mainly determined by the two factors of privacy concerns and expected benefits. This paper analyzes how the privacy calculus is affected by popularity cues, namely like and dislike buttons. In addition, the privacy calculus is extended by elaborating on the process of comparing benefits and drawbacks, termed privacy deliberation, and by investigating the role of trust and self-efficacy. To this end, a preregistered one-week field experiment with 590 participants was conducted. Participants were randomly distributed to three different websites, on which they discussed a current political topic. The websites featured either (a) like buttons, (b) both like and dislike buttons, or (c) no like or dislike buttons. The exploratory analyses revealed, contrary to what was expected, that implementing both like and dislike buttons decreased online communication. As predicted by the privacy calculus model, expected benefits and perceived privacy concerns substantially affected communcation. Actively deliberating about privacy by comparing benefits and drawbacks decreased communication, while experiencing self-efficacy and trust strongly increased communication.

keywords          : "privacy calculus, communication, popularity cues, field experiment, preregistration"

bibliography      : 
  - [bibliography/r-references.bib]
  - [bibliography/references.bib]
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : yes
wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
header-includes:
  - \setlength{\parskip}{0em}
  - \raggedbottom
  - \note{\clearpage}
# output            : papaja::apa6_docx
# output:
#   html_document:
#     toc: TRUE
#     toc_float:
#       collapsed: FALSE
#     toc_depth: 2
---

```{r include=F}
knitr::opts_chunk$set(
  cache=F, 
  echo=F, 
  warning=F, 
  message=F
  )
options(
  digits = 2
)
```

```{r setup, include=F}
# install github packages
# devtools::install_github("tdienlin/td@v.0.0.2.3")

# load packages
pcks <- c(
  "devtools", 
  "english",
  "jpeg", 
  "knitr", 
  "lavaan", 
  "magrittr", 
  "papaja", 
  "png", 
  "pwr", 
  "semTools", 
  "td", 
  "tidyverse"
  )

invisible(
  lapply(
    pcks, 
    library, 
    character.only = TRUE
    )
  )

# create bib with r-packages
r_refs(file = "bibliography/r-references.bib")

# load bib
r_citations <- 
  cite_r(
    "bibliography/r-references.bib"
    , footnote = FALSE
    , withhold = FALSE
    , pkgs = c(
      "brms"
      , "tidyverse"
      , "lavaan"
      , "marginaleffects"
      , "papaja" 
      , "pwr"
      , "quanteda"
      , "semTools"
      )
    )
```

```{r load-data, cache=F, include=F}
load("data/workspace.rData")
```

# Introduction

<!-- Understanding why people share personal information online is important.  -->
According to the privacy paradox, the way users share information online is erratic [@barnesPrivacyParadoxSocial2006]:
<!-- Personal beliefs, privacy concerns, or behavioral attitudes do not affect online behavior. -->
<!-- [for an overview of the privacy paradox, see @dienlinPrivacyParadoxAus2019].  -->
People communicate vast amounts of personal information online, although they are concerned about their privacy [@taddickenUsesPrivacyOnline2011].
However, despite its popularity in both academic research [@dienlinPrivacyParadoxAus2019] and the public press [@newyorkpublicradioPrivacyParadox2018], empirical support for the privacy paradox is weak [@baruhOnlinePrivacyConcerns2017; @dienlinDoesPrivacyParadox2021]. 
<!-- , which shows that privacy concerns are indeed related to communication online.  -->
<!-- Rather than further pursuing the privacy paradox,  -->
Research is therefore increasingly building on the privacy calculus model, which states that communication online can be explained successfully by means of perceived risks and expected benefits [@bolUnderstandingEffectsPersonalization2018b; @krasnovaOnlineSocialNetworks2010; @meierPrivacyCalculusRevisited2022].
<!-- Several studies have shown that experiencing more privacy risks or concerns is related to sharing less information online [@bolUnderstandingEffectsPersonalization2018b; @meierPrivacyCalculusRevisited2022], while expecting more benefits is related to sharing more information online [@heirmanPredictingAdolescentsDisclosure2013; @koohikamaliInvestigationDynamicModel2019]. -->

Although the privacy calculus has gained momentum in academic research, several important questions remain unanswered. 
First, we still know little about how the privacy calculus and online communication can be affected by external influences [@bazarovaIntegrationIndividualisticNetworked2020; @braunlichLinkingLooseEnds2020].
For example, does the existence of popularity cues such as like and dislike buttons affect the privacy calculus and online communication?
<!-- I therefore analyze whether the privacy calculus is affected by the affordances of a website.  -->
<!-- Specifically, I investigate whether *popularity cues* such as like and dislike buttons affect the privacy calculus and whether they foster communication online. -->
Second, the privacy calculus' empirical foundation needs to be improved [@knijnenburgDeathPrivacyCalculus2017]. 
To date, much research on the privacy calculus builds on (a) self-reports of behavior [@krasnovaOnlineSocialNetworks2010], (b) vignette approaches [@bolUnderstandingEffectsPersonalization2018b], or (c) one-shot experiments in the lab [@treptePrivacyCalculusContextualized2020]. 
Can the privacy calculus be replicated in an authentic and more long-term setting using actual behavioral data?
Third, research on the privacy calculus so far did not measure the actual process of weighing pros and cons [@knijnenburgDeathPrivacyCalculus2017], 
<!-- According to critics , showing that both concerns and gratifications correlate with communication behavior online is not sufficient evidence for an explicit weighing process.  -->
<!-- In this study I will thus focus on the explicit process of comparing pros and cons  -->
which I will do in this study by elaborating on the privacy deliberation process. 
Fourth, the privacy calculus model is criticized for over-emphasizing rationality [@knijnenburgDeathPrivacyCalculus2017].
Hence, I extend the privacy calculus in analyzing how trust and self-efficacy, two more psychological variables, affect communication.
<!-- Third, in this study I approach the privacy calculus from the theoretical perspective of _bounded rationality_.  -->
<!-- It is likely that other factors next to risks and benefits also determine behavior. -->
<!-- I therefore extend the privacy calculus model theoretically by investigating the role and interplay of trust and self-efficacy. -->

<!-- To answer these research questions, a representative sample of the German population was collected in a preregistered online field experiment. -->
<!-- Participants were randomly distributed to one of three different websites, which either included a like button, both a like and a dislike button, or no buttons at all.  -->
<!-- Over the course of one week, participants discussed a topical issue (i.e., prevention of terrorist attacks in Germany).  -->
<!-- In a follow-up questionnaire, they answered items measuring the privacy calculus variables. -->

## The Privacy Calculus

The privacy calculus analyzes why people communicate online.
When are people willing to engage in a conversation?
<!-- Do they express their opinion?  -->
It builds on the calculus of behavior [@lauferPrivacyConceptSocial1977], which states that people are weighing risks and benefits before communicating.
<!-- In communicating online, people share much information about themselves. -->
Communication is closely related to privacy, which is defined as a "voluntary and temporary withdrawal of a person from the general society" [@westinPrivacyFreedom1967, p. 7].
People regulate their privacy by deciding what and what not to communicate [@dienlinPrivacyProcessModel2014].
Disclosing information can be risky, and if people are more concerned about their privacy 
<!-- they should be less likely to communicate information. -->
<!-- Almost all types of communication allow for meaningful inferences about a person, even when we _don't_ communicate [@watzlawickPragmaticsHumanCommunication2011].  -->
<!-- However, the recent years have illustrated vividly how much additional insights we can get about a person, simply by analyzing their digital traces of communication or their meta-data [@kosinskiPrivateTraitsAttributes2013].  -->
<!-- The more we communicate, the more we self-disclose. -->
<!-- Online privacy concerns represent "[...] how much an individual is motivated to focus on their control over a voluntary withdrawal from other people or societal institutions on the Internet, accompanied by an uneasy feeling that their privacy might be threatened" [@dienlinLongitudinalAnalysisPrivacy2021, p. 4].  -->
<!-- Notably, I don't assume that this weighing process is flawless or perfectly rational. -->
<!-- Instead, I understand the privacy calculus from the perspective of _bounded rationality_ [@simonBoundedRationality1990], which has three main tenets:  -->
<!-- "(1) humans are cognitively constrained;  -->
<!-- (2) these constraints impact decision making;  -->
<!-- and (3) difficult problems reveal the constraints and highlight their significance." [@bendorBoundedRationality2015, p. 1303] -->
<!-- Crucially, although bounded rationally upholds that human behavior is not perfectly logical, this does not meant that it is illogical [@gigerenzerBoundedRationalityAdaptive2002]. -->
<!-- Instead, it makes more sense to consider rationality a continuum. -->
<!-- Humans are still trying to optimize the outcomes of their behavior according to their own best interests or values. -->
<!-- It is only that their capacity to do so is bounded. -->
<!-- Transferred to the context of online privacy, it is by now well known that several irregularities and inconsistencies between concerns and communication behavior exist. -->
<!-- These differences stem from, for example, information asymmetries, present bias, intangibility, illusory control, or herding [@acquistiSecretsLikesDrive2020]. -->
<!-- Indeed, If people experience more concerns,  -->
they are less likely to communicate online [@baruhOnlinePrivacyConcerns2017; @dienlinExtendedPrivacyCalculus2016a; @krasnovaOnlineSocialNetworks2010; @masurUnderstandingEffectsConceptual2023; @meierPrivacyCalculusRevisited2022].
According to a meta-analysis by @baruhOnlinePrivacyConcerns2017, the effect is small but significant (*r* = -.13).
<!-- At the same time, _on average_ people do behave according to their interests, respond to incentives, or actively manage their privacy [@baruhOnlinePrivacyConcerns2017; @braunlichLinkingLooseEnds2020; @dienlinExtendedPrivacyCalculus2016a; @soloveMythPrivacyParadox2020]. -->

<!-- I therefore hypothesize that people who experience more privacy concerns engage in less communication online. -->
<!-- In light of bounded rationality and the existence of other competing factors that also influence online-communication (see below), the effect is likely small. -->

Outweighing concerns, the most relevant drivers of online communication are expected gratifications [@dienlinExtendedPrivacyCalculus2016a; @bolUnderstandingEffectsPersonalization2018b; @kezerGettingPrivacyCalculus2022].
People are happy to trade in parts of their privacy, when they can get something more valuable in return [@lauferPrivacyConceptSocial1977].
In online communication, the most important benefits include social support [@krasnovaOnlineSocialNetworks2010], social capital [@ellisonNegotiatingPrivacyConcerns2011], entertainment [@dhirUnderstandingRelationshipIntensity2017], information-seeking [@whitingWhyPeopleUse2013], and self-presentation [@minHowArePeople2015].
<!-- As a result, we expect a moderate relationship. -->

H1: People who are more concerned about their privacy than others are less likely to communicate actively on a website.

H2: People who obtain more gratifications from using a website are more likely to communicate actively on a website.

Although privacy calculus implies that people explicitly compare benefits and drawbacks before communicating online, research has neglected this aspect [@knijnenburgDeathPrivacyCalculus2017].
Only observing that privacy concerns or expected gratifications and communication online are related does not prove that an explicit weighing process took place [@knijnenburgDeathPrivacyCalculus2017]. 
Instead, we need to analyze if and how much people actively deliberate about their privacy, and whether doing so influences their decision to communicate.
<!-- We can understand the privacy calculus from two perspectives. -->
<!-- First, is the communication behavior aligned with people's privacy concerns and expected benefits?  -->
<!-- Second, is the communication process implicit or explicit? -->
<!-- Here, I suggest that the privacy calculus should be discussed in light of dual process theories, which state that people either deliberately, explicitly, and centrally take decisions, or instead do so automatically, implicitly, and peripherally [@kahnemanThinkingFastSlow2011; @pettyCommunicationPersuasionCentral1986].  -->
<!-- Accordingly, privacy calculus would assume that people, when it comes to disclosing, engage in a central processing.  -->
Self-disclosure theory [@omarzuDisclosureDecisionModel2000;  @altmanPrivacyConceptualAnalysis1976] suggests that if the benefits to be attained from communication are attractive, deciding whether or not to communicate is a "conscious and deliberative process"  [@omarzuDisclosureDecisionModel2000, p. 183].
I hence introduce and investigate a novel concept termed _privacy deliberation_.
Privacy deliberation captures the extent to which individuals explicitly compare risks and benefits before communicating with others.
How could deliberating on one's privacy affect communication?
On the one hand, deliberating about privacy could reduce subsequent communication.
Refraining from communication---the primary means of connecting with others [@altmanPrivacyConceptualAnalysis1976]---likely requires some active and deliberate restraint [@omarzuDisclosureDecisionModel2000]. 
This is especially true for social media, which are designed to foster communication and participation [@ellisonSocialNetworkSite2015; @masurBehavioralContagionSocial2021].
Actively thinking about whether communicating is worthwhile might be the first step not to participate.
On the other hand, deliberating about privacy might also increase communication.
In light of the benefits mentioned above, a person might conclude that communication is beneficial, thereby legitimating communication [@krasnovaOnlineSocialNetworks2010]. 
<!-- I therefore formulate the following research question: -->
<!-- Deliberation could represent some kind of inner consent, providing additional affirmation. -->
<!-- Alternatively, it could be that deliberation functions as a moderator. -->
<!-- For example, if people actively deliberate about whether or not to disclose, this might reinforce the effect of concerns or gratifications. -->
<!-- Reflecting about the pros and cons of communication might concerns and gratifications more salient.  -->
<!-- Alternatively, it could also be that deliberating decreases the effects, for example because apparent gratifications are considered more critically, and maybe loose their appeal. -->

RQ1: Do people who deliberate more actively whether they should communicate, communicate more or less online?

<!-- RQ2: Do people who deliberate more actively whether they should communicate, show larger or smaller relations between concerns, gratifications and communication behavior? -->
This weighing process is not flawless or perfect.
It is therefore useful to understand the privacy calculus from a perspective of _bounded rationality_ [@simonBoundedRationality1990].
Bounded rationality states that "(1) humans are cognitively constrained; (2) these constraints impact decision making; and (3) difficult problems reveal the constraints and highlight their significance." [@bendorBoundedRationality2015, p. 1303].
But although human behavior is partly irrational, bounded rationality does not state that it is completely irrational [@gigerenzerBoundedRationalityAdaptive2002].
Rationality is a continuum. 
<!-- Instead, it makes more sense to consider rationality a continuum. -->
<!-- Humans are still trying to optimize the outcomes of their behavior according to their own best interests or values. -->
<!-- It is only that their capacity to do so is bounded. -->
In the context of online privacy, for example, rationality is impeded by information asymmetries, presence bias, intangibility, illusory control, or herding [@acquistiSecretsLikesDrive2020].
It follows that to provide a more complete picture, additional factors next to gratifications and concerns should also explain communication.
Factors less focused on rationality, but more on psychosocial aspects.
<!-- Communication online often takes place in situations where information is limited or obscure. -->

For example, if users are more familiar, experienced, and knowledgeable in a given online context, they are more likely to navigate that online contexts successfully and to communicate actively [@baruhOnlinePrivacyConcerns2017; @kramerMasteringChallengeBalancing2020].
People with more privacy self-efficacy also engage more successfully in self-withdrawal [@dienlinExtendedPrivacyCalculus2016a].
Hence, if users possess more _self-efficacy_ to participate, they should also communicate more.

H3: People are more likely to communicate on a website when their self-efficacy to actively use the website is higher.

In situations where people lack experience or competence, a relevant variable to understand behavior is _trust_.
Especially in online contexts, users often cannot control the environment or the way their information is handled [@acquistiSecretsLikesDrive2020; @braunlichLinkingLooseEnds2020].
Trust plays a key role in online communication [@metzgerPrivacyTrustDisclosure2004]. 
Trust either captures "_specific_ beliefs dealing primarily with the integrity, benevolence, and ability of another party" [@gefenTrustTAMOnline2003, p. 55, emphasis added] or a "_general_ belief that another party can be trusted" [@gefenTrustTAMOnline2003, p.55, emphasis added]. 
<!-- Whereas specific trust focuses on the causes of trust, general trust emphasizes the experience of trust. -->
In online contexts, there are different _targets_ of trust, including (a) the information system, (b) the provider, (c) the Internet, and (d) the community of other users [@sollnerWhyDifferentTrust2016]. 
People who put more trust in the providers of networks, for example, disclose more personal information [@liEmpiricalStudiesOnline2011]. 
<!-- @gefenTrustTAMOnline2003 prioritize specific trust (p. 60).  -->
<!-- Because the targets can be largely different, it is often recommended to analyze them individually. -->

H4: People are more likely to communicate on a website when they have greater trust in the provider, the website, and the other users.

## The Effects of Popularity Cues

How are the privacy calculus and communication affected by the context, the digital infrastructure? 
First, it makes sense not to focus on specific features of particular websites, which change and become obsolete [@foxDistinguishingTechnologiesSocial2017]. 
Instead, it is recommended focusing on the underlying latent structures by analyzing so-called _affordances_ [@ellisonSocialNetworkSite2015; @foxDistinguishingTechnologiesSocial2017].  
Affordances are mental representations of how objects might be used.
They emphasize that it is not the _objective features_ that determine behavior, but rather our _subjective perceptions_ [@gibsonEcologicalApproachVisual2015].
<!-- ; as such, they are by definition subjective.  -->
There is an ongoing debate on what exactly defines an affordance [@evansExplicatingAffordancesConceptual2017].
Whereas @evansExplicatingAffordancesConceptual2017 propose three affordances for mediated communication (i.e., anonymity, persistence, and visibility), @foxDistinguishingTechnologiesSocial2017 suggest 10 affordances for SNSs alone (i.e., accessibility, bandwidth, social presence, privacy, network association, personalization, persistence, editability, conversation control, and anonymity).
<!-- The privacy calculus states that both benefits and costs determine behavior. -->
Popularity cues such as like and dislike buttons, which are of interest here, are categorized as "paralinguistic digital affordances" [@carrPredictingThresholdPerceived2018, p. 142].

<!-- Both can be linked to the two sides of the privacy calculus.  -->
<!-- The like button is positive and a potential benefit: -->
<!-- It expresses an endorsement, a compliment, a reward [@carrPredictingThresholdPerceived2018; @sumnerFunctionalApproachFacebook2017].  -->
<!-- The dislike button is negative and a potential cost:  -->
<!-- It expresses criticism and a way to downgrade content.  -->

Paralinguistic digital affordances and specifically popularity cues have been shown to affect behavior [@kramerMasteringChallengeBalancing2020; @masurBehavioralContagionSocial2021; @treptePrivacyCalculusContextualized2020].
Online comments that already have several dislikes are more likely to receive further dislikes [@muchnikSocialInfluenceBias2013]. 
When users disagree with a post, they are more likely to click on a button labeled _respect_ compared to a button labeled _like_ [@stroudRecommendRespectAltering2017].
<!-- In light of their potentially strong negative effects, most major social networking sites did not implement dislike buttons.  -->
<!-- At the time of writing, only a handful of websites have (partially) implemented it (e.g., youtube, stackexchange, or reddit). -->
Popularity cues likely impact the privacy calculus via two underlying theoretical mechanisms [@kramerMasteringChallengeBalancing2020]:
First, the _mere presence_ of popularity cues might affect whether people are willing to disclose. 
Being able to attract likes might motivate users to communicate, while the mere option to receive dislikes might intimidate others.
Second, _actually receiving_ likes or dislikes might additionally affect subsequent behavior, thereby reinforcing the process.

Likes are positive and represent the positivity bias of social media [@schreursExposurePositivityBias2022]. 
Receiving a like online is similar to receiving a compliment offline [@carrPredictingThresholdPerceived2018; @sumnerFunctionalApproachFacebook2017].
Like-buttons afford and emphasize a _gain frame_ [@rosoffHeuristicsBiasesCyber2013].
These gains can be garnered only through active participation. 
Because like buttons emphasize positive outcomes, it is likely that concerns decrease. 
In situations where there is more to win, people might also more actively deliberate about whether or not to communicate. 
Dislike represent a punishment, introducing a _loss frame_. 
<!-- Although most communication emphasizes positive aspects, the Internet is also replete with spite, envy, and arguments. -->
Websites featuring both like _and_ dislike buttons should be more ambivalent compared to websites without popularity cues.
<!-- Especially in online contexts, short-term gains often outweigh long-term losses [@acquistiSecretsLikesDrive2020]. -->
<!-- Having both like and dislike buttons might still lead to more gratifications and communication. -->
Privacy concerns should not be reduced anymore:
People who are more concerned about their privacy are also more shy and risk averse [@dienlinPsychologyPrivacyAnalyzing2017].
Implementing the dislike button might therefore increase privacy concerns, thereby canceling out the positive effects of the like button. 
<!-- And because there is more at stake, participants should deliberate even more whether or not to disclose.  -->

H5.	People who use a website with like buttons (a) communicate more, (b) obtain more gratifications, (c) are less concerned about their privacy, and (d) deliberate more about whether they should communicate online.

H6.	People who use a website with like _and_ dislike buttons (a) communicate more, (b) obtain more gratifications, and (c) deliberate more about whether they should communicate online.

<!-- When directly comparing websites including both like and dislike buttons with websites including only like buttons, building on the rationales presented above, it is likely that websites including both buttons should increase privacy concerns and privacy deliberation. -->

H7.	Compared to people who use a website with only like buttons, people who use a website with like and dislike buttons (a) are more concerned about their privacy, and (b) deliberate more about whether they should communicate online.

For a simplified overview of the analyzed model, see Figure \@ref(fig:model).

```{r model, fig.cap="Overview of analyzed model.", fig.align='center', out.width=".8\\textwidth"}
# knitr::include_graphics("figures/design/model_simplified.pdf")
knitr::include_graphics("figures/design/model_simplified.png")
```

# Methods
## Open Science

This manuscript features a [companion website](https://XMtRa.github.io/like_dislike), which includes the data, research materials, analyses scripts, and a reproducible version of this manuscript (see https://XMtRa.github.io/like_dislike).
The hypotheses, sample size, research materials, analyses, and exclusion criteria were preregistered (see https://osf.io/a6tzc/?view_only=5d0ef9fe5e1745878cd1b19273cdf859). 
In some cases, the pre-registered approach needed to be changed (see [companion website](https://XMtRa.github.io/like_dislike)). 
Analyses that were not preregistered are reported as exploratory analyses.

## Procedure

The study was designed as an online field experiment with three different groups. 
The first experimental group used a website that included like buttons buttons; the second experimental group used an identical website including both like and dislike buttons; and the control group used an identical website without like and dislike buttons. 
Participants were randomly distributed to one of the three websites in a between-subject design.

The data were collected in Germany.
Participants were recruited using the professional panel agency Norstat.
As incentive, participants were awarded digital points, which they could use to get special offers from online retailers. 
Participants had to be above the age of 18 and had to live in Germany. 
In a first step, the company sent its panel members an invitation to participate in the study (_invitation_). 
In this invitation, panel members were asked to participate in a study analyzing the current threat posed by terrorist attacks in Germany.
<!-- [^1]  -->
Members who agreed to participate were sent the first questionnaire (_T1_).
The questionnaire asked participants about their sociodemographic background, (b) provided more details about the study, and (c) included a registration link for the website, which was described as "participation platform".
Afterward, participants were randomly assigned to one of the three websites. 
After registration was completed, participants were invited (but not obliged) to visit the website and to discuss the topic of the terrorism threat in Germany (_field_). 
Participants had the chance to use the website and to provide comments over the course of one week.
Subsequently, participants received a follow-up questionnaire in which the self-reported measures reported below were collected (_T2_). 
<!-- Measures were collected after and not before the field phase in order not to prime participants or reveal the primary research interest. -->

<!-- [^1]: Although the terror attack was not of primary interest for this study, the data can and will also be used to analyze perceptions of the terrorism threat. Hence, no deception took place, and in the debriefing participants were informed about the additional research interest in privacy.  -->

The online website was programmed based on the open-source software _discourse_ (https://www.discourse.org/). 
To make sure the website was professional and authentic, several pretests with students from the local university were run.
`r n_users %>% english::english() %>% str_to_sentence` participants created a user account on the website (see below) and used the website actively. 
Overall, they spent `r sum(d_raw$time_read, na.rm = TRUE) %>% "/"(3600) %>% round(0) %>% format(big.mark = ",")` hours online, wrote `r sum(d_raw$post_count, na.rm = TRUE) %>% format(big.mark = ",")` comments, and clicked on `r sum(d_raw$reactions, na.rm = TRUE)` popularity cues. 
All communication was checked, and there were no instances of people providing meaningless text or doubting the experiment.
For a screenshot of the landing page and an example of comments that were written, see Figure \@ref(fig:website).

```{r website, echo=FALSE, out.width="49%", fig.cap="Screenshot of the landing page and of communication taking place", fig.show='hold', fig.align='center'}
knitr::include_graphics(c("figures/website/website_translated.png","figures/website/comments_translated.png"))
```

## Participants

Sample size was determined using a priori power analyses.
The power analysis was based on a smallest effect size of interest approach [SESOI, @lakensEquivalenceTestingPsychological2018]. 
<!-- Namely, I defined a minimum effect size considered sufficiently large to support the hypotheses.  -->
When researching aspects of privacy online [e.g., @baruhOnlinePrivacyConcerns2017], effects are often small [i.e., _r_ = .10, @cohenPowerPrimer1992].
Hence, the SESOI was set to be _r_ = `r r_sesoi %>% my_round("std")`. 
The aim was to be able to detect this SESOI with a probability of at least 95% (i.e., power = 95%).
Using the regular alpha level of 5%, power analyses suggested a minimum sample size of _N_ = `r n_desired %>% format(big.mark = ",")`. 
In the end, I was able to include _N_ = `r n_final` in the analyses (see below), which was significantly smaller than the original aim.
With this sample size, the study had a power of `r power_achieved * 100`% to find an effect at least as large as _r_ = `r r_sesoi %>% my_round("std")`. 
<!-- To understand the implications, I ran sensitivity analyses. -->
<!-- With the final sample size, what effects can still be found reliably, that is with a power of 95%? -->
Sensitivity analyses showed that the current study could still make reliable results (i.e., power = 95%) for effects at least as large as _r_ = `r r_sensitive %>% my_round("std")`.
In conclusion, although not as powerful as planned, the study is still adequately powered to find the small effects reported in the privacy literature [@baruhOnlinePrivacyConcerns2017].

A quota sample that matched the German population in terms of age, gender, and federal state was collected. 
In sum, `r n_t1 %>% format(big.mark = ",")` participants completed the survey at T1; 
`r n_users` participants created a user account on the website;  and `r n_t2` participants completed the survey at T2. 
The data were connected using tokens and IP addresses.
For technical reasons, the data of several participants could not be matched (for example, because they used different devices for the respective steps).
In the end, the data of `r n_matched` participants could be matched successfully.
Considered unreasonably fast, `r n_speeding %>% english()` participants were excluded who finished the questionnaire at T2 in less than three minutes.
To detect atypical data and response patterns, I calculated Cook's distance.
I excluded `r english(n_resp_pattern)` participants with clear response patterns (i.e., straight-lining). 
The final sample included _N_ = `r n_final` participants.
The sample characteristics at T1 and T2 were as follows: 
T1: age = `r round(age_t1_m, 0)` years, gender = `r round(male_t1_m, 2)*100`% male, college degree = `r round(college_t1_m, 2)*100`%.
T2: age = `r round(age_final_m, 0)` years, gender = `r round(male_final_m, 2)*100`% male, college degree = `r round(college_final_m * 100, 0)`%.
One participant did not report their gender.

## Measures

<!-- Wherever possible, I operationalized the variables using established measures. -->
<!-- Where impossible (for example, to date there exists no scale on privacy deliberation), I self-designed novel items, which were pretested concerning legibility and understandability. -->
Factor validity was assessed using confirmatory factor analyses (CFA). 
If the CFAs revealed insufficient fit, malfunctioning items were deleted.
All items were measured on bipolar 7-point scales. 
Answer options were visualized as follows: -3 (_strongly disagree_), -2 (_disagree_), -1 (_slightly disagree_), 0 (_neutral_), +1 (_slightly agree_), +2 (_agree_), +3 (_strongly agree_). 
For the analyses, answers were coded from 1 to 7.
All items measuring the same variable were presented in randomized order on the same page.

All measures showed high factorial validity. For an overview of the means, standard deviations, factorial validity, and reliability, see Table \@ref(tab:CFA). 
For the variables' distributions, see Figure \@ref(fig:corrplot). 
For the exact wording of all items and their individual distributions, see [companion website](https://XMtRa.github.io/like_dislike).

```{r CFA, results = "asis"}
apa_table(
  facval_tab %>% 
    select(-alpha) %>% 
    rename(`p-value` = pvalue), 
  font_size = "footnotesize",
  caption = "Psychometric Properties, Factorial Validity, and Reliability of Measures",
  note = "omega = Raykov's composite reliability coefficient omega; avevar = average variance extracted."
  )
```

<!-- ### Privacy concerns -->

_Privacy concerns_ were measured with seven items based on @buchananDevelopmentMeasuresOnline2007.
One example item was "When using the participation platform, I had concerns about my privacy". 
One item was deleted due to poor psychometric properties.

<!-- ### Gratifications -->

Two types of gratifications were collected.
_General gratifications_ were measured with five items based on @sunLocationInformationDisclosure2015.
One example item was "Using the participation platform has paid off for me". 
Based on @schererGratifikationMinuteZeitnahe2002, _specific gratifications_ were measured on five dimensions with three items each. 
Example items were: "Using the participation platform made it possible for me to" ... "learn things I would not have noticed otherwise" (information), "react to a subject that is important to me" (relevance), "engage politically" (political participation), "try to improve society" (idealism), and "soothe my guilty consciences" (extrinsic benefits).

<!-- ### Privacy deliberation -->

_Privacy deliberation_ was measured with five self-designed items. 
One example item was "While using the participation platform I have weighed the advantages and disadvantages of writing a comment."

<!-- ### Self-efficacy -->

_Self-efficacy_ was captured with six self-designed items, which measured whether participants felt that they had sufficient self-efficacy to write a comment on the website. 
For example, "I felt technically competent enough to write a comment." 
Two inverted items were deleted due to poor psychometric properties.

<!-- ### Trust -->

Two types of trust were measured.
_General trust_ was operationalized based on @sollnerWhyDifferentTrust2016, addressing three targets (i.e., provider, website, and other users), measured with one item each. 
One example item was "The operators of the participation platform seemed trustworthy."
_Specific trust_ was operationalized for the same three targets with three subdimensions each (i.e., ability, benevolence/integrity, and reliability), measured with one item each. 
Example items were "The operators of the participation platform have done a good job" (ability), "The other users had good intentions" (benevolence/integrity), "The website worked well" (reliability). 
Because they were closely related, the two targets "provider" and "website" were combined into one dimension. 
<!-- , as was evidenced by a Heywood case (i.e., standardized coefficient greater than 1).  -->
<!-- I hence adapted the scale to combine these two targets.  -->
The updated scale showed adequate fit.

_Communication_ was calculated by counting the number of words each participant wrote in a comment.
Communication was zero-inflated and heavily skewed.
While `r round(no_words_perc * 100, 0)` percent did not communicate at all, some communicated a lot.
On average, participants wrote `r words_m %>% round(0)` words.

## Data analysis

As preregistered, all hypotheses and research questions were initially tested using structural equation modeling with latent variables. 
The influence of the three websites was analyzed using contrast coding.
<!-- I could therefore test the effects of experimental manipulations within a theoretical framework while using latent variables [@klinePrinciplesPracticeStructural2016].  -->
Because the assumption of multivariate normality was violated, I estimated the models using robust maximum likelihood [@klinePrinciplesPracticeStructural2016]. 
As recommended by @klinePrinciplesPracticeStructural2016, to assess global fit I report the model's $\chi^2$, RMSEA (90% CI), CFI, and SRMR. 
To exclude confounding influences, I controlled all variables for age, gender, and education, which were shown to affect both privacy concerns and online communication [@masurUnderstandingEffectsConceptual2023; @tifferetGenderDifferencesPrivacy2019a].
Preregistered hypotheses were tested with a one-sided significance level of 5%. 
Research questions were tested with a two-sided 5% significance level using family-wise Bonferroni-Holm correction.

As became apparent when analyzing the data, the preregistered analyses had two major problems.
First, communication was zero-inflated and gamma distributed. 
Although it is possible to analyze non-normal data with structural equation modeling, it is recommended to use analyses that model the variables' distribution, which can be done with Bayesian hurdle models [@mcelreathStatisticalRethinkingBayesian2016].
I conclusion, in the exploratory analyses I ran Bayesian hurdle regression models, modeling the outcome as a zero-inflated gamma distribution.
Second, in the preregistered analyses several variables were combined that are theoretically and empirically closely related, leading to multicollinearity [@vanhoveCollinearityIsnDisease2021].
As a remedy, I adopted a causal modeling perspective, controlling only for confounders---in this case, age, gender, and education---but not for mediators [@rohrerThinkingClearlyCorrelations2018]. 
To assess the effects, I tested whether or not the 95% credibility intervals of the average marginal effects excluded zero.
If they excluded zero, effects can be considered "significant" [@mcelreathStatisticalRethinkingBayesian2016]. 
I also plotted the distribution of the effects.
For more information, see online supplementary material.

<!-- Exploratory analyses were conducted from a descriptive perspective. -->
<!-- The reported p-values and confidence intervals should thus not be overinterpreted. -->

The data were analyzed using `r r_citations`.

# Results

## Descriptive Analyses

```{r PriDel}
# calc participants who actively deliberated
pridel_active <- select(d, starts_with("PD01")) %>% 
  as.data.frame %>% 
  mutate(m = apply(., 1, mean, na.rm = T) %>% round(0)) %>% 
  select(m) %$% 
  nrow(filter(., m > 4)) / n_final * 100
```

```{r corrplot, fig.cap="Above diagonal: zero-order correlation matrix; diagonal: density plots for each variable; below diagonal: bivariate scatter plots for zero-order correlations. Solid regression lines represent linear regressions, dotted regression lines represent quadratic regressions. Calculated with the model predicted values for each variable (baseline model).", fig.height=8, fig.width=8, out.width=".9\\textwidth", fig.align='center', fig.pos = "!h", warning=F}
knitr::include_graphics("figures/results/cor_plot.png")
```

I first measured and plotted all bivariate relations between the study variables (see Figure \@ref(fig:corrplot)). 
<!-- No relationship was particularly curvilinear.  -->
All variables referring to the privacy calculus demonstrated the expected bivariate relationships with communication. 
For example, people who were more concerned about their privacy disclosed less information (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "pri_con" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")`). 
Specific gratifications predicted communication better than general gratifications (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_spec" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")` vs. _r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_gen" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")`).
The mean of privacy deliberation was _m_ = `r des_pridel$m %>% round(2)`. 
Altogether, `r pridel_active %>% round(0)`% of participants reported having actively deliberated about their privacy.

The bivariate results showed three large correlations: 
specific trust and general gratifications (_r_ = `r d_fs %>% select("Specific\ntrust", "General\ngratifications") %>% cor %>% .[2, 1] %>% my_round("std")`), 
privacy concerns and privacy deliberation (_r_ = `r d_fs %>% select("Privacy\nconcerns", "Privacy\ndeliberation") %>% cor %>% .[2, 1] %>% my_round("std")`),
and specific gratifications and self-efficacy (_r_ = `r d_fs %>% select("Specific\ngratifications", "Self-\nefficacy") %>% cor %>% .[2, 1] %>% my_round("std")`). 
As all six variables were later analyzed within a single multiple regression, problems of multicollinearity might occur.

## Preregistered analyses

First, as preregistered I ran a structural equation model with multiple predictors. 
The model fit the data okay, `r fit_txt(fit_prereg, scaled = TRUE)`. 
Regarding H1, results showed that gratifications did not predict communication (`r coeffs_txt(fit_prereg, "a1", one_sided=T)`; one-sided). 
With regard to H2, privacy concerns did not significantly predict communication (`r coeffs_txt(fit_prereg, "b1", one_sided=T)`; one-sided). 
RQ1 similarly revealed that privacy deliberation did not predict communication (`r coeffs_txt(fit_prereg, "c1")`; two-sided). 
Regarding H3, however, I found that experiencing self-efficacy predicted communication substantially (`r coeffs_txt(fit_prereg, "d1", one_sided=T)`; one-sided). 
Concerning H4, results showed that trust was not associated with communication (`r coeffs_txt(fit_prereg, "e1", one_sided=T)`; one-sided).

However, these results should be treated with caution.
I found several signs of multicollinearity, as evidenced by the large standard errors or "wrong" and reversed signs of predictors [@vanhoveCollinearityIsnDisease2021]. 
For example, in the bivariate analysis trust had a _positive_ relation with communication, whereas in the multiple regression the effect was _negative_---which should make us wary.

Next, I analyzed the effects of the popularity cues. 
It was for example expected that websites with like buttons would lead to more communication, more gratifications, more privacy deliberation, and to less privacy concerns.
The results showed that the popularity cues had no effects on communication and on the privacy calculus variables.
For an illustration, see Figure \@ref(fig:popularitycues). 
<!-- The results show that the confidence intervals of all preregistered variables overlap, illustrating that there were no statistically significant differences across websites. -->
For the detailed results of the specific inference tests using contrasts, see [companion website](https://XMtRa.github.io/like_dislike).

```{r popularitycues, fig.cap="Overview of the model-predicted values for each variable, separated for the three websites. Control: Website without buttons. Like: Website with like buttons. Like \\& Dislike: Website with like and dislike buttons.", out.width = "\\textwidth", fig.pos = "!h"}
knitr::include_graphics("figures/results/violin_plot.png")
```

## Exploratory analyses

As explained above, the preregistered results were problematic, because communication was not normally distributed and because the predictors were collinear.
I hence ran updated analyses, using Bayesian hurdle models, controlling only for confounders but not mediators.
The updated exploratory analyses showed different results.

Hypotheses 1, 2, 3, and 4 were all confirmed:
If participants expected more gratifications from participation, they communicated more: 
If their expected gratifications increased by one point, on average they also wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(Estimate) %>% round(0)` more words (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(UL) %>% round(0)`). 
If participants were more concerned about their privacy, they communicated less: 
With each one-point increase in privacy concerns, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(Estimate) %>% round(0) %>% abs()` fewer words (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(UL) %>% round(0)`).
If participants felt more self-efficacious, they also communicated much more:
If their self-efficacy increased by one point, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Self-efficacy") %>%  select(Estimate) %>% round(0)` more words (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Self-efficacy") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Self-efficacy") %>%  select(UL) %>% round(0)`).
The relationship was curvilinear, almost exponential: 
Whereas a change in self-efficacy from 1 to 2 only led to an "increase" of `r effects_wrds_selfeff_12 %>% round(0) %>% unlist %>% english()` words, a change from 6 to 7 led to an increase of `r effects_wrds_selfeff_67 %>% round(0)` words.
And if participants experienced more trust in the website, provider, and other users, they also communicated much more:
If their trust increased by one point, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Trust") %>%  select(Estimate) %>% round(0)` more words (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Trust") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Trust") %>%  select(UL) %>% round(0)`).
The first research question asked how privacy deliberation would affect communication.
The results revealed a negative effect. 
The more people deliberated about their privacy, the less they communicated.
If privacy deliberation increased by one point, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy deliberation") %>%  select(Estimate) %>% round(0) %>% abs()` less words (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy deliberation") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy deliberation") %>%  select(UL) %>% round(0)`).

I then reanalyzed the effects of the popularity cues on communication.
Compared to the control condition without popularity cues, implementing like buttons did not significantly affect communication, _b_ = `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like vs.control") %>%  select(Estimate) %>% round(0)` (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like vs.control") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like vs.control") %>%  select(UL) %>% round(0)`).
However, implementing both like and dislike buttons affected communication.
Contrary to what I expected, implementing both popularity cues did not increase but rather decreased communication.
If both popularity cues were present, participants on average wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like & dislike vs.control") %>%  select(Estimate) %>% round(0) %>% abs()` words less (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like & dislike vs.control") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like & dislike vs.control") %>%  select(UL) %>% round(0)`).
The introduction of both cues hence led to a `r effect_lkdlk_prcnt %>% as.integer()`% decline in number of words that were written.

Finally, I tested if the effect of the popularity cues on communication were potentially mediated by the privacy calculus variables. 
Results showed that this was not the case (see online companion material),
<!-- Additional analyses showed that the popularity cues did not affect the privacy calculus' variables of privacy concerns, gratifications, trust, self-efficacy, or privacy deliberation.  -->
suggesting that the effect was either direct or mediated by other variables not included here [@coenenIndirectEffectOmitted2022].

```{r slopes, fig.cap="Exploratory analyses. Plotted are the average marginal effects of the Bayesian hurdle models. The difference between the control group and like \\& disklike is significant.", fig.height=8, fig.width=8, out.width=".9\\textwidth", fig.align='center', fig.pos = "!h", warning=F}
knitr::include_graphics("figures/results/effects.png")
```

```{r results}
apa_table(tab_slopes %>% 
            filter(Outcome == "words") %>% 
            select(-Outcome)
          , stub_indents = list(
            "Privacy calculus" = c(1:5),
            "Experimental conditions" = c(6:8)
          ) 
          , col_spanners = list(
            "CI" = c(3, 4)
          )
          , font_size = "footnotesize"
          , caption = "Effects of the privacy calculus variables and the popularity cues on communication. Credibility intervals exluding zero are considered significant."
          , note = "CI = credibility interval, LL = lower level; UL = upper level. Reported are average marginal effects."
          # , align = c("l{5cm}rrr")
          # , align = c("p{6cm}", rep("r", 3))
          , digits = 0
          )
```

# Discussion

This study analyzed whether like and dislike buttons would affect online communication and the privacy calculus.
To this end, a preregistered field experiment was conducted, which lasted one week.
<!-- and that produced actual behavioral data. -->
Furthermore, the privacy calculus model was extended.
The privacy deliberation processes was tested explicitly, and trust and self-efficacy were added as predictors.

The preregistered analyses showed that the popularity cues did not affect communication. 
Only trust emerged as a significant predictor of online communication.
All other variables remained insignificant.
However, these analyses need to be treated with caution.
The predictors were collinear, which makes their integration in one single model problematic [@vanhoveCollinearityIsnDisease2021].
<!-- Confidence intervals are inflated and the interpretation becomes difficult . -->
In addition, the main variable and outcome of the study, number of communicated words, was zero-inflated and gamma distributed, requiring a different type of analysis.
The preregistered analyses using structural equation modeling with multiple predictors were hence subpar.

To address these shortcoming, in several exploratory analyses I conducted Bayesian hurdle-gamma models (see Data analysis).
<!-- To account for the data's distribution, I now ran Bayesian hurdle-gamma models,  -->
<!-- and to address multicollinearity, I adopted a causal modeling perspective by controlling for confounders but not for mediators [@rohrerThinkingClearlyCorrelations2018]. -->
This updated approach changed the results.
People who were more concerned about their privacy wrote significantly less words. 
To illustrate, people who reported being very much concerned posted only `r wrds_pricon_7` words on average, whereas people who reported being not concerned posted `r wrds_pricon_1` words.
Participants who received more gratifications wrote substantially more words, too.
Together, the results provide further support for the privacy calculus and against the privacy paradox [@dienlinPrivacyParadoxAus2019].
Communication online does not seem to be overly illogical. 
To large extents, it is aligned with respondents' concerns and benefits.

Results showed that trust and self-efficacy are important drivers of online communication.
Participants who placed more trust into the website, the providers, and the other community members communicated more actively.
Self-efficacy was the strongest of all predictors.
Participants who felt more self-efficacious disclosed much more than others.
To illustrate, if people reported no self-efficacy, they wrote only `r wrds_selfeff_1` words on average.
However, when they reported high levels of self-efficacy, they wrote `r wrds_selfeff_7` words.
<!-- In conclusion, trust and efficacy play an important role when it comes to online communication. -->
This finding further supports the underlying premise of bounded rationality [@simonBoundedRationality1990].
Although more rational aspects such as costs and benefits influence behavior, behavior is also determined by more psychosocial variables such as trust and efficacy.

The privacy calculus was criticized for not explicitly analyzing the process of weighing pros and cons before disclosing [@knijnenburgDeathPrivacyCalculus2017].
In this study, I thus elaborated on the privacy deliberation process.
The results showed that only one third of all participants agreed to have actively weighed the benefits and drawbacks before communicating on the platform.
The figure is comparatively low.
Even in new online contexts, the majority of users does not seem to actively deliberate about their online communication, suggesting that online use is to large extents implicit [@acquistiSecretsLikesDrive2020].

Privacy deliberation and privacy concerns were strongly correlated (_r_ = .61), showing comparable correlations with other variables. 
If we are concerned, we also think and deliberate more about our privacy. 
And if we are not concerned, we do not deliberate.
This finding is aligned with decision theory [@elsbachEffectsMoodIndividuals1999].
When in a negative state---such as when being concerned---, we judge more critically.
And when in a positive mood, we are more lenient. 
At this point, it is still unknown if thinking about privacy increases concerns or, conversely, if growing more concerned about privacy encourages us to deliberate more carefully. 
<!-- Future research might tell. -->

The updated results showed that implementing both like and dislike buttons decreased communication. 
This was an unexpected and interesting finding.
It suggest that negative feedback, or even only the risks of receiving negative feedback, stifles communication. 
The effect was strong: Implementing both like and dislikes cues led to a `r effect_lkdlk_prcnt %>% as.integer()`% decrease in number of written words.
This finding is aligned with studies that reported strong effects of popularity cues on behavior [@muchnikSocialInfluenceBias2013]. 
The negative effects of dislike buttons might explain why almost all existing and successful social network sites have chosen to omit such negative popularity cues. 
At the time of writing, only a handful of websites have (partially) implemented dislike buttons (e.g., youtube, stackexchange, or reddit).
Despite the positivity bias of social media [@schreursExposurePositivityBias2022], chances of receiving negative feedback and communication are of course real, as can be seen by moral outrages or "shit-storms".
Explicit negative popularity cues are low threshold paralinguistic affordances [@carrPredictingThresholdPerceived2018].
They likely prime or trigger negative experiences or expectations, thereby reducing communication.

Websites only with like buttons had no effect on the number of communicated words. 
If anything, there was an unexpected (nonsignificant) trend toward reduced communication.
Although we would expect that like buttons, being positive feedback cues, would increase communication, it also seems plausible that they can decrease communication.
<!-- there might be contexts and scenarios where this is not the case. -->
Not receiving any likes, although the option exists, can be perceived as ostracizing [@schneiderSocialMediaOstracism2017].
In the context of this study, participants discussed a political topic.
Not receiving likes might be more threatening and intimidating than on regular social media, on which it is more common to discuss every-day topics.
Although like buttons are commonplace in social media, the findings suggests that in specific contexts they inhibit communication.

<!-- Next to these theoretical and practical implications, the study has also several methodological ones. -->
<!-- First, when analyzing extended privacy calculus models, aspects of multicollinearity need to taken into account.  -->
<!-- Trust and self-efficacy are highly related, as privacy concerns and privacy deliberation. -->
<!-- Hence, when estimating their causal effect on communication, they should not be combined in one single model. -->
<!-- Instead, they should only be controlled for confounding variables. -->
<!-- Finally, when analyzing count data, it is recommended to implement models that can explicitly account for the data's distribution. -->

<!-- The results also have methodological implications.  -->
<!-- First, one can question the tendency to further increase the complexity of the privacy calculus model by adding additional variables [e.g., @dienlinExtendedPrivacyCalculus2016a].  -->
<!-- "Since all models are wrong the scientist cannot obtain a "correct" one by excessive elaboration. [...] Just as the ability to devise simple but evocative models is the signature of the great scientist so overelaboration and overparameterization is often the mark of mediocrity" [@boxScienceStatistics1976, p. 792].  -->
<!-- For example, it seems that adding self-efficacy to privacy calculus models is of limited theoretical value. -->
<!-- Self-efficacy is often only a self-reported proxy of behavior and offers little incremental insight.  -->
<!-- Instead, it might be more interesting to find out _why_ some people feel sufficiently efficacious to communicate whereas others do not.  -->

<!-- In addition, although adding variables increases explained variance, it can also introduce multicollinearity. -->
<!-- Multicollinearity is not a problem per se, but rather a helpful warning sign [@vanhoveCollinearityIsnDisease2021]. -->
<!-- From a _statistical_ perspective, strongly correlated predictors mean that standard errors become larger [@vanhoveCollinearityIsnDisease2021].  -->
<!-- We can be less certain about the effects, because there is less unique variance [@vanhoveCollinearityIsnDisease2021].  -->
<!-- As a remedy, researchers could collect larger samples, which would increase statistical power and precision. -->
<!-- Using accessible statistical software it is now possible to run a priori power analyses that explicitly account for correlated or collinear predictors [@wangPowerAnalysisParameter2020]. -->

<!-- From a _theoretical_ perspective, multicollinearity could also suggest that the underlying theoretical model is ill-configured. -->
<!-- It is my understanding that multiple regression is often used to isolate effects, to make sure that they are not caused by other third variables. -->
<!-- However, in cases of highly correlated variables this often does not make much sense theoretically. -->
<!-- Combining trust and gratification in a multiple regression asks how increasing benefits affects communication _while holding trust constant_. -->
<!-- However, it seems more plausible to assume that increasing gratifications also automatically increases trust [@sollnerWhyDifferentTrust2016]. -->
<!-- In the preregistered analysis I even went further and tested whether trust increases communication while holding constant gratifications, privacy concerns, privacy deliberations, and self-efficacy---an unlikely scenario.  -->
<!-- In short, the effects I found could be correct, but the interpretation is more difficult, potentially artificial, and thereby of little theoretical and practical value. -->
<!-- In short, analyses with multicolinear predictors provide the correct answer to the wrong question. -->

<!-- Finally, I found a surprisingly strong correlation between specific trust and expected gratifications (i.e., _r_ = .79). -->
<!-- Operationalizations of trust are remarkably close to expected gratifications.  -->
<!-- To illustrate, the trust subdimension _ability_ includes items such as “The comments of other users were useful”.  -->
<!-- Trust is often operationalized as a formative construct that directly results from factors such as expected benefits [@sollnerWhyDifferentTrust2016].  -->
<!-- In conclusion, it is important not to confuse _causes_ of trust with _measures_ of trust. -->
<!-- <!-- Doing so can introduce problems of homogeneity and multicollinearity. -->
<!-- I thus recommend using general and reflective measures of trust. -->

## Limitations

The main implications and results discussed above rest on exploratory analyses not registered a priori.
Exploratory analyses are part of the research process, compatible with preregistration, and important for scientific progress [@dienlinAgendaOpenScience2021].
<!-- Preregistration does not prevent exploration. -->
The updated analyses represent and document a learning process, which arguably led to an improved analysis.
However, the results should still be considered preliminary, to be confirmed in subsequent studies.

Whereas the effects of the popularity cues on all variables can be interpreted from a causal perspective (but see below), more caution is needed when regarding the effects of the privacy calculus variables on communication.
Although the effects were controlled for age, gender, and education, other variables not included here might exist that potentially bias the causal estimates presented here [@coenenIndirectEffectOmitted2022].
<!-- The results do not allow for causal interpretation.  -->
<!-- First, all results are based on analyses of between-person variance. -->
<!-- However, between-person relations often do not translate to within-person effects [@hamakerCritiqueCrosslaggedPanel2015].  -->
<!-- While some studies on privacy concerns online have begun to examine both sources of variance [@dietvorstAdolescentPerceptionsParental2017], similar analyses are still lacking for the privacy calculus.  -->
<!-- Likewise, the mediation model is only suggestive, as I did not experimentally manipulate the mediating variables and also did not use a longitudinal design. -->
<!-- However, note that in all these analyses,  -->
<!-- Hence, the aforementioned relations cannot be explained by the fact that for example females are more concerned about their privacy while communicating less online. -->

<!-- Although I did not find significant effects of like and dislike buttons in this study, they could still affect the privacy calculus in other contexts and settings. -->
<!-- All findings are limited to the context I analyzed and should not be overly generalized. -->
<!-- Null-findings pose the *Duhème-Quinn Problem* [@dienesUnderstandingPsychologyScience2008]. -->
<!-- They can either result from an actual non-existence of effects or, instead, from a poor operationalization of the research question.  -->
<!-- In this case, it was not possible to send participants notifications when their comments were liked or disliked, which significantly decreased the popularity cues' salience. -->

<!-- The self-reported measures were collected _after_ the field phase in which the dependent variable was measured.  -->
<!-- As a result, the coefficients might overestimate the actual relations, because demand effects might have led participants to artificially align their theoretical answers with their practical behavior.  -->

In experiments only the treatment variable should be manipulated, while all others should be held constant [assumption of stable unit treatment, @klinePrinciplesPracticeStructural2016]. 
<!-- In this study, I explicitly manipulated the popularity cues.  -->
Being a field experiment, several variables could not be held constant, such as the content of communication by other users, the unfolding communication dynamics, and the characteristics of other users.
Future research should repeat the design, preferably using several runs of the same experiment, to further assess generalizability and robustness.
<!-- As a result, the assumption of stable unit treatment was violated. -->

## Conclusion

This study provides further support for the privacy calculus model and against the privacy paradox approach.
Expected benefits, privacy concerns, comparing benefits and drawbacks, trust, and self-efficacy all affected communication.
<!-- People who were more concerned about their privacy communicated less actively online, whereas people who received more gratifications communicated more. -->
<!-- The more people compared pros and cons, they less they communicated. -->
<!-- Trust and self-efficacy were also major drivers of communication.  -->
Like and dislike buttons reduced communication significantly.
<!-- In conclusion, the results provide further evidence against the privacy paradox. -->
Users can be considered proactive and reasonable.
But, similar to everyday offline contexts, users are also affected by the affordances of their environment, often acting implicitly.

\newpage

# References

### 2023-04-11 preregistration_changes.rmd
- initalize repo

---
title: "Changes From Preregistration"
output: "html_document"
---

The preregistration can be found [here](https://osf.io/a6tzc/?view_only=5d0ef9fe5e1745878cd1b19273cdf859). In what follows, we present where we decided to deviate from the preregistration.

# Theoretical Background

In general, instead of analyzing _self-disclosure_, we're now analyzing communication behavior. Before, we tried to operationalized self-disclosure with the log of communication frequency plus likes and dislikes. However, we realized that this operationalization is too coarse to represent self-disclosure. We now analyze the mere quantity of communication, which is much less debatable.

## Hypotheses

 -	We've changed the order of the hypotheses.
 -	We've changed the wording of the hypotheses (but not the content).
 -  We've changed the enumeration of the hypotheses. 
    - Before, hypotheses were enumerated from 1-13.
    - Now, it's 1, 2, 3, 4, 5a, 5b, 5c, 5d, 6a, 6b, 6c, 7a, 7b.

## Research Question

 -  We dropped two Research Questions, because we realized that they just didn't make sense. That is, we dropped the RQ that popularity cues might affect self-efficacy and trust

# Methods
## Participants
### Exclusion criteria

Initially, we planned to exclude all participants who finished the questionnaire in less than 6 minutes. However, this would lead to the deletion of participants who provided answers that seemed perfectly fine. In conclusion, we relaxed the criterion to 3 minutes, which led to the exclusion of 27 participants. Results changed only marginally and do not hinge on exclusion (see additional analyses).

# Material
## Expected Benefits

In the preregistration, we stated that we would measure expected benefits by means of 5 general items (“Using the participation platform had many benefits for me”). However, we had also designed additional items for more specific gratifications that we did not include in the preregistration (the preregistration manual stated that additional variables that one does not plan to analyze do not need to be preregistered). These specific measures of gratifications were hence used for exploratory analyses.

## Trust

Originally, we operationalized trust for three entities (i.e., provider, website, and other users) using four subdimensions (i.e., general trust, ability, benevolence, and integrity). Only later did we realize that the literature differentiates between general and specific trust beliefs, which we could conceptualize with the items we measured. As a result, in the paper we now differentiate both dimensions.

# Results

- Given that we found not apparent effects of the three websites on the privacy calculus, we did not test for indirect effects as proposed in the preregistration. 
- We additionally also controlled for education (we forgot to explicitly mention this control variable in the preregistration; results do not differ, but we think it should be included, which is why we did).

# Power analyses

In the preregistration, power analyses were conducted assuming 80% statistical power. However, in the meantime we have come to believe that in most cases and if logistically possible we should strive for balanced alpha and beta errors, which given an alpha of 5% leads to a desired power of 95%. As a result, we report power analyses aiming for 95% power.

# Inferences

In the preregistration, we stated that we would analyze the additional exploratory analyses using Bonferroni-Holm correction. However, in the meantime we have come to understand that formal inferences tests for exploratory analyses are debatable, for example because the number of tests one could potentially account for is infinite. Instead, we decided not to make strong inferences on the basis of the exploratory analyses, and report p-values / confidence intervals only descriptively as a measure of precision.

### 2023-04-11 analyses_explorations.R

@@ -1,0 +1,241 @@
+#### Preregistered
+
+```{r}
+fit_brms_hrdl_prereg <- 
+  brm(
+    bf(
+      COMM ~ 
+        1 + 
+        pri_con_fs + 
+        grats_spec_fs + 
+        pri_del_fs + 
+        trust_gen_fs +
+        self_eff_fs +
+        age + 
+        male + 
+        edu, 
+      hu ~ 
+        1 + 
+        pri_con_fs + 
+        grats_spec_fs + 
+        pri_del_fs + 
+        trust_gen_fs +
+        self_eff_fs +
+        age + 
+        male + 
+        edu
+    ), 
+    data = d, 
+    family = hurdle_gamma()
+  )
+
+```
+
+
+```{r}
+plot(fit_brms_hrdl_prereg, ask = FALSE)
+```
+
+```{r}
+model_diagnostics(fit_brms_hrdl_prereg)
+```
+
+```{r}
+summary(fit_brms_hrdl_prereg)
+```
+
+```{r}
+conditional_effects(fit_brms_hrdl_prereg, ask = FALSE)
+```
+
+#### Adapted
+
+```{r}
+fit_brms_hrdl_adapted <- 
+  brm(
+    bf(
+      COMM ~ 
+        1 + 
+        pri_con_fs + 
+        grats_spec_fs + 
+        pri_del_fs + 
+        self_eff_fs +
+        age + 
+        male + 
+        edu, 
+      hu ~ 
+        1 + 
+        pri_con_fs + 
+        grats_spec_fs + 
+        pri_del_fs + 
+        self_eff_fs +
+        age + 
+        male + 
+        edu
+    ), 
+    data = d, 
+    family = hurdle_gamma()
+  )
+
+```
+
+
+```{r}
+plot(fit_brms_hrdl_adapted, ask = FALSE)
+```
+
+```{r}
+model_diagnostics(fit_brms_hrdl_adapted)
+```
+
+```{r}
+summary(fit_brms_hrdl_adapted)
+```
+
+```{r}
+conditional_effects(fit_brms_hrdl_adapted, ask = FALSE)
+```
+
+#### 3-way Interaction
+
+```{r}
+fit_brms_hrdl_inter <- 
+  brm(
+    bf(
+      COMM ~ 
+        1 + 
+        pri_con_fs_c * 
+        grats_spec_fs_c * 
+        pri_del_fs_c + 
+        self_eff_fs_c +
+        age_c + 
[…]

### 2023-04-11 manuscript.RmD
- added html

@@
 classoption       : "man"
-output            : papaja::apa6_pdf
-header-includes:
-  - \setlength{\parskip}{0em}
-  - \raggedbottom
-  - \note{\clearpage}
+# output            : papaja::apa6_pdf
+# header-includes:
+#   - \setlength{\parskip}{0em}
+#   - \raggedbottom
+#   - \note{\clearpage}
 # output            : papaja::apa6_docx
-# output:
-#   html_document:
-#     toc: TRUE
-#     toc_float:
-#       collapsed: FALSE
-#     toc_depth: 2
+output:
+  html_document:
+    toc: TRUE
+    toc_float:
+      collapsed: FALSE
+    toc_depth: 2
 ---

### 2023-04-12 analyses.Rmd
- Language updates

@@
         "Like", 
-        "Like & Dislike"
+        "Like & dislike"
         )
@@
       levels = c(
-        "Like & Dislike", 
+        "Like & dislike", 
         "Like", 
@@
       "Like" = 2, 
-      "Like & Dislike" = 3
+      "Like & dislike" = 3
       ),
@@
       "Like" = 1, 
-      "Like & Dislike" = 0
+      "Like & dislike" = 0
       ),
@@
       "Like" = 0, 
-      "Like & Dislike" = 1
+      "Like & dislike" = 1
       ),
@@
       "Like" = 0, 
-      "Like & Dislike" = 0
+      "Like & dislike" = 0
       ),
@@
   fig_wrds_ctrl$data %>% 
-  filter(effect1__ == "Like & Dislike") %>% 
+  filter(effect1__ == "Like & dislike") %>% 
   select(estimate__)
@@
       ifelse(
-        .$contrast == "Like & Dislike - Control", 
-        "Like & Dislike - Control",
+        .$contrast == "Like & dislike - Control", 
+        "Like & dislike - Control",
         ifelse(
-          .$contrast == "Like - Like & Dislike", 
-          "Like - Like & Dislike", 
+          .$contrast == "Like - Like & dislike", 
+          "Like - Like & dislike", 
           .$term
@@
       term, 
-      "Like - Control" = "Like vs.control",
-      "Like & Dislike - Control" = "Like & dislike vs.control",
-      "Like - Like & Dislike" = "Like vs.like & dislike",
+      "Like - Control" = "Like vs. control",
+      "Like & dislike - Control" = "Like & dislike vs. control",
+      "Like - Like & dislike" = "Like vs. like & dislike",
       "pri_con_fs" = "Privacy concerns",
@@
     Predictor %in% c(
-      "Like vs.control",
-      "Like & dislike vs.control",
-      "Like vs.like & dislike",
+      "Like vs. control",
+      "Like & dislike vs. control",
+      "Like vs. like & dislike",
       "Privacy concerns",
@@
       "Privacy concerns",
-      "Like vs.like & dislike",
-      "Like & dislike vs.control",
-      "Like vs.control"
+      "Like vs. like & dislike",
+      "Like & dislike vs. control",
+      "Like vs. control"
       )

### 2023-04-12 index.Rmd
- Language updates

@@
 
-On this website, you can find the companion material for the paper _Like or Dislike, Gratifications or Concerns? Analyzing Popularity Cues and Privacy Calculus in Online Communication_.
+On this website, you can find the companion material for the paper _Likes or Dislikes, Gratifications or Concerns?
+Analyzing the Effects of Popularity Cues on the Privacy Calculus in Online Communication_.
 

### 2023-04-12 manuscript.RmD
- Language updates

--- 2023-04-11 manuscript.RmD
@@
 ---
-title             : "Likes or Dislikes, Gratifications or Concerns? Analyzing Popularity Cues and Privacy Calculus in Online Communication"
+title             : "Likes or Dislikes, Gratifications or Concerns? Analyzing the Effects of Popularity Cues on the Privacy Calculus in Online Communication"
 
@@
 abstract: |
-    According to the privacy calculus model, online communication is mainly determined by the two factors of privacy concerns and expected benefits.
-This paper analyzes how the privacy calculus is affected by popularity cues, namely like and dislike buttons.
-In addition, the privacy calculus is extended by elaborating on the process of comparing benefits and drawbacks, termed privacy deliberation, and by investigating the role of trust and self-efficacy.
+    According to the privacy calculus model, online communication is determined by two factors, privacy concerns and expected benefits.
+How is the privacy calculus affected by external affordances, for example popularity cues such as like and dislike buttons?
+And should the privacy calculus model be extended by integrating more socio-psychological measures such as trust, self-efficacy, and privacy deliberation?
 To this end, a preregistered one-week field experiment with 590 participants was conducted.
 Participants were randomly distributed to three different websites, on which they discussed a current political topic.
-The websites featured either (a) like buttons, (b) both like and dislike buttons, or (c) no like or dislike buttons.
-The exploratory analyses revealed, contrary to what was expected, that implementing both like and dislike buttons decreased online communication.
+The websites included either (a) like buttons, (b) both like and dislike buttons, or (c) no like or dislike buttons.
+Because of multicollinearity and non-normal distribution of the outcome, the preregistered analyses needed to be updated.
+The results revealed that implementing both like and dislike buttons decreased online communication by 44%.
 As predicted by the privacy calculus model, expected benefits and perceived privacy concerns substantially affected communcation.
@@
 <!-- Rather than further pursuing the privacy paradox,  -->
-Research is therefore increasingly building on the privacy calculus model, which states that communication online can be explained successfully by means of perceived risks and expected benefits [@bolUnderstandingEffectsPersonalization2018b; @krasnovaOnlineSocialNetworks2010; @meierPrivacyCalculusRevisited2022].
+Research is therefore increasingly building on the privacy calculus model, which states that communication online can be explained successfully by perceived risks and expected benefits [@bolUnderstandingEffectsPersonalization2018b; @krasnovaOnlineSocialNetworks2010; @meierPrivacyCalculusRevisited2022].
 <!-- Several studies have shown that experiencing more privacy risks or concerns is related to sharing less information online [@bolUnderstandingEffectsPersonalization2018b; @meierPrivacyCalculusRevisited2022], while expecting more benefits is related to sharing more information online [@heirmanPredictingAdolescentsDisclosure2013; @koohikamaliInvestigationDynamicModel2019].
@@
 Although the privacy calculus has gained momentum in academic research, several important questions remain unanswered. 
-First, we still know little about how the privacy calculus and online communication can be affected by external influences [@bazarovaIntegrationIndividualisticNetworked2020; @braunlichLinkingLooseEnds2020].
-For example, does the existence of popularity cues such as like and dislike buttons affect the privacy calculus and online communication?
+First, we still know little about how the privacy calculus and online communication can be affected by external affordances [@bazarovaIntegrationIndividualisticNetworked2020; @braunlichLinkingLooseEnds2020].
+For example, do popularity cues such as like and dislike buttons affect the privacy calculus and online communication?
 <!-- I therefore analyze whether the privacy calculus is affected by the affordances of a website.  -->
@@
 To date, much research on the privacy calculus builds on (a) self-reports of behavior [@krasnovaOnlineSocialNetworks2010], (b) vignette approaches [@bolUnderstandingEffectsPersonalization2018b], or (c) one-shot experiments in the lab [@treptePrivacyCalculusContextualized2020].
-Can the privacy calculus be replicated in an authentic and more long-term setting using actual behavioral data?
+Can the privacy calculus be replicated in more authentic and long-term settings using actual behavioral data?
 Third, research on the privacy calculus so far did not measure the actual process of weighing pros and cons [@knijnenburgDeathPrivacyCalculus2017], 
@@
 <!-- In this study I will thus focus on the explicit process of comparing pros and cons  -->
-which I will do in this study by elaborating on the privacy deliberation process. 
+which I do in this study by elaborating on what I will call the the privacy deliberation process. 
 Fourth, the privacy calculus model is criticized for over-emphasizing rationality [@knijnenburgDeathPrivacyCalculus2017].
-Hence, I extend the privacy calculus in analyzing how trust and self-efficacy, two more psychological variables, affect communication.
+Hence, I extend the privacy calculus in analyzing how trust and self-efficacy, two more socio-psychological variables, affect communication.
 <!-- Third, in this study I approach the privacy calculus from the theoretical perspective of _bounded rationality_.  -->
@@
 The privacy calculus analyzes why people communicate online.
-When are people willing to engage in a conversation?
+When are we willing to engage in a conversation?
 <!-- Do they express their opinion?  -->
-It builds on the calculus of behavior [@lauferPrivacyConceptSocial1977], which states that people are weighing risks and benefits before communicating.
+It builds on the calculus of behavior [@lauferPrivacyConceptSocial1977] and states that people are weighing risks and benefits before communicating.
 <!-- In communicating online, people share much information about themselves. -->
@@
 Outweighing concerns, the most relevant drivers of online communication are expected gratifications [@dienlinExtendedPrivacyCalculus2016a; @bolUnderstandingEffectsPersonalization2018b; @kezerGettingPrivacyCalculus2022].
-People are happy to trade in parts of their privacy, when they can get something more valuable in return [@lauferPrivacyConceptSocial1977].
+People are happy to trade in parts of their privacy when they can receive something more valuable in return [@lauferPrivacyConceptSocial1977].
 In online communication, the most important benefits include social support [@krasnovaOnlineSocialNetworks2010], social capital [@ellisonNegotiatingPrivacyConcerns2011], entertainment [@dhirUnderstandingRelationshipIntensity2017], information-seeking [@whitingWhyPeopleUse2013], and self-presentation [@minHowArePeople2015].
@@
 
-H1: People who are more concerned about their privacy than others are less likely to communicate actively on a website.
+H1: People who are more concerned about their privacy are less likely to communicate actively on a website.
 
@@
 Only observing that privacy concerns or expected gratifications and communication online are related does not prove that an explicit weighing process took place [@knijnenburgDeathPrivacyCalculus2017].
-Instead, we need to analyze if and how much people actively deliberate about their privacy, and whether doing so influences their decision to communicate.
+Instead, we need to analyze if and by how much people actively deliberate about their privacy, and whether doing so influences their decision to communicate.
 <!-- We can understand the privacy calculus from two perspectives. -->
@@
 Privacy deliberation captures the extent to which individuals explicitly compare risks and benefits before communicating with others.
-How could deliberating on one's privacy affect communication?
-On the one hand, deliberating about privacy could reduce subsequent communication.
+
+How could deliberating about one's privacy affect communication?
+On the one hand, it could reduce subsequent communication.
 Refraining from communication---the primary means of connecting with others [@altmanPrivacyConceptualAnalysis1976]---likely requires some active and deliberate restraint [@omarzuDisclosureDecisionModel2000].
@@
 On the other hand, deliberating about privacy might also increase communication.
-In light of the benefits mentioned above, a person might conclude that communication is beneficial, thereby legitimating communication [@krasnovaOnlineSocialNetworks2010]. 
+In light of the benefits mentioned above, would it not make sense to conclude that participation is beneficial, thereby fostering communication [@krasnovaOnlineSocialNetworks2010]?
 <!-- I therefore formulate the following research question: -->
@@
 
-RQ1: Do people who deliberate more actively whether they should communicate, communicate more or less online?
+RQ1: Do people who deliberate more actively about their privacy communicate more or less online?
 
@@
 1303].
-But although human behavior is partly irrational, bounded rationality does not state that it is completely irrational [@gigerenzerBoundedRationalityAdaptive2002].
+Although human behavior is partly irrational, bounded rationality does not state that it is completely irrational [@gigerenzerBoundedRationalityAdaptive2002].
 Rationality is a continuum. 
@@
 It follows that to provide a more complete picture, additional factors next to gratifications and concerns should also explain communication.
-Factors less focused on rationality, but more on psychosocial aspects.
+Factors less focused on rationality, but more on socio-psychological aspects.
 <!-- Communication online often takes place in situations where information is limited or obscure. -->
@@
 <!-- Whereas specific trust focuses on the causes of trust, general trust emphasizes the experience of trust. -->
-In online contexts, there are different _targets_ of trust, including (a) the information system, (b) the provider, (c) the Internet, and (d) the community of other users [@sollnerWhyDifferentTrust2016].
+In online contexts, there are different targets of trust, including (a) the information system, (b) the provider, (c) the Internet, and (d) the community of other users [@sollnerWhyDifferentTrust2016].
 People who put more trust in the providers of networks, for example, disclose more personal information [@liEmpiricalStudiesOnline2011]. 
@@
 How are the privacy calculus and communication affected by the context, the digital infrastructure? 
-First, it makes sense not to focus on specific features of particular websites, which change and become obsolete [@foxDistinguishingTechnologiesSocial2017]. 
+In analyzing this question, it makes sense not to focus on specific features of particular websites, which change and become obsolete [@foxDistinguishingTechnologiesSocial2017]. 
 Instead, it is recommended focusing on the underlying latent structures by analyzing so-called _affordances_ [@ellisonSocialNetworkSite2015; @foxDistinguishingTechnologiesSocial2017].
@@
 <!-- ; as such, they are by definition subjective.  -->
-There is an ongoing debate on what exactly defines an affordance [@evansExplicatingAffordancesConceptual2017].
+There is an ongoing debate on how to best understand and operationalize affordances [@evansExplicatingAffordancesConceptual2017].
 Whereas @evansExplicatingAffordancesConceptual2017 propose three affordances for mediated communication (i.e., anonymity, persistence, and visibility), @foxDistinguishingTechnologiesSocial2017 suggest 10 affordances for SNSs alone (i.e., accessibility, bandwidth, social presence, privacy, network association, personalization, persistence, editability, conversation control, and anonymity).
@@
 Being able to attract likes might motivate users to communicate, while the mere option to receive dislikes might intimidate others.
-Second, _actually receiving_ likes or dislikes might additionally affect subsequent behavior, thereby reinforcing the process.
+Second, _actually receiving_ likes or dislikes might additionally affect subsequent behavior, thereby reinforcing the process [@skinnerScienceHumanBehavior2014].
 
-Likes are positive and represent the positivity bias of social media [@schreursExposurePositivityBias2022]. 
+Likes are affirmative and represent the positivity bias of social media [@schreursExposurePositivityBias2022]. 
 Receiving a like online is similar to receiving a compliment offline [@carrPredictingThresholdPerceived2018; @sumnerFunctionalApproachFacebook2017].
@@
 In situations where there is more to win, people might also more actively deliberate about whether or not to communicate. 
-Dislike represent a punishment, introducing a _loss frame_. 
+Dislikes, instead, represent a punishment, introducing a _loss frame_. 
 <!-- Although most communication emphasizes positive aspects, the Internet is also replete with spite, envy, and arguments. -->
-Websites featuring both like _and_ dislike buttons should be more ambivalent compared to websites without popularity cues.
+Websites featuring both like _and_ dislike buttons should therefore be more ambivalent compared to websites without popularity cues.
 <!-- Especially in online contexts, short-term gains often outweigh long-term losses [@acquistiSecretsLikesDrive2020]. -->
@@
 The hypotheses, sample size, research materials, analyses, and exclusion criteria were preregistered (see https://osf.io/a6tzc/?view_only=5d0ef9fe5e1745878cd1b19273cdf859). 
-In some cases, the pre-registered approach needed to be changed (see [companion website](https://XMtRa.github.io/like_dislike)). 
+In some cases, the preregistered approach needed to be changed (see [companion website](https://XMtRa.github.io/like_dislike/preregistration_changes)). 
 Analyses that were not preregistered are reported as exploratory analyses.
@@
 The study was designed as an online field experiment with three different groups. 
-The first experimental group used a website that included like buttons buttons; the second experimental group used an identical website including both like and dislike buttons; and the control group used an identical website without like and dislike buttons.
+The first experimental group used a website that included like buttons; the second experimental group used an identical website including both like and dislike buttons; and the control group used an identical website without like and dislike buttons.
 Participants were randomly distributed to one of the three websites in a between-subject design.
@@
 Members who agreed to participate were sent the first questionnaire (_T1_).
-The questionnaire asked participants about their sociodemographic background, (b) provided more details about the study, and (c) included a registration link for the website, which was described as "participation platform".
+The questionnaire asked participants about their sociodemographic background, (b) provided more details about the study, and (c) included a registration link for the website, which was introduced as "participation platform".
 Afterward, participants were randomly assigned to one of the three websites. 
 After registration was completed, participants were invited (but not obliged) to visit the website and to discuss the topic of the terrorism threat in Germany (_field_). 
-Participants had the chance to use the website and to provide comments over the course of one week.
+Participants could use the website and write comments over the course of one week.
 Subsequently, participants received a follow-up questionnaire in which the self-reported measures reported below were collected (_T2_). 
@@
 All communication was checked, and there were no instances of people providing meaningless text or doubting the experiment.
-For a screenshot of the landing page and an example of comments that were written, see Figure \@ref(fig:website).
+For a screenshot of the landing page and for examples of comments, see Figure \@ref(fig:website).
 
@@
 Sample size was determined using a priori power analyses.
-The power analysis was based on a smallest effect size of interest approach [SESOI, @lakensEquivalenceTestingPsychological2018]. 
+The power analyses were based on a smallest effect size of interest approach [SESOI, @lakensEquivalenceTestingPsychological2018]. 
 <!-- Namely, I defined a minimum effect size considered sufficiently large to support the hypotheses.  -->
@@
 <!-- With the final sample size, what effects can still be found reliably, that is with a power of 95%? -->
-Sensitivity analyses showed that the current study could still make reliable results (i.e., power = 95%) for effects at least as large as _r_ = `r r_sensitive %>% my_round("std")`.
+Sensitivity analyses showed that the current study could still make reliable results (i.e., with a power of 95%) for effects at least as large as _r_ = `r r_sensitive %>% my_round("std")`.
 In conclusion, although not as powerful as planned, the study is still adequately powered to find the small effects reported in the privacy literature [@baruhOnlinePrivacyConcerns2017].
@@
 For the variables' distributions, see Figure \@ref(fig:corrplot). 
-For the exact wording of all items and their individual distributions, see [companion website](https://XMtRa.github.io/like_dislike).
+For all items and their distributions, see [companion website](https://XMtRa.github.io/like_dislike).
 
@@
 To exclude confounding influences, I controlled all variables for age, gender, and education, which were shown to affect both privacy concerns and online communication [@masurUnderstandingEffectsConceptual2023; @tifferetGenderDifferencesPrivacy2019a].
-Preregistered hypotheses were tested with a one-sided significance level of 5%. 
-Research questions were tested with a two-sided 5% significance level using family-wise Bonferroni-Holm correction.
+The preregistered hypotheses were tested with a one-sided significance level of 5%; the research questions were tested with a two-sided 5% significance level using family-wise Bonferroni-Holm correction.
 
@@
 First, communication was zero-inflated and gamma distributed. 
-Although it is possible to analyze non-normal data with structural equation modeling, it is recommended to use analyses that model the variables' distribution, which can be done with Bayesian hurdle models [@mcelreathStatisticalRethinkingBayesian2016].
+Although it is possible to analyze non-normal data with structural equation modeling, it is recommended to use analyses that model the variables' distribution, which can be achieved with Bayesian hurdle models [@mcelreathStatisticalRethinkingBayesian2016].
 I conclusion, in the exploratory analyses I ran Bayesian hurdle regression models, modeling the outcome as a zero-inflated gamma distribution.
@@
 I also plotted the distribution of the effects.
-For more information, see online supplementary material.
+For more information, see [online companion website](https://XMtRa.github.io/like_dislike).
 
@@
 
-I first measured and plotted all bivariate relations between the study variables (see Figure \@ref(fig:corrplot)). 
+I first plotted the bivariate relations of all variables (see Figure \@ref(fig:corrplot)). 
 <!-- No relationship was particularly curvilinear.  -->
 All variables referring to the privacy calculus demonstrated the expected bivariate relationships with communication. 
-For example, people who were more concerned about their privacy disclosed less information (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "pri_con" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")`).
-Specific gratifications predicted communication better than general gratifications (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_spec" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")` vs.
-_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_gen" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")`).
+For example, people who were more concerned about their privacy disclosed less information (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "pri_con" & rhs == "Words_log") %>% select(std.all) %>%  my_round("std_txt")`).
+Specific gratifications predicted communication better than general gratifications (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_spec" & rhs == "Words_log") %>% select(std.all) %>%  my_round("std_txt")` vs.
+_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_gen" & rhs == "Words_log") %>% select(std.all) %>%  my_round("std_txt")`).
 The mean of privacy deliberation was _m_ = `r des_pridel$m %>% round(2)`. 
@@
 I found several signs of multicollinearity, as evidenced by the large standard errors or "wrong" and reversed signs of predictors [@vanhoveCollinearityIsnDisease2021]. 
-For example, in the bivariate analysis trust had a _positive_ relation with communication, whereas in the multiple regression the effect was _negative_---which should make us wary.
+For example, in the bivariate analysis trust had a _positive_ relation with communication, whereas in the multiple regression the effect was _negative_---which should make us sceptical
 
@@
 Hypotheses 1, 2, 3, and 4 were all confirmed:
-If participants expected more gratifications from participation, they communicated more: 
-If their expected gratifications increased by one point, on average they also wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(Estimate) %>% round(0)` more words (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(UL) %>% round(0)`).
+If participants expected more gratifications from participation, they communicated more actively: 
+If their expected gratifications increased by one point, on average they also wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(Estimate) %>% round(0)` words more (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(UL) %>% round(0)`).
 If participants were more concerned about their privacy, they communicated less: 
-With each one-point increase in privacy concerns, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(Estimate) %>% round(0) %>% abs()` fewer words (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(UL) %>% round(0)`).
+With each one-point increase in privacy concerns, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(Estimate) %>% round(0) %>% abs()` words fewer (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(UL) %>% round(0)`).
 If participants felt more self-efficacious, they also communicated much more:
-If their self-efficacy increased by one point, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Self-efficacy") %>%  select(Estimate) %>% round(0)` more words (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Self-efficacy") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Self-efficacy") %>%  select(UL) %>% round(0)`).
+If their self-efficacy increased by one point, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Self-efficacy") %>%  select(Estimate) %>% round(0)` words more (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Self-efficacy") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Self-efficacy") %>%  select(UL) %>% round(0)`).
 The relationship was curvilinear, almost exponential: 
-Whereas a change in self-efficacy from 1 to 2 only led to an "increase" of `r effects_wrds_selfeff_12 %>% round(0) %>% unlist %>% english()` words, a change from 6 to 7 led to an increase of `r effects_wrds_selfeff_67 %>% round(0)` words.
-And if participants experienced more trust in the website, provider, and other users, they also communicated much more:
-If their trust increased by one point, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Trust") %>%  select(Estimate) %>% round(0)` more words (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Trust") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Trust") %>%  select(UL) %>% round(0)`).
+Whereas a change in self-efficacy from 1 to 2 only led to an "increase" of `r effects_wrds_selfeff_12 %>% round(0) %>% as.integer() %>% english()` words, a change from 6 to 7 led to an increase of `r effects_wrds_selfeff_67 %>% as.integer() %>%  round(0)` words.
+Next, if participants experienced more trust in the website, provider, and other users, they also communicated much more:
+If their trust increased by one point, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Trust") %>%  select(Estimate) %>% as.integer() %>% round(0)` words more (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Trust") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Trust") %>%  select(UL) %>% round(0)`).
 The first research question asked how privacy deliberation would affect communication.
@@
 The more people deliberated about their privacy, the less they communicated.
-If privacy deliberation increased by one point, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy deliberation") %>%  select(Estimate) %>% round(0) %>% abs()` less words (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy deliberation") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy deliberation") %>%  select(UL) %>% round(0)`).
+If privacy deliberation increased by one point, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy deliberation") %>%  select(Estimate) %>% round(0) %>% abs()` words less (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy deliberation") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy deliberation") %>%  select(UL) %>% round(0)`).
 
 I then reanalyzed the effects of the popularity cues on communication.
-Compared to the control condition without popularity cues, implementing like buttons did not significantly affect communication, _b_ = `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like vs.control") %>%  select(Estimate) %>% round(0)` (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like vs.control") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like vs.control") %>%  select(UL) %>% round(0)`).
+Compared to the control condition without popularity cues, implementing like buttons did not significantly affect communication, _b_ = `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like vs.
+control") %>%  select(Estimate) %>% round(0)` (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like vs.
+control") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like vs.
+control") %>%  select(UL) %>% round(0)`).
 However, implementing both like and dislike buttons affected communication.
-Contrary to what I expected, implementing both popularity cues did not increase but rather decreased communication.
-If both popularity cues were present, participants on average wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like & dislike vs.control") %>%  select(Estimate) %>% round(0) %>% abs()` words less (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like & dislike vs.control") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like & dislike vs.control") %>%  select(UL) %>% round(0)`).
+Contrary to what I expected, implementing both popularity cues decreased communication.
+If both popularity cues were present, participants on average wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like & dislike vs.
+control") %>%  select(Estimate) %>% round(0) %>% abs()` words less (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like & dislike vs.
+control") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like & dislike vs.
+control") %>%  select(UL) %>% round(0)`).
 The introduction of both cues hence led to a `r effect_lkdlk_prcnt %>% as.integer()`% decline in number of words that were written.
@@
 Finally, I tested if the effect of the popularity cues on communication were potentially mediated by the privacy calculus variables. 
-Results showed that this was not the case (see online companion material),
+Results showed that this was not the case (see [online companion website](https://XMtRa.github.io/like_dislike)),
 <!-- Additional analyses showed that the popularity cues did not affect the privacy calculus' variables of privacy concerns, gratifications, trust, self-efficacy, or privacy deliberation.  -->
@@
 
-```{r results}
+```{r results, include=T}
 apa_table(tab_slopes %>% 
@@
           , note = "CI = credibility interval, LL = lower level; UL = upper level. Reported are average marginal effects."
-          # , align = c("l{5cm}rrr")
-          # , align = c("p{6cm}", rep("r", 3))
+          , align = c("p{6cm}", rep("r", 3))
           , digits = 0
@@
 In addition, the main variable and outcome of the study, number of communicated words, was zero-inflated and gamma distributed, requiring a different type of analysis.
-The preregistered analyses using structural equation modeling with multiple predictors were hence subpar.
+The preregistered analyses using structural equation modeling with multiple predictors were hence problematic
 
-To address these shortcoming, in several exploratory analyses I conducted Bayesian hurdle-gamma models (see Data analysis).
+To address these shortcomings, in several exploratory analyses I conducted Bayesian hurdle-gamma models (see Data analysis).
 <!-- To account for the data's distribution, I now ran Bayesian hurdle-gamma models,  -->
@@
 This updated approach changed the results.
-People who were more concerned about their privacy wrote significantly less words. 
+People who were more concerned about their privacy wrote fewer words. 
 To illustrate, people who reported being very much concerned posted only `r wrds_pricon_7` words on average, whereas people who reported being not concerned posted `r wrds_pricon_1` words.
@@
 Participants who felt more self-efficacious disclosed much more than others.
-To illustrate, if people reported no self-efficacy, they wrote only `r wrds_selfeff_1` words on average.
+To illustrate, if people reported no self-efficacy, they wrote only `r wrds_selfeff_1` word on average.
 However, when they reported high levels of self-efficacy, they wrote `r wrds_selfeff_7` words.
@@
 This finding further supports the underlying premise of bounded rationality [@simonBoundedRationality1990].
-Although more rational aspects such as costs and benefits influence behavior, behavior is also determined by more psychosocial variables such as trust and efficacy.
+Although more rational aspects such as costs and benefits influence behavior, behavior is also determined by more socio-psychological variables such as trust and self-efficacy.
 
@@
 
-Privacy deliberation and privacy concerns were strongly correlated (_r_ = .61), showing comparable correlations with other variables. 
+Privacy deliberation and privacy concerns were strongly correlated (_r_ = .61) and showed comparable correlations with other variables. 
 If we are concerned, we also think and deliberate more about our privacy. 
@@
 And when in a positive mood, we are more lenient. 
-At this point, it is still unknown if thinking about privacy increases concerns or, conversely, if growing more concerned about privacy encourages us to deliberate more carefully. 
+At this point, it is still unknown if thinking about privacy increases concerns or, conversely, if growing more concerned about privacy makes us deliberate more carefully. 
 <!-- Future research might tell. -->
@@
 If anything, there was an unexpected (nonsignificant) trend toward reduced communication.
-Although we would expect that like buttons, being positive feedback cues, would increase communication, it also seems plausible that they can decrease communication.
+Although we would expect that like buttons, being positive feedback cues, increase communication, it also seems plausible that they can decrease communication.
 <!-- there might be contexts and scenarios where this is not the case. -->
@@
 Not receiving likes might be more threatening and intimidating than on regular social media, on which it is more common to discuss every-day topics.
-Although like buttons are commonplace in social media, the findings suggests that in specific contexts they inhibit communication.
+Although like buttons are commonplace in social media, the findings suggest that in specific contexts they inhibit communication.
 
@@
 
-Whereas the effects of the popularity cues on all variables can be interpreted from a causal perspective (but see below), more caution is needed when regarding the effects of the privacy calculus variables on communication.
-Although the effects were controlled for age, gender, and education, other variables not included here might exist that potentially bias the causal estimates presented here [@coenenIndirectEffectOmitted2022].
+Whereas the effects of the popularity cues on all variables can be interpreted from a causal perspective (but see below), more caution is needed regarding the effects of the privacy calculus variables on communication.
+Although the effects were controlled for age, gender, and education, other variables not included could potentially bias the causal estimates presented here [@coenenIndirectEffectOmitted2022].
 <!-- The results do not allow for causal interpretation.  -->
@@
 Users can be considered proactive and reasonable.
-But, similar to everyday offline contexts, users are also affected by the affordances of their environment, often acting implicitly.
+But, similar to everyday offline contexts, they are also affected by the affordances of their environment, and often act implicitly without pondering the consequences of their actions.
 

### 2023-05-12 analyses.Rmd
- major updates before submission - language, analyses, commenting

@@
 
+Let's first load the packages we require for our analyses. Note that some need to be installed manually from github.
+
 ```{r results='hide', cache=F}
@@
     "GGally",
-    "gganimate",
     "kableExtra", 
@@
     "MVN",
-    # "psych", 
     "pwr", 
@@
 ## Custom Functions
+
+We now build some custom functions required for the analyses. Note that here you can find the syntax for the main analyses wrapped in helper functions, which we will then call below.
 
@@
 ## Data-Wrangling
+
+Let's next tidy up and prepare the data, so we can analyze them.
 
@@
     # take logarithm
-    words_log = log1p(words)
+    words_log = log1p(words),
+    self_dis_log = log1p(self_dis)
   )
@@
 
-We filtered participants who answered the questionnaire in less than three minutes, which we considered to be unreasonably fast.
+I filtered participants who answered the questionnaire in less than three minutes, which I considered to be unreasonably fast.
 
@@
 
-We inspected the data manually for cases with obvious response patterns. The following cases show extreme response patterns (alongside fast response times), and were hence removed.
+I inspected the data manually for cases with obvious response patterns. The following cases show extreme response patterns (alongside fast response times), and were hence removed.
 
@@
     )
-
-# infl_cases_tokens <- infl_cases_tokens[!infl_cases_tokens %in% resp_pattern]
 
@@
 # Measures
+
+Let's next inspect all measures. I list all items, their distributions and CFAs.
+
 ## Privacy concerns
@@
 ```
+
+Model fit was good.
 
@@
 
+Model fit was okay.
+
 ## Privacy deliberation
@@
 
+Model fit was very good (which is nice, given it's a newly designed scale).
+
 ## Trust general
@@
 
-&nbsp;&nbsp;&nbsp;1. The other users seemed trustworthy.  
-&nbsp;&nbsp;&nbsp;2. The operators of the participation platform seemed trustworthy.  
-&nbsp;&nbsp;&nbsp;3. The website seemed trustworthy.
+ 1. The other users seemed trustworthy.  
+ 2. The operators of the participation platform seemed trustworthy.  
+ 3. The website seemed trustworthy.
 
@@
 ### CFA
+
+Note that I constrained two loadings to be able to report model fit. I used operators and website, as these are theoretically closer.
 
@@
 
-Note that we constrained Items 5 and Item 9 to be equal.
+Note that I constrained Items 5 and Item 9 to be equal.
 Explanation: First, they are theoretically related.
@@
 ```{r}
-name <- "trust_spec"
+name <- "trustspec"
 model <- "
@@
 
-  trust =~ trust_community + trust_provider + trust_system
+  trust_spec =~ trust_community + trust_provider + trust_system
 "
@@
 
-### CFA 2
-
-Because there was Heywoodcase, we now also run a model in which the subdimensions `provider` and `system` are combined.
-
-```{r}
-name <- "trustspec"
-model <- "
-  trust_community =~ TR01_01 + TR01_02 + TR01_03
-  trust_provider =~ TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09
-  trust_spec =~ b*trust_community + b*trust_provider
-"
-fit <- lavaan::sem(
-  model = model, 
-  data = d, 
-  estimator = "MLR", 
-  missing = "ML"
-  )
-```
-
-Model fit:
-
-```{r}
-facval <- 
-  fit_tab(
-    fit, 
-    reliability = TRUE, 
-    scaled = TRUE
-    ) %T>%
-  print()
-
-assign(
-  paste0(
-    name, 
-    "_facval"
-    ), 
-  facval
-  )
-```
-
-Factor loadings:
-
-```{r}
-inspect(
-  fit,
-  what = "std"
-  ) %$%
-  lambda
-```
-Warning disappears, results show adequate fit.
+Model fit was good (there's a Highwood case on level 1, which is not too problematic in this case.)
 
@@
 
-Shows significant misfit. We will delete inverted items, while allowing covariations between Items 1 and 2 (tech-oriented) and Items 3 and 4 (topic-oriented).
+Shows significant misfit. I will delete inverted items, while allowing covariations between Items 1 and 2 (tech-oriented) and Items 3 and 4 (topic-oriented).
 
@@
 
-We see that Communication is severely skewed. Let's calculate how many participants actually commented.
+We can see that Communication is severely skewed. Let's calculate how many participants actually commented.
 
@@
 ```
+
+`r no_words_perc` percent wrote a comment. The average number of communicated words was `r words_m`.
 
@@
   trust_community =~ TR01_01 + TR01_02 + TR01_03
-  trust_provider =~ TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09
-  trust_spec =~ b*trust_community + b*trust_provider
+  trust_provider =~ TR01_04 + TR01_05 + TR01_06
+  trust_system =~ TR01_07 + TR01_08 + TR01_09
+  trust_spec =~ trust_community + trust_provider + trust_system
   self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
@@
 
-We first report the factor validity of all variables combined.
+I first report the factor validity of all variables combined.
 
@@
 
-# add centered predictors for interaction analyses later
-d %<>%
-  mutate(
-    pri_con_fs_c = scale(pri_con_fs, scale = FALSE),
-    grats_spec_fs_c = scale(grats_spec_fs, scale = FALSE),
-    pri_del_fs_c = scale(pri_del_fs, scale = FALSE),
-    trust_gen_fs_c = scale(trust_gen_fs, scale = FALSE),
-    self_eff_fs_c = scale(self_eff_fs, scale = FALSE),
-    male_c = scale(male, scale = FALSE),
-    edu_c = scale(edu, scale = FALSE),
-    age_c = scale(age, scale = FALSE),
-    con_x_del = pri_con_fs_c * pri_del_fs_c,
-    grats_x_del = grats_spec_fs_c * pri_del_fs_c
-    )
-
 # rename for plotting
@@
 
-In what follows, we report zero-order correlations, distributions, and scatterplots of the variables' factor scores.
+In what follows, I report zero-order correlations, distributions, and scatterplots of the variables' factor scores.
 
@@
 
-In what follows, we report power analyses for our study.
-Please note that we conduct a rudimentary power-analysis, assuming bivariate correlations.
-To explain, at the time we were not yet aware of the existence of power analyses for multivariate structural equation models.
+In what follows, I report power analyses for our study.
+Please note that I conduct a rudimentary power-analysis, assuming bivariate correlations.
+(At the time I was not yet aware of the existence of power analyses for multivariate structural equation models.)
 
@@
 
-We first estimate the sample size necessary to find small effects in 95% of all cases.
+I first estimate the sample size necessary to find small effects in 95% of all cases.
 
@@
 
-We then compute the power we have achieved with our finale sample size to detect small effects.
+I then compute the power we have achieved with our final sample size to detect small effects.
 
@@
 
-We finally compute what effect size we are likely to find in 95% of all cases given our final sample size.
+I finally compute what effect size we are likely to find in 95% of all cases given our final sample size.
 
@@
 
-Shows that multivariate normal distribution is violated. We hence use maximum likelihood estimation with robust standard errors and a Satorra-Bentler scaled test statistic.
+Shows that multivariate normal distribution is violated. I hence use maximum likelihood estimation with robust standard errors and a Satorra-Bentler scaled test statistic.
 
@@
 
-[Note: These lines stopped working after some time, potentially due to changes in package.]
-
-In what follows we test for influential cases in the baseline model, to detect potentially corrupt data (e.g., people who provided response patterns). Specifically, we compute Cook's distance.
+In what follows I test for influential cases in the baseline model, to detect potentially corrupt data (e.g., people who provided response patterns). Specifically, I compute Cook's distance.
+
+[Note: The following lines stopped working after some time, potentially due to changes in package. I can hence not recreate them here, but refer to results obtained before.]
 
@@
   trust_community =~ TR01_01 + TR01_02 + TR01_03
-  trust_provider =~ TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09
-  trust_spec =~ b*trust_community + b*trust_provider
+  trust_provider =~ TR01_04 + TR01_05 + TR01_06
+  trust_system =~ TR01_07 + TR01_08 + TR01_09
+
+  trust_spec =~ trust_community + trust_provider + trust_system
 
@@
 
-In what follows, we also report explicit statistical tests of the differences between the conditions using contrasts.
+In what follows, I also report explicit statistical tests of the differences between the conditions using contrasts.
 
@@
   trust_community =~ TR01_01 + TR01_02 + TR01_03
-  trust_provider =~ TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09
-  trust_spec =~ b*trust_community + b*trust_provider
+  trust_provider =~ TR01_04 + TR01_05 + TR01_06
+  trust_system =~ TR01_07 + TR01_08 + TR01_09
+  trust_spec =~ trust_community + trust_provider + trust_system
 
@@
 
-We first compare likes and likes plus dislikes to the control condition.
+I first compare likes and likes plus dislikes to the control condition.
 
@@
 
-We then compare likes and likes plus dislikes to the control condition.
+I then compare likes and likes plus dislikes to the control condition.
 
@@
 
-We then compare likes and likes plus dislikes to the control condition.
+I then compare the likes and control conditions to the likes plus dislikes condition.
 
@@
   , fit_baseline, fit_prereg
-  # , fig_fs_m, fig_fs_cor, fig_coeffs
   , des_pridel
@@
   , n_users, n_final
-  # , infl_cases, infl_cases_tokens
   , resp_pattern, n_resp_pattern

### 2023-05-12 manuscript.RmD
- major updates before submission - language, analyses, commenting

@@
 ---
-title             : "Likes or Dislikes, Gratifications or Concerns? Analyzing the Effects of Popularity Cues on the Privacy Calculus in Online Communication"
+title             : "Likes or Dislikes, Gratifications or Concerns? A One-Week Field Experiment Analyzing the Effects of Popularity Cues on the Privacy Calculus in Online Communication"
 
@@
 abstract: |
-    According to the privacy calculus model, online communication is determined by two factors, privacy concerns and expected benefits.
-How is the privacy calculus affected by external affordances, for example popularity cues such as like and dislike buttons?
-And should the privacy calculus model be extended by integrating more socio-psychological measures such as trust, self-efficacy, and privacy deliberation?
-To this end, a preregistered one-week field experiment with 590 participants was conducted.
-Participants were randomly distributed to three different websites, on which they discussed a current political topic.
-The websites included either (a) like buttons, (b) both like and dislike buttons, or (c) no like or dislike buttons.
-Because of multicollinearity and non-normal distribution of the outcome, the preregistered analyses needed to be updated.
-The results revealed that implementing both like and dislike buttons decreased online communication by 44%.
-As predicted by the privacy calculus model, expected benefits and perceived privacy concerns substantially affected communcation.
-Actively deliberating about privacy by comparing benefits and drawbacks decreased communication, while experiencing self-efficacy and trust strongly increased communication.
+    The privacy calculus model states that people weigh risks and benefits before communicating online.
+This paper analyzes three open questions.
+How robust is the privacy calculus, can it be replicated with actual behavior in realistic online setting?
+Do we need to extend the model by integrating more socio-psychological measures such as trust, self-efficacy, and privacy deliberation?
+How easily can the privacy calculus be be manipulated by external factors such as like and dislike buttons?
+In a preregistered one-week field experiment (N = 590), participants discussed a current political topic on an online website, which included either (a) like buttons, (b) both like and dislike buttons, or (c) no buttons.
+The privacy calculus model was confirmed: Benefits and concerns affected communication.
+Deliberating about privacy by comparing benefits and risks decreased communication.
+Experiencing self-efficacy and trust increased communication.
+Implementing both like and dislike buttons had a strong effect on behavior: It reduced online communication by 45 percent.
 
@@
 
-<!-- Understanding why people share personal information online is important.  -->
 According to the privacy paradox, the way users share information online is erratic [@barnesPrivacyParadoxSocial2006]:
-<!-- Personal beliefs, privacy concerns, or behavioral attitudes do not affect online behavior. -->
-<!-- [for an overview of the privacy paradox, see @dienlinPrivacyParadoxAus2019].  -->
-People communicate vast amounts of personal information online, although they are concerned about their privacy [@taddickenUsesPrivacyOnline2011].
-However, despite its popularity in both academic research [@dienlinPrivacyParadoxAus2019] and the public press [@newyorkpublicradioPrivacyParadox2018], empirical support for the privacy paradox is weak [@baruhOnlinePrivacyConcerns2017; @dienlinDoesPrivacyParadox2021].
-<!-- , which shows that privacy concerns are indeed related to communication online.  -->
-<!-- Rather than further pursuing the privacy paradox,  -->
-Research is therefore increasingly building on the privacy calculus model, which states that communication online can be explained successfully by perceived risks and expected benefits [@bolUnderstandingEffectsPersonalization2018b; @krasnovaOnlineSocialNetworks2010; @meierPrivacyCalculusRevisited2022].
-<!-- Several studies have shown that experiencing more privacy risks or concerns is related to sharing less information online [@bolUnderstandingEffectsPersonalization2018b; @meierPrivacyCalculusRevisited2022], while expecting more benefits is related to sharing more information online [@heirmanPredictingAdolescentsDisclosure2013; @koohikamaliInvestigationDynamicModel2019].
--->
+People communicate much personal information online, although being strongly concerned about their privacy [@taddickenUsesPrivacyOnline2011].
+However, despite its popularity in both academic research [@dienlinPrivacyParadoxAus2019] and the public press [@newyorkpublicradioPrivacyParadox2018], empirical support for the privacy paradox is tenuous [@baruhOnlinePrivacyConcerns2017; @dienlinDoesPrivacyParadox2021].
+Research is increasingly building on the privacy calculus model, which states that communication online can be explained by perceived risks and expected benefits [@bolUnderstandingEffectsPersonalization2018b; @krasnovaOnlineSocialNetworks2010; @meierPrivacyCalculusRevisited2022].
 
 Although the privacy calculus has gained momentum in academic research, several important questions remain unanswered. 
-First, we still know little about how the privacy calculus and online communication can be affected by external affordances [@bazarovaIntegrationIndividualisticNetworked2020; @braunlichLinkingLooseEnds2020].
-For example, do popularity cues such as like and dislike buttons affect the privacy calculus and online communication?
-<!-- I therefore analyze whether the privacy calculus is affected by the affordances of a website.  -->
-<!-- Specifically, I investigate whether *popularity cues* such as like and dislike buttons affect the privacy calculus and whether they foster communication online. -->
-Second, the privacy calculus' empirical foundation needs to be improved [@knijnenburgDeathPrivacyCalculus2017]. 
+First, the privacy calculus' empirical foundation needs to be improved [@knijnenburgDeathPrivacyCalculus2017]. 
 To date, much research on the privacy calculus builds on (a) self-reports of behavior [@krasnovaOnlineSocialNetworks2010], (b) vignette approaches [@bolUnderstandingEffectsPersonalization2018b], or (c) one-shot experiments in the lab [@treptePrivacyCalculusContextualized2020].
-Can the privacy calculus be replicated in more authentic and long-term settings using actual behavioral data?
-Third, research on the privacy calculus so far did not measure the actual process of weighing pros and cons [@knijnenburgDeathPrivacyCalculus2017], 
-<!-- According to critics , showing that both concerns and gratifications correlate with communication behavior online is not sufficient evidence for an explicit weighing process.  -->
-<!-- In this study I will thus focus on the explicit process of comparing pros and cons  -->
-which I do in this study by elaborating on what I will call the the privacy deliberation process. 
-Fourth, the privacy calculus model is criticized for over-emphasizing rationality [@knijnenburgDeathPrivacyCalculus2017].
-Hence, I extend the privacy calculus in analyzing how trust and self-efficacy, two more socio-psychological variables, affect communication.
-<!-- Third, in this study I approach the privacy calculus from the theoretical perspective of _bounded rationality_.  -->
-<!-- It is likely that other factors next to risks and benefits also determine behavior. -->
-<!-- I therefore extend the privacy calculus model theoretically by investigating the role and interplay of trust and self-efficacy. -->
+Self-reports are often unreliable measures of online behavior [@parrySystematicReviewMetaanalysis2021], vignette approaches have limited external validity, and one-shot experiments cannot analyze compound effects of sustained use.
+The first aim is therefore to replicate the privacy calculus model in a more authentic and long-term setting using actual behavioral data.
+Doing so will show its robustness, and it will help understand if behavior is better explained by the privacy paradox approach or by the privacy calculus model.
 
-<!-- To answer these research questions, a representative sample of the German population was collected in a preregistered online field experiment. -->
-<!-- Participants were randomly distributed to one of three different websites, which either included a like button, both a like and a dislike button, or no buttons at all.  -->
-<!-- Over the course of one week, participants discussed a topical issue (i.e., prevention of terrorist attacks in Germany).  -->
-<!-- In a follow-up questionnaire, they answered items measuring the privacy calculus variables. -->
+Second, the privacy calculus model is criticized for neglecting the actual process of weighing pros and cons, and for over-emphasizing rationality  [@knijnenburgDeathPrivacyCalculus2017].
+Simply showing that both concerns and gratifications correlate with communication online does not prove that an explicit weighing process took place.
+Instead, we need to find out if people deliberately compare costs and benefits before communicating online. 
+Therefore, I will also analyze the process of comparing pros and cons explicitly, by elaborating on what I will call the the privacy deliberation process [@omarzuDisclosureDecisionModel2000]. 
+Next, focusing exclusively on costs and benefits does not fully capture how and why users engage online.
+I, hence, extend the privacy calculus by analyzing how online communication is affected by trust and self-efficacy, two variables less focused on rationality and more oriented toward socio-psychological aspects [@metzgerPrivacyTrustDisclosure2004].
 
-## The Privacy Calculus
+Online behavior is determined by the person itself and their external circumstances [@bazarovaIntegrationIndividualisticNetworked2020; @treptePrivacyCalculusContextualized2020; @spottswoodShouldShareThat2017].
+The privacy calculus upholds that much of behavior is rational and self-determined, but how easily can this process be manipulated by external circumstances?
+Online contexts are optimized to elicit as much interaction as possible [@ellisonSocialNetworkSite2015; @masurBehavioralContagionSocial2021], for example via low threshold communication features such as likes, shares, replies, or reactions  [@carrPredictingThresholdPerceived2018].
+Implicit and explicit cues on how a website is used can increase self-disclosure [@spottswoodShouldShareThat2017; @treptePrivacyCalculusContextualized2020].
+How large are the effects of external popularity cues such as like and dislike buttons compared to the internal weighing of pros and cons?
+And how easily can the privacy calculus be manipulated by popularity cues?
+
+## Replicating the Privacy Calculus
 
@@
 When are we willing to engage in a conversation?
-<!-- Do they express their opinion?  -->
-It builds on the calculus of behavior [@lauferPrivacyConceptSocial1977] and states that people are weighing risks and benefits before communicating.
-<!-- In communicating online, people share much information about themselves. -->
+It builds on the calculus of behavior [@lauferPrivacyConceptSocial1977] and states that people are weighing risks and benefits before engaging in communication.
 Communication is closely related to privacy, which is defined as a "voluntary and temporary withdrawal of a person from the general society" [@westinPrivacyFreedom1967, p. 7].
@@
 Disclosing information can be risky, and if people are more concerned about their privacy 
-<!-- they should be less likely to communicate information. -->
-<!-- Almost all types of communication allow for meaningful inferences about a person, even when we _don't_ communicate [@watzlawickPragmaticsHumanCommunication2011].  -->
-<!-- However, the recent years have illustrated vividly how much additional insights we can get about a person, simply by analyzing their digital traces of communication or their meta-data [@kosinskiPrivateTraitsAttributes2013].
--->
-<!-- The more we communicate, the more we self-disclose. -->
-<!-- Online privacy concerns represent "[...] how much an individual is motivated to focus on their control over a voluntary withdrawal from other people or societal institutions on the Internet, accompanied by an uneasy feeling that their privacy might be threatened" [@dienlinLongitudinalAnalysisPrivacy2021, p.
-4].
--->
-<!-- Notably, I don't assume that this weighing process is flawless or perfectly rational. -->
-<!-- Instead, I understand the privacy calculus from the perspective of _bounded rationality_ [@simonBoundedRationality1990], which has three main tenets:  -->
-<!-- "(1) humans are cognitively constrained;  -->
-<!-- (2) these constraints impact decision making;  -->
-<!-- and (3) difficult problems reveal the constraints and highlight their significance." [@bendorBoundedRationality2015, p. 1303] -->
-<!-- Crucially, although bounded rationally upholds that human behavior is not perfectly logical, this does not meant that it is illogical [@gigerenzerBoundedRationalityAdaptive2002]. -->
-<!-- Instead, it makes more sense to consider rationality a continuum. -->
-<!-- Humans are still trying to optimize the outcomes of their behavior according to their own best interests or values. -->
-<!-- It is only that their capacity to do so is bounded. -->
-<!-- Transferred to the context of online privacy, it is by now well known that several irregularities and inconsistencies between concerns and communication behavior exist. -->
-<!-- These differences stem from, for example, information asymmetries, present bias, intangibility, illusory control, or herding [@acquistiSecretsLikesDrive2020]. -->
-<!-- Indeed, If people experience more concerns,  -->
-they are less likely to communicate online [@baruhOnlinePrivacyConcerns2017; @dienlinExtendedPrivacyCalculus2016a; @krasnovaOnlineSocialNetworks2010; @masurUnderstandingEffectsConceptual2023; @meierPrivacyCalculusRevisited2022].
+they are less likely to communicate online [@baruhOnlinePrivacyConcerns2017; @krasnovaOnlineSocialNetworks2010; @masurUnderstandingEffectsConceptual2023; @meierPrivacyCalculusRevisited2022].
 According to a meta-analysis by @baruhOnlinePrivacyConcerns2017, the effect is small but significant (*r* = -.13).
-<!-- At the same time, _on average_ people do behave according to their interests, respond to incentives, or actively manage their privacy [@baruhOnlinePrivacyConcerns2017; @braunlichLinkingLooseEnds2020; @dienlinExtendedPrivacyCalculus2016a; @soloveMythPrivacyParadox2020].
--->
-
-<!-- I therefore hypothesize that people who experience more privacy concerns engage in less communication online. -->
-<!-- In light of bounded rationality and the existence of other competing factors that also influence online-communication (see below), the effect is likely small. -->
 
@@
 People are happy to trade in parts of their privacy when they can receive something more valuable in return [@lauferPrivacyConceptSocial1977].
-In online communication, the most important benefits include social support [@krasnovaOnlineSocialNetworks2010], social capital [@ellisonNegotiatingPrivacyConcerns2011], entertainment [@dhirUnderstandingRelationshipIntensity2017], information-seeking [@whitingWhyPeopleUse2013], and self-presentation [@minHowArePeople2015].
-<!-- As a result, we expect a moderate relationship. -->
+In online communication, the most important benefits include social support [@krasnovaOnlineSocialNetworks2010], social capital [@ellisonBenefitsFacebookFriends2007], entertainment [@dhirUnderstandingRelationshipIntensity2017], information-seeking [@whitingWhyPeopleUse2013], and self-presentation [@minHowArePeople2015].
 
@@
 
-Although privacy calculus implies that people explicitly compare benefits and drawbacks before communicating online, research has neglected this aspect [@knijnenburgDeathPrivacyCalculus2017].
+## Extending the Privacy Calculus
+
+Although privacy calculus implies that people explicitly compare benefits and risks before communicating online, prior research has neglected this aspect [@knijnenburgDeathPrivacyCalculus2017].
 Only observing that privacy concerns or expected gratifications and communication online are related does not prove that an explicit weighing process took place [@knijnenburgDeathPrivacyCalculus2017].
-Instead, we need to analyze if and by how much people actively deliberate about their privacy, and whether doing so influences their decision to communicate.
-<!-- We can understand the privacy calculus from two perspectives. -->
-<!-- First, is the communication behavior aligned with people's privacy concerns and expected benefits?  -->
-<!-- Second, is the communication process implicit or explicit? -->
-<!-- Here, I suggest that the privacy calculus should be discussed in light of dual process theories, which state that people either deliberately, explicitly, and centrally take decisions, or instead do so automatically, implicitly, and peripherally [@kahnemanThinkingFastSlow2011; @pettyCommunicationPersuasionCentral1986].
--->
-<!-- Accordingly, privacy calculus would assume that people, when it comes to disclosing, engage in a central processing.  -->
-Self-disclosure theory [@omarzuDisclosureDecisionModel2000;  @altmanPrivacyConceptualAnalysis1976] suggests that if the benefits to be attained from communication are attractive, deciding whether or not to communicate is a "conscious and deliberative process"  [@omarzuDisclosureDecisionModel2000, p.
+Instead, we need to analyze if, and if so by how much, people actively deliberate about their privacy, and whether doing so influences their decision to communicate.
+Self-disclosure theory [@omarzuDisclosureDecisionModel2000;  @altmanPrivacyConceptualAnalysis1976] suggests that if the benefits of communication are attractive, deciding whether or not to communicate is a "conscious and deliberative process"  [@omarzuDisclosureDecisionModel2000, p.
 183].
@@
 On the one hand, it could reduce subsequent communication.
-Refraining from communication---the primary means of connecting with others [@altmanPrivacyConceptualAnalysis1976]---likely requires some active and deliberate restraint [@omarzuDisclosureDecisionModel2000].
+Refraining from communication---the primary means of connecting with others [@altmanPrivacyConceptualAnalysis1976]---often requires restraint [@omarzuDisclosureDecisionModel2000]. 
 This is especially true for social media, which are designed to foster communication and participation [@ellisonSocialNetworkSite2015; @masurBehavioralContagionSocial2021].
@@
 On the other hand, deliberating about privacy might also increase communication.
-In light of the benefits mentioned above, would it not make sense to conclude that participation is beneficial, thereby fostering communication [@krasnovaOnlineSocialNetworks2010]?
-<!-- I therefore formulate the following research question: -->
-<!-- Deliberation could represent some kind of inner consent, providing additional affirmation. -->
-<!-- Alternatively, it could be that deliberation functions as a moderator. -->
-<!-- For example, if people actively deliberate about whether or not to disclose, this might reinforce the effect of concerns or gratifications. -->
-<!-- Reflecting about the pros and cons of communication might concerns and gratifications more salient.  -->
-<!-- Alternatively, it could also be that deliberating decreases the effects, for example because apparent gratifications are considered more critically, and maybe loose their appeal. -->
+In light of the numerous benefits mentioned above, it might make sense to conclude that participation is beneficial, thereby fostering communication [@krasnovaOnlineSocialNetworks2010].
 
@@
 
-<!-- RQ2: Do people who deliberate more actively whether they should communicate, show larger or smaller relations between concerns, gratifications and communication behavior? -->
-This weighing process is not flawless or perfect.
-It is therefore useful to understand the privacy calculus from a perspective of _bounded rationality_ [@simonBoundedRationality1990].
+The aforementioned weighing process is not flawless or perfect.
+It is useful to understand the privacy calculus from the perspective of _bounded rationality_ [@simonBoundedRationality1990].
 Bounded rationality states that "(1) humans are cognitively constrained; (2) these constraints impact decision making; and (3) difficult problems reveal the constraints and highlight their significance." [@bendorBoundedRationality2015, p.
 1303].
-Although human behavior is partly irrational, bounded rationality does not state that it is completely irrational [@gigerenzerBoundedRationalityAdaptive2002].
+Importantly, although human behavior is _partly_ irrational, bounded rationality does not state that it is _completely_ irrational [@gigerenzerBoundedRationalityAdaptive2002].
 Rationality is a continuum. 
-<!-- Instead, it makes more sense to consider rationality a continuum. -->
-<!-- Humans are still trying to optimize the outcomes of their behavior according to their own best interests or values. -->
-<!-- It is only that their capacity to do so is bounded. -->
-In the context of online privacy, for example, rationality is impeded by information asymmetries, presence bias, intangibility, illusory control, or herding [@acquistiSecretsLikesDrive2020].
+In the context of online privacy, rationality is impeded by information asymmetries, presence bias, intangibility, illusory control, or herding [@acquistiSecretsLikesDrive2020].
 It follows that to provide a more complete picture, additional factors next to gratifications and concerns should also explain communication.
 Factors less focused on rationality, but more on socio-psychological aspects.
-<!-- Communication online often takes place in situations where information is limited or obscure. -->
 
+Prior research suggests that perhaps the following two factors are most important when it comes to understanding online communication: self-efficacy and trust [@correaParticipationDivideOnline2010; @hossainICTEnabledVirtual2004; @metzgerPrivacyTrustDisclosure2004].
 For example, if users are more familiar, experienced, and knowledgeable in a given online context, they are more likely to navigate that online contexts successfully and to communicate actively [@baruhOnlinePrivacyConcerns2017; @kramerMasteringChallengeBalancing2020].
 People with more privacy self-efficacy also engage more successfully in self-withdrawal [@dienlinExtendedPrivacyCalculus2016a].
-Hence, if users possess more _self-efficacy_ to participate, they should also communicate more.
+Hence, if users possess more self-efficacy to participate, they should also communicate more.
 
@@
 
-In situations where people lack experience or competence, a relevant variable to understand behavior is _trust_.
-Especially in online contexts, users often cannot control the environment or the way their information is handled [@acquistiSecretsLikesDrive2020; @braunlichLinkingLooseEnds2020].
-Trust plays a key role in online communication [@metzgerPrivacyTrustDisclosure2004]. 
+In all situations where people lack experience, control, or competence, a central variable to understand behavior is trust [@gefenTrustTAMOnline2003].
+Especially in online contexts, trust plays a key role [@metzgerPrivacyTrustDisclosure2004].
+Users often cannot control the environment or the way their information is handled [@acquistiSecretsLikesDrive2020; @braunlichLinkingLooseEnds2020].
 Trust either captures "_specific_ beliefs dealing primarily with the integrity, benevolence, and ability of another party" [@gefenTrustTAMOnline2003, p.
 55, emphasis added] or a "_general_ belief that another party can be trusted" [@gefenTrustTAMOnline2003, p.55, emphasis added].
-<!-- Whereas specific trust focuses on the causes of trust, general trust emphasizes the experience of trust. -->
 In online contexts, there are different targets of trust, including (a) the information system, (b) the provider, (c) the Internet, and (d) the community of other users [@sollnerWhyDifferentTrust2016].
 People who put more trust in the providers of networks, for example, disclose more personal information [@liEmpiricalStudiesOnline2011].
-<!-- @gefenTrustTAMOnline2003 prioritize specific trust (p. 60).  -->
-<!-- Because the targets can be largely different, it is often recommended to analyze them individually. -->
 
@@
 
-## The Effects of Popularity Cues
+## Analyzing the Impact of Popularity Cues
 
 How are the privacy calculus and communication affected by the context, the digital infrastructure? 
-In analyzing this question, it makes sense not to focus on specific features of particular websites, which change and become obsolete [@foxDistinguishingTechnologiesSocial2017]. 
-Instead, it is recommended focusing on the underlying latent structures by analyzing so-called _affordances_ [@ellisonSocialNetworkSite2015; @foxDistinguishingTechnologiesSocial2017].
+How easily can the calculus be manipulated externally?
+One of the central tools to afford and govern online behavior are popularity cues such as like and dislike buttons [@stsiampkouskayaNotExperimentalStudy2023].
+Popularity cues have been shown to affect behavior [@kramerMasteringChallengeBalancing2020; @masurBehavioralContagionSocial2021; @treptePrivacyCalculusContextualized2020]:
+Online comments that already have several dislikes are more likely to receive further dislikes [@muchnikSocialInfluenceBias2013]. 
+When users disagree with a post, they are more likely to click on a button labeled _respect_ compared to a button labeled _like_ [@stroudRecommendRespectAltering2017].
+
+How and why might popularity cues affect the privacy calculus?
+In analyzing this question, it makes sense to analyze the cues' underlying affordances [@ellisonSocialNetworkSite2015; @foxDistinguishingTechnologiesSocial2017].
 Affordances are mental representations of how objects might be used.
 They emphasize that it is not the _objective features_ that determine behavior, but rather our _subjective perceptions_ [@gibsonEcologicalApproachVisual2015].
-<!-- ; as such, they are by definition subjective.  -->
 There is an ongoing debate on how to best understand and operationalize affordances [@evansExplicatingAffordancesConceptual2017].
 Whereas @evansExplicatingAffordancesConceptual2017 propose three affordances for mediated communication (i.e., anonymity, persistence, and visibility), @foxDistinguishingTechnologiesSocial2017 suggest 10 affordances for SNSs alone (i.e., accessibility, bandwidth, social presence, privacy, network association, personalization, persistence, editability, conversation control, and anonymity).
-<!-- The privacy calculus states that both benefits and costs determine behavior. -->
-Popularity cues such as like and dislike buttons, which are of interest here, are categorized as "paralinguistic digital affordances" [@carrPredictingThresholdPerceived2018, p. 142].
+Popularity cues such as like and dislike buttons, which are of primary interest in this study, are understood as "paralinguistic digital affordances" [@carrPredictingThresholdPerceived2018, p. 142].
 
-<!-- Both can be linked to the two sides of the privacy calculus.  -->
-<!-- The like button is positive and a potential benefit: -->
-<!-- It expresses an endorsement, a compliment, a reward [@carrPredictingThresholdPerceived2018; @sumnerFunctionalApproachFacebook2017].  -->
-<!-- The dislike button is negative and a potential cost:  -->
-<!-- It expresses criticism and a way to downgrade content.  -->
+```{r model, fig.cap="Overview of analyzed model.", fig.align='center', out.width=".8\\textwidth"}
+# knitr::include_graphics("figures/design/model_simplified.pdf")
+knitr::include_graphics("figures/design/model_simplified.png")
+```
 
-Paralinguistic digital affordances and specifically popularity cues have been shown to affect behavior [@kramerMasteringChallengeBalancing2020; @masurBehavioralContagionSocial2021; @treptePrivacyCalculusContextualized2020].
-Online comments that already have several dislikes are more likely to receive further dislikes [@muchnikSocialInfluenceBias2013]. 
-When users disagree with a post, they are more likely to click on a button labeled _respect_ compared to a button labeled _like_ [@stroudRecommendRespectAltering2017].
-<!-- In light of their potentially strong negative effects, most major social networking sites did not implement dislike buttons.  -->
-<!-- At the time of writing, only a handful of websites have (partially) implemented it (e.g., youtube, stackexchange, or reddit). -->
 Popularity cues likely impact the privacy calculus via two underlying theoretical mechanisms [@kramerMasteringChallengeBalancing2020]:
 First, the _mere presence_ of popularity cues might affect whether people are willing to disclose. 
-Being able to attract likes might motivate users to communicate, while the mere option to receive dislikes might intimidate others.
-Second, _actually receiving_ likes or dislikes might additionally affect subsequent behavior, thereby reinforcing the process [@skinnerScienceHumanBehavior2014].
-
-Likes are affirmative and represent the positivity bias of social media [@schreursExposurePositivityBias2022]. 
+Being able to attract likes might afford active communication. 
+The mere option to receive dislikes, conversely, might inhibit communication.
+Second, _actually receiving_ likes or dislikes might affect behavior, by means of positive reinforcement (likes) or punishment (dislikes) [@skinnerScienceHumanBehavior2014].
+To illustrate, likes are affirmative and embody the positivity bias of social media [@schreursExposurePositivityBias2022]. 
 Receiving a like online is similar to receiving a compliment offline [@carrPredictingThresholdPerceived2018; @sumnerFunctionalApproachFacebook2017].
@@
 Dislikes, instead, represent a punishment, introducing a _loss frame_. 
-<!-- Although most communication emphasizes positive aspects, the Internet is also replete with spite, envy, and arguments. -->
 Websites featuring both like _and_ dislike buttons should therefore be more ambivalent compared to websites without popularity cues.
-<!-- Especially in online contexts, short-term gains often outweigh long-term losses [@acquistiSecretsLikesDrive2020]. -->
-<!-- Having both like and dislike buttons might still lead to more gratifications and communication. -->
 Privacy concerns should not be reduced anymore:
 People who are more concerned about their privacy are also more shy and risk averse [@dienlinPsychologyPrivacyAnalyzing2017].
-Implementing the dislike button might therefore increase privacy concerns, thereby canceling out the positive effects of the like button. 
-<!-- And because there is more at stake, participants should deliberate even more whether or not to disclose.  -->
+Implementing the dislike button might therefore increase privacy concerns, canceling out the positive effects of the like button.
 
@@
 
-<!-- When directly comparing websites including both like and dislike buttons with websites including only like buttons, building on the rationales presented above, it is likely that websites including both buttons should increase privacy concerns and privacy deliberation.
--->
-
 H7.	Compared to people who use a website with only like buttons, people who use a website with like and dislike buttons (a) are more concerned about their privacy, and (b) deliberate more about whether they should communicate online.
@@
 
-```{r model, fig.cap="Overview of analyzed model.", fig.align='center', out.width=".8\\textwidth"}
-# knitr::include_graphics("figures/design/model_simplified.pdf")
-knitr::include_graphics("figures/design/model_simplified.png")
-```
-
 # Methods
@@
 
-This manuscript features a [companion website](https://XMtRa.github.io/like_dislike), which includes the data, research materials, analyses scripts, and a reproducible version of this manuscript (see https://XMtRa.github.io/like_dislike).
+This manuscript features a [companion website](https://XMtRa.github.io/like_dislike), which includes the data, research materials, analysis scripts, and a reproducible version of this manuscript (see https://XMtRa.github.io/like_dislike).
 The hypotheses, sample size, research materials, analyses, and exclusion criteria were preregistered (see https://osf.io/a6tzc/?view_only=5d0ef9fe5e1745878cd1b19273cdf859). 
-In some cases, the preregistered approach needed to be changed (see [companion website](https://XMtRa.github.io/like_dislike/preregistration_changes)). 
-Analyses that were not preregistered are reported as exploratory analyses.
+In some cases, the preregistered approach had to be changed (see [companion website](https://XMtRa.github.io/like_dislike/preregistration_changes)). 
+Analyses not preregistered are reported as exploratory analyses.
 
@@
 Participants were recruited using the professional panel agency Norstat.
-As incentive, participants were awarded digital points, which they could use to get special offers from online retailers. 
+As incentive, participants were awarded digital points, to receive special offers from online retailers. 
 Participants had to be above the age of 18 and had to live in Germany. 
-In a first step, the company sent its panel members an invitation to participate in the study (_invitation_). 
+In a first step, the company sent its panel members an invitation to participate in the study. 
 In this invitation, panel members were asked to participate in a study analyzing the current threat posed by terrorist attacks in Germany.
-<!-- [^1]  -->
 Members who agreed to participate were sent the first questionnaire (_T1_).
@@
 Afterward, participants were randomly assigned to one of the three websites. 
-After registration was completed, participants were invited (but not obliged) to visit the website and to discuss the topic of the terrorism threat in Germany (_field_). 
+After registration was completed, participants were invited (but not obliged) to visit the website and to discuss the topic of the terrorism threat in Germany. 
 Participants could use the website and write comments over the course of one week.
 Subsequently, participants received a follow-up questionnaire in which the self-reported measures reported below were collected (_T2_).
-<!-- Measures were collected after and not before the field phase in order not to prime participants or reveal the primary research interest. -->
 
-<!-- [^1]: Although the terror attack was not of primary interest for this study, the data can and will also be used to analyze perceptions of the terrorism threat.
-Hence, no deception took place, and in the debriefing participants were informed about the additional research interest in privacy.
--->
+```{r website, echo=FALSE, out.width="49%", fig.cap="Screenshot of the landing page and of communication taking place. Translated into English.", fig.show='hold', fig.align='center'}
+knitr::include_graphics(c("figures/website/website_translated.png","figures/website/comments_translated.png"))
+```
 
@@
 
-```{r website, echo=FALSE, out.width="49%", fig.cap="Screenshot of the landing page and of communication taking place", fig.show='hold', fig.align='center'}
-knitr::include_graphics(c("figures/website/website_translated.png","figures/website/comments_translated.png"))
-```
-
 ## Participants
@@
 Sample size was determined using a priori power analyses.
-The power analyses were based on a smallest effect size of interest approach [SESOI, @lakensEquivalenceTestingPsychological2018]. 
-<!-- Namely, I defined a minimum effect size considered sufficiently large to support the hypotheses.  -->
+The power analyses were based on estimates from the literature.
 When researching aspects of privacy online [e.g., @baruhOnlinePrivacyConcerns2017], effects are often small [i.e., _r_ = .10, @cohenPowerPrimer1992].
-Hence, the SESOI was set to be _r_ = `r r_sesoi %>% my_round("std")`. 
-The aim was to be able to detect this SESOI with a probability of at least 95% (i.e., power = 95%).
+Hence, the minimum effect size was set to be _r_ = `r r_sesoi %>% my_round("std")`. 
+The aim was to be able to detect this effect with a probability of at least 95% (i.e., power = 95%).
 Using the regular alpha level of 5%, power analyses suggested a minimum sample size of _N_ = `r n_desired %>% format(big.mark = ",")`. 
-In the end, I was able to include _N_ = `r n_final` in the analyses (see below), which was significantly smaller than the original aim.
+In the end, I was able to include _N_ = `r n_final` in the analyses (see below), which was significantly lower than the original aim.
 With this sample size, the study had a power of `r power_achieved * 100`% to find an effect at least as large as _r_ = `r r_sesoi %>% my_round("std")`. 
-<!-- To understand the implications, I ran sensitivity analyses. -->
-<!-- With the final sample size, what effects can still be found reliably, that is with a power of 95%? -->
 Sensitivity analyses showed that the current study could still make reliable results (i.e., with a power of 95%) for effects at least as large as _r_ = `r r_sensitive %>% my_round("std")`.
@@
 Considered unreasonably fast, `r n_speeding %>% english()` participants were excluded who finished the questionnaire at T2 in less than three minutes.
-To detect atypical data and response patterns, I calculated Cook's distance.
+To detect atypical data and response patterns, Cook's distance was calculated.
 I excluded `r english(n_resp_pattern)` participants with clear response patterns (i.e., straight-lining). 
@@
 
-<!-- Wherever possible, I operationalized the variables using established measures. -->
-<!-- Where impossible (for example, to date there exists no scale on privacy deliberation), I self-designed novel items, which were pretested concerning legibility and understandability. -->
 Factor validity was assessed using confirmatory factor analyses (CFA). 
@@
     select(-alpha) %>% 
-    rename(`p-value` = pvalue), 
+    rename(`p-value` = pvalue) %>% 
+    mutate(df = as.integer(.$df)), 
   font_size = "footnotesize",
@@
   note = "omega = Raykov's composite reliability coefficient omega; avevar = average variance extracted."
+  # , align = c("l", rep("r", 11))
   )
 ```
-
-<!-- ### Privacy concerns -->
 
@@
 One item was deleted due to poor psychometric properties.
-
-<!-- ### Gratifications -->
+The mean was _m_ = `r facval_tab["Privacy concerns", "m"]`. This value is below the scale's midpoint of 4, showing that on average people were not strongly concerned about their privacy.
 
@@
 "learn things I would not have noticed otherwise" (information), "react to a subject that is important to me" (relevance), "engage politically" (political participation), "try to improve society" (idealism), and "soothe my guilty consciences" (extrinsic benefits).
-
-<!-- ### Privacy deliberation -->
+The means for both dimensions were _m_ = `r facval_tab["General gratifications", "m"]` (general gratifications) and _m_ = `r facval_tab["Specific gratifications", "m"]` (specific gratifications), which were above the scales' midpoint.
+This shows that on average people considered the website to be beneficial.
 
@@
 One example item was "While using the participation platform I have weighed the advantages and disadvantages of writing a comment."
-
-<!-- ### Self-efficacy -->
+The mean lay on the scale's neutral midpoint (_m_ = `r facval_tab["Privacy deliberation", "m"]`). 
+(For an interpretation, see below.)
 
@@
 Two inverted items were deleted due to poor psychometric properties.
-
-<!-- ### Trust -->
+People felt self-efficacious to use the website (_m_ = `r facval_tab["Self-efficacy", "m"]`).
 
@@
 One example item was "The operators of the participation platform seemed trustworthy."
-_Specific trust_ was operationalized for the same three targets with three subdimensions each (i.e., ability, benevolence/integrity, and reliability), measured with one item each. 
+_Specific trust_ was operationalized for the same three targets with three sub-dimensions each (i.e., ability, benevolence/integrity, and reliability), measured with one item each. 
 Example items were "The operators of the participation platform have done a good job" (ability), "The other users had good intentions" (benevolence/integrity), "The website worked well" (reliability).
-Because they were closely related, the two targets "provider" and "website" were combined into one dimension. 
-<!-- , as was evidenced by a Heywood case (i.e., standardized coefficient greater than 1).  -->
-<!-- I hence adapted the scale to combine these two targets.  -->
-The updated scale showed adequate fit.
+Participants placed a lot of trust in the website, the providers and the other users (trust general: _m_ = `r facval_tab["General trust", "m"]`; trust specific: _m_ = `r facval_tab["Specific trust", "m"]`).
 
 _Communication_ was calculated by counting the number of words each participant wrote in a comment.
-Communication was zero-inflated and heavily skewed.
-While `r round(no_words_perc * 100, 0)` percent did not communicate at all, some communicated a lot.
+Communication was zero-inflated and heavily skewed:
+While `r round(no_words_perc * 100, 0)` percent did not communicate at all, the maximum number of words communicated by a single user was `r d %$% words %>% max()` words.
 On average, participants wrote `r words_m %>% round(0)` words.
 
-## Data analysis
+## Data Analysis
 
@@
 The influence of the three websites was analyzed using contrast coding.
-<!-- I could therefore test the effects of experimental manipulations within a theoretical framework while using latent variables [@klinePrinciplesPracticeStructural2016].  -->
 Because the assumption of multivariate normality was violated, I estimated the models using robust maximum likelihood [@klinePrinciplesPracticeStructural2016]. 
 As recommended by @klinePrinciplesPracticeStructural2016, to assess global fit I report the model's $\chi^2$, RMSEA (90% CI), CFI, and SRMR. 
-To exclude confounding influences, I controlled all variables for age, gender, and education, which were shown to affect both privacy concerns and online communication [@masurUnderstandingEffectsConceptual2023; @tifferetGenderDifferencesPrivacy2019a].
+To exclude confounding influences, I controlled all variables for age, gender, and education, which have been shown to affect both privacy concerns and online communication [@masurUnderstandingEffectsConceptual2023; @tifferetGenderDifferencesPrivacy2019a].
 The preregistered hypotheses were tested with a one-sided significance level of 5%; the research questions were tested with a two-sided 5% significance level using family-wise Bonferroni-Holm correction.
@@
 Although it is possible to analyze non-normal data with structural equation modeling, it is recommended to use analyses that model the variables' distribution, which can be achieved with Bayesian hurdle models [@mcelreathStatisticalRethinkingBayesian2016].
-I conclusion, in the exploratory analyses I ran Bayesian hurdle regression models, modeling the outcome as a zero-inflated gamma distribution.
+I conclusion, in the exploratory analyses I ran Bayesian hurdle regression models, modeling the outcome as a zero-inflated gamma distribution using default (flat) priors [chains = 4, iterations = 2,000, warm-up = 1,000, @R-brms_a].
 Second, in the preregistered analyses several variables were combined that are theoretically and empirically closely related, leading to multicollinearity [@vanhoveCollinearityIsnDisease2021].
 As a remedy, I adopted a causal modeling perspective, controlling only for confounders---in this case, age, gender, and education---but not for mediators [@rohrerThinkingClearlyCorrelations2018]. 
-To assess the effects, I tested whether or not the 95% credibility intervals of the average marginal effects excluded zero.
+To assess the effects, I tested whether or not the 95% highest density intervals of the average marginal effects excluded zero.
 If they excluded zero, effects can be considered "significant" [@mcelreathStatisticalRethinkingBayesian2016]. 
 I also plotted the distribution of the effects.
-For more information, see [online companion website](https://XMtRa.github.io/like_dislike).
-
-<!-- Exploratory analyses were conducted from a descriptive perspective. -->
-<!-- The reported p-values and confidence intervals should thus not be overinterpreted. -->
+For more information on the fitted models, see [online companion website](https://XMtRa.github.io/like_dislike).
 
@@
 I first plotted the bivariate relations of all variables (see Figure \@ref(fig:corrplot)). 
-<!-- No relationship was particularly curvilinear.  -->
 All variables referring to the privacy calculus demonstrated the expected bivariate relationships with communication. 
@@
 
-## Preregistered analyses
+## Preregistered Analyses
 
@@
 However, these results should be treated with caution.
-I found several signs of multicollinearity, as evidenced by the large standard errors or "wrong" and reversed signs of predictors [@vanhoveCollinearityIsnDisease2021]. 
-For example, in the bivariate analysis trust had a _positive_ relation with communication, whereas in the multiple regression the effect was _negative_---which should make us sceptical
+I found several signs of multicollinearity, evidenced by the large standard errors or "wrong" and reversed signs of predictors [@vanhoveCollinearityIsnDisease2021]. 
+For example, in the bivariate analysis trust had a positive relation with communication, whereas in the multiple regression the effect was negative---which should make us skeptical.
 
 Next, I analyzed the effects of the popularity cues. 
-It was for example expected that websites with like buttons would lead to more communication, more gratifications, more privacy deliberation, and to less privacy concerns.
+It was for example expected that websites with like buttons would lead to more communication, more gratifications, more privacy deliberation, and less privacy concerns.
 The results showed that the popularity cues had no effects on communication and on the privacy calculus variables.
 For an illustration, see Figure \@ref(fig:popularitycues). 
-<!-- The results show that the confidence intervals of all preregistered variables overlap, illustrating that there were no statistically significant differences across websites. -->
 For the detailed results of the specific inference tests using contrasts, see [companion website](https://XMtRa.github.io/like_dislike).
@@
 Like: Website with like buttons.
-Like \\& Dislike: Website with like and dislike buttons.", out.width = "\\textwidth", fig.pos = "!h"}
+Like \\& Dislike: Website with like and dislike buttons.
+Values from preregistered SEM.", out.width = "\\textwidth", fig.pos = "!h"}
 knitr::include_graphics("figures/results/violin_plot.png")
@@
 
-## Exploratory analyses
+## Exploratory Analyses
 
-As explained above, the preregistered results were problematic, because communication was not normally distributed and because the predictors were collinear.
-I hence ran updated analyses, using Bayesian hurdle models, controlling only for confounders but not mediators.
+As explained above, the preregistered results were problematic.
+Communication was not normally distributed and the predictors were collinear.
+I hence updated the analyses, using Bayesian hurdle models controlling only for confounders but not mediators.
 The updated exploratory analyses showed different results.
+
+```{r slopes, fig.cap="Exploratory analyses.
+Plotted are the average marginal effects of the Bayesian hurdle models.
+The difference between the control and the like \\& disklike group is significant.", fig.height=8, fig.width=8, out.width=".9\\textwidth", fig.align='center', fig.pos = "!h", warning=F}
+knitr::include_graphics("figures/results/effects.png")
+```
 
@@
 If participants expected more gratifications from participation, they communicated more actively: 
-If their expected gratifications increased by one point, on average they also wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(Estimate) %>% round(0)` words more (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(UL) %>% round(0)`).
+If their expected gratifications increased by one point, on average they also wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(Estimate) %>% round(0)` words more (95% HDI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(UL) %>% round(0)`).
 If participants were more concerned about their privacy, they communicated less: 
-With each one-point increase in privacy concerns, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(Estimate) %>% round(0) %>% abs()` words fewer (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(UL) %>% round(0)`).
-If participants felt more self-efficacious, they also communicated much more:
-If their self-efficacy increased by one point, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Self-efficacy") %>%  select(Estimate) %>% round(0)` words more (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Self-efficacy") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Self-efficacy") %>%  select(UL) %>% round(0)`).
+With each one-point increase in privacy concerns, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(Estimate) %>% round(0) %>% abs()` words less (95% HDI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(UL) %>% round(0)`).
+If participants felt more self-efficacious, they communicated much more:
+If their self-efficacy increased by one point, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Self-efficacy") %>%  select(Estimate) %>% round(0)` words more (95% HDI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Self-efficacy") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Self-efficacy") %>%  select(UL) %>% round(0)`).
 The relationship was curvilinear, almost exponential: 
@@
 Next, if participants experienced more trust in the website, provider, and other users, they also communicated much more:
-If their trust increased by one point, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Trust") %>%  select(Estimate) %>% as.integer() %>% round(0)` words more (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Trust") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Trust") %>%  select(UL) %>% round(0)`).
+If their trust increased by one point, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Trust") %>%  select(Estimate) %>% as.integer() %>% round(0)` words more (95% HDI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Trust") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Trust") %>%  select(UL) %>% round(0)`).
 The first research question asked how privacy deliberation would affect communication.
@@
 The more people deliberated about their privacy, the less they communicated.
-If privacy deliberation increased by one point, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy deliberation") %>%  select(Estimate) %>% round(0) %>% abs()` words less (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy deliberation") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy deliberation") %>%  select(UL) %>% round(0)`).
-
-I then reanalyzed the effects of the popularity cues on communication.
-Compared to the control condition without popularity cues, implementing like buttons did not significantly affect communication, _b_ = `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like vs.
-control") %>%  select(Estimate) %>% round(0)` (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like vs.
-control") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like vs.
-control") %>%  select(UL) %>% round(0)`).
-However, implementing both like and dislike buttons affected communication.
-Contrary to what I expected, implementing both popularity cues decreased communication.
-If both popularity cues were present, participants on average wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like & dislike vs.
-control") %>%  select(Estimate) %>% round(0) %>% abs()` words less (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like & dislike vs.
-control") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like & dislike vs.
-control") %>%  select(UL) %>% round(0)`).
-The introduction of both cues hence led to a `r effect_lkdlk_prcnt %>% as.integer()`% decline in number of words that were written.
-
-Finally, I tested if the effect of the popularity cues on communication were potentially mediated by the privacy calculus variables. 
-Results showed that this was not the case (see [online companion website](https://XMtRa.github.io/like_dislike)),
-<!-- Additional analyses showed that the popularity cues did not affect the privacy calculus' variables of privacy concerns, gratifications, trust, self-efficacy, or privacy deliberation.  -->
-suggesting that the effect was either direct or mediated by other variables not included here [@coenenIndirectEffectOmitted2022].
-
-```{r slopes, fig.cap="Exploratory analyses.
-Plotted are the average marginal effects of the Bayesian hurdle models.
-The difference between the control group and like \\& disklike is significant.", fig.height=8, fig.width=8, out.width=".9\\textwidth", fig.align='center', fig.pos = "!h", warning=F}
-knitr::include_graphics("figures/results/effects.png")
-```
+If privacy deliberation increased by one point, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy deliberation") %>%  select(Estimate) %>% round(0) %>% abs()` words less (95% HDI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy deliberation") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy deliberation") %>%  select(UL) %>% round(0)`).
 
@@
           , col_spanners = list(
-            "CI" = c(3, 4)
+            "HDI" = c(3, 4)
           )
@@
           , caption = "Effects of the privacy calculus variables and the popularity cues on communication. Credibility intervals exluding zero are considered significant."
-          , note = "CI = credibility interval, LL = lower level; UL = upper level. Reported are average marginal effects."
-          , align = c("p{6cm}", rep("r", 3))
+          , note = "HDI = highest density interval, LL = lower level; UL = upper level. Reported are average marginal effects."
+          # , align = c("p{6cm}", rep("r", 3))
           , digits = 0
@@
 
+I then reanalyzed the effects of the popularity cues on communication.
+Compared to the control condition without popularity cues, implementing like buttons did not significantly affect communication, _b_ = `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like vs.
+control") %>%  select(Estimate) %>% round(0)` (95% HDI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like vs.
+control") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like vs.
+control") %>%  select(UL) %>% round(0)`).
+But note that the effect was very close to not including the zero.
+However, implementing both like and dislike buttons affected communication.
+Contrary to what I expected, implementing both popularity cues _decreased_ communication.
+If both popularity cues were present, participants on average wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like & dislike vs.
+control") %>%  select(Estimate) %>% round(0) %>% abs()` words less (95% HDI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like & dislike vs.
+control") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like & dislike vs.
+control") %>%  select(UL) %>% round(0)`).
+The introduction of both cues hence led to a `r effect_lkdlk_prcnt %>% as.integer()`% decline in number of words that were written.
+
+Finally, I tested if the effect of the popularity cues on communication were potentially mediated by the privacy calculus variables. 
+Results showed that this was not the case. 
+The popularity cues only affected behavior, but not the predictors of the privacy calculus model (see [online companion website](https://XMtRa.github.io/like_dislike)).
+The results suggest that the effect was either direct or mediated by other variables not included here [@coenenIndirectEffectOmitted2022].
+
 # Discussion
 
-This study analyzed whether like and dislike buttons would affect online communication and the privacy calculus.
+This study analyzed whether the privacy calculus can be replicated with behavioral data in an authentic setting; if the model needs to be extended theoretically; and whether like and dislike buttons affect online communication and the privacy calculus.
 To this end, a preregistered field experiment was conducted, which lasted one week.
-<!-- and that produced actual behavioral data. -->
-Furthermore, the privacy calculus model was extended.
-The privacy deliberation processes was tested explicitly, and trust and self-efficacy were added as predictors.
+The privacy calculus model was extended: 
+The privacy deliberation processes was tested explicitly, and trust and self-efficacy were included as predictors.
 
@@
 All other variables remained insignificant.
-However, these analyses need to be treated with caution.
+However, the preregistered analyses have to be treated with caution.
 The predictors were collinear, which makes their integration in one single model problematic [@vanhoveCollinearityIsnDisease2021].
-<!-- Confidence intervals are inflated and the interpretation becomes difficult . -->
-In addition, the main variable and outcome of the study, number of communicated words, was zero-inflated and gamma distributed, requiring a different type of analysis.
-The preregistered analyses using structural equation modeling with multiple predictors were hence problematic
+In addition, the main variable and outcome of the study, number of communicated words, was zero-inflated and gamma distributed, which requires a different type of analysis.
+The preregistered analyses using structural equation modeling with multiple predictors were hence problematic.
 
-To address these shortcomings, in several exploratory analyses I conducted Bayesian hurdle-gamma models (see Data analysis).
-<!-- To account for the data's distribution, I now ran Bayesian hurdle-gamma models,  -->
-<!-- and to address multicollinearity, I adopted a causal modeling perspective by controlling for confounders but not for mediators [@rohrerThinkingClearlyCorrelations2018]. -->
+To address these issues, I conducted Bayesian hurdle-gamma models (see section Data analysis).
 This updated approach changed the results.
@@
 To illustrate, people who reported being very much concerned posted only `r wrds_pricon_7` words on average, whereas people who reported being not concerned posted `r wrds_pricon_1` words. 
-Participants who received more gratifications wrote substantially more words, too.
-Together, the results provide further support for the privacy calculus and against the privacy paradox [@dienlinPrivacyParadoxAus2019].
+People who experienced privacy concerns hence differed strongly in their communication behavior from people who were unconcerned. 
+Participants who received more gratifications wrote substantially more words.
+The effect was even larger, almost twice as large.
+For each point-increase in gratifications, participants wrote 27 words more. 
+Attaining benefits online is hence a strong predictor of online communication.
+Together, the results provide further support for the privacy calculus and against the privacy paradox [@baruhOnlinePrivacyConcerns2017; @dienlinPrivacyParadoxAus2019].
 Communication online does not seem to be overly illogical. 
@@
 
-Results showed that trust and self-efficacy are important drivers of online communication.
+Results showed that trust and self-efficacy were important drivers of online communication.
 Participants who placed more trust into the website, the providers, and the other community members communicated more actively.
-Self-efficacy was the strongest of all predictors.
+Interestingly, self-efficacy was the strongest of all predictors.
 Participants who felt more self-efficacious disclosed much more than others.
@@
 However, when they reported high levels of self-efficacy, they wrote `r wrds_selfeff_7` words.
-<!-- In conclusion, trust and efficacy play an important role when it comes to online communication. -->
 This finding further supports the underlying premise of bounded rationality [@simonBoundedRationality1990].
 Although more rational aspects such as costs and benefits influence behavior, behavior is also determined by more socio-psychological variables such as trust and self-efficacy.
+The findings are also aligned with the technology acceptance model, which states that online behavior is most strongly determined by usefulness and ease of use [@venkateshUserAcceptanceInformation2003]---two variables closely related to gratifications and self-efficacy.
 
@@
 In this study, I thus elaborated on the privacy deliberation process.
-The results showed that only one third of all participants agreed to have actively weighed the benefits and drawbacks before communicating on the platform.
-The figure is comparatively low.
+The results showed that only one third of all participants agreed to have actively weighed the benefits and risks before communicating on the platform.
+This figure is comparatively low.
 Even in new online contexts, the majority of users does not seem to actively deliberate about their online communication, suggesting that online use is to large extents implicit [@acquistiSecretsLikesDrive2020].
 
-Privacy deliberation and privacy concerns were strongly correlated (_r_ = .61) and showed comparable correlations with other variables. 
+Interestingly, and perhaps also somewhat surprisingly, privacy deliberation and privacy concerns were strongly correlated (_r_ = .61). 
 If we are concerned, we also think and deliberate more about our privacy. 
 And if we are not concerned, we do not deliberate.
-This finding is aligned with decision theory [@elsbachEffectsMoodIndividuals1999].
-When in a negative state---such as when being concerned---, we judge more critically.
-And when in a positive mood, we are more lenient. 
+This finding can be aligned with decision theory [@elsbachEffectsMoodIndividuals1999]:
+When being concerned, we are in a negative state; and when in a negative state, we judge more critically.
 At this point, it is still unknown if thinking about privacy increases concerns or, conversely, if growing more concerned about privacy makes us deliberate more carefully.
-<!-- Future research might tell. -->
 
@@
 This was an unexpected and interesting finding.
-It suggest that negative feedback, or even only the risks of receiving negative feedback, stifles communication. 
+It suggests that negative feedback, or even only risks of negative feedback, stifles communication. 
 The effect was strong: Implementing both like and dislikes cues led to a `r effect_lkdlk_prcnt %>% as.integer()`% decrease in number of written words.
-This finding is aligned with studies that reported strong effects of popularity cues on behavior [@muchnikSocialInfluenceBias2013]. 
-The negative effects of dislike buttons might explain why almost all existing and successful social network sites have chosen to omit such negative popularity cues. 
+When compared to the privacy calculus variables, we see that the effect is of similar size: Growing a bit more concerned or receiving less gratifications have a comparable impact on behavior.
+This finding is aligned with studies reporting strong effects of popularity cues on behavior [@muchnikSocialInfluenceBias2013].
+
+The negative effects of dislike buttons might help explain why almost all existing successful social network sites have chosen to omit negative popularity cues. 
 At the time of writing, only a handful of websites have (partially) implemented dislike buttons (e.g., youtube, stackexchange, or reddit).
-Despite the positivity bias of social media [@schreursExposurePositivityBias2022], chances of receiving negative feedback and communication are of course real, as can be seen by moral outrages or "shit-storms".
+Despite the positivity bias of social media [@schreursExposurePositivityBias2022], chances of receiving negative feedback and communication are real, as can be seen by moral outrages or "shit-storms".
 Explicit negative popularity cues are low threshold paralinguistic affordances [@carrPredictingThresholdPerceived2018].
-They likely prime or trigger negative experiences or expectations, thereby reducing communication.
+They likely prime or trigger negative experiences or expectations, thereby stifling communication. 
+Interestingly, however, they did not affect the privacy calculus variables, and no indirect effect was found.
+Hence, the effect is either transmitted via variables not included here [@coenenIndirectEffectOmitted2022], or perhaps subconscious and direct.
 
-Websites only with like buttons had no effect on the number of communicated words. 
-If anything, there was an unexpected (nonsignificant) trend toward reduced communication.
-Although we would expect that like buttons, being positive feedback cues, increase communication, it also seems plausible that they can decrease communication.
-<!-- there might be contexts and scenarios where this is not the case. -->
-Not receiving any likes, although the option exists, can be perceived as ostracizing [@schneiderSocialMediaOstracism2017].
+Websites only including like buttons had no effect on the number of communicated words. 
+If anything, there was an unexpected (non-significant) trend toward reduced communication.
+Although one might expect that like buttons, being positive feedback cues, increase communication, it is also plausible that they can decrease communication.
+Not receiving any likes can be perceived as ostracizing [@schneiderSocialMediaOstracism2017].
 In the context of this study, participants discussed a political topic.
-Not receiving likes might be more threatening and intimidating than on regular social media, on which it is more common to discuss every-day topics.
+Here, not receiving likes might be even more threatening and intimidating than on regular social media, where it is more common to discuss every-day and low-threshold topics.
 Although like buttons are commonplace in social media, the findings suggest that in specific contexts they inhibit communication.
-
-<!-- Next to these theoretical and practical implications, the study has also several methodological ones. -->
-<!-- First, when analyzing extended privacy calculus models, aspects of multicollinearity need to taken into account.  -->
-<!-- Trust and self-efficacy are highly related, as privacy concerns and privacy deliberation. -->
-<!-- Hence, when estimating their causal effect on communication, they should not be combined in one single model. -->
-<!-- Instead, they should only be controlled for confounding variables. -->
-<!-- Finally, when analyzing count data, it is recommended to implement models that can explicitly account for the data's distribution. -->
-
-<!-- The results also have methodological implications.  -->
-<!-- First, one can question the tendency to further increase the complexity of the privacy calculus model by adding additional variables [e.g., @dienlinExtendedPrivacyCalculus2016a].  -->
-<!-- "Since all models are wrong the scientist cannot obtain a "correct" one by excessive elaboration.
-[...] Just as the ability to devise simple but evocative models is the signature of the great scientist so overelaboration and overparameterization is often the mark of mediocrity" [@boxScienceStatistics1976, p.
-792].
--->
-<!-- For example, it seems that adding self-efficacy to privacy calculus models is of limited theoretical value. -->
-<!-- Self-efficacy is often only a self-reported proxy of behavior and offers little incremental insight.  -->
-<!-- Instead, it might be more interesting to find out _why_ some people feel sufficiently efficacious to communicate whereas others do not.  -->
-
-<!-- In addition, although adding variables increases explained variance, it can also introduce multicollinearity. -->
-<!-- Multicollinearity is not a problem per se, but rather a helpful warning sign [@vanhoveCollinearityIsnDisease2021]. -->
-<!-- From a _statistical_ perspective, strongly correlated predictors mean that standard errors become larger [@vanhoveCollinearityIsnDisease2021].  -->
-<!-- We can be less certain about the effects, because there is less unique variance [@vanhoveCollinearityIsnDisease2021].  -->
-<!-- As a remedy, researchers could collect larger samples, which would increase statistical power and precision. -->
-<!-- Using accessible statistical software it is now possible to run a priori power analyses that explicitly account for correlated or collinear predictors [@wangPowerAnalysisParameter2020]. -->
-
-<!-- From a _theoretical_ perspective, multicollinearity could also suggest that the underlying theoretical model is ill-configured. -->
-<!-- It is my understanding that multiple regression is often used to isolate effects, to make sure that they are not caused by other third variables. -->
-<!-- However, in cases of highly correlated variables this often does not make much sense theoretically. -->
-<!-- Combining trust and gratification in a multiple regression asks how increasing benefits affects communication _while holding trust constant_. -->
-<!-- However, it seems more plausible to assume that increasing gratifications also automatically increases trust [@sollnerWhyDifferentTrust2016]. -->
-<!-- In the preregistered analysis I even went further and tested whether trust increases communication while holding constant gratifications, privacy concerns, privacy deliberations, and self-efficacy---an unlikely scenario.
--->
-<!-- In short, the effects I found could be correct, but the interpretation is more difficult, potentially artificial, and thereby of little theoretical and practical value. -->
-<!-- In short, analyses with multicolinear predictors provide the correct answer to the wrong question. -->
-
-<!-- Finally, I found a surprisingly strong correlation between specific trust and expected gratifications (i.e., _r_ = .79). -->
-<!-- Operationalizations of trust are remarkably close to expected gratifications.  -->
-<!-- To illustrate, the trust subdimension _ability_ includes items such as “The comments of other users were useful”.  -->
-<!-- Trust is often operationalized as a formative construct that directly results from factors such as expected benefits [@sollnerWhyDifferentTrust2016].  -->
-<!-- In conclusion, it is important not to confuse _causes_ of trust with _measures_ of trust. -->
-<!-- <!-- Doing so can introduce problems of homogeneity and multicollinearity. -->
-<!-- I thus recommend using general and reflective measures of trust. -->
 
@@
 Exploratory analyses are part of the research process, compatible with preregistration, and important for scientific progress [@dienlinAgendaOpenScience2021].
-<!-- Preregistration does not prevent exploration. -->
 The updated analyses represent and document a learning process, which arguably led to an improved analysis.
-However, the results should still be considered preliminary, to be confirmed in subsequent studies.
+However, the results should still be considered somewhat preliminary, to be confirmed in subsequent studies.
 
 Whereas the effects of the popularity cues on all variables can be interpreted from a causal perspective (but see below), more caution is needed regarding the effects of the privacy calculus variables on communication.
-Although the effects were controlled for age, gender, and education, other variables not included could potentially bias the causal estimates presented here [@coenenIndirectEffectOmitted2022].
-<!-- The results do not allow for causal interpretation.  -->
-<!-- First, all results are based on analyses of between-person variance. -->
-<!-- However, between-person relations often do not translate to within-person effects [@hamakerCritiqueCrosslaggedPanel2015].  -->
-<!-- While some studies on privacy concerns online have begun to examine both sources of variance [@dietvorstAdolescentPerceptionsParental2017], similar analyses are still lacking for the privacy calculus.
--->
-<!-- Likewise, the mediation model is only suggestive, as I did not experimentally manipulate the mediating variables and also did not use a longitudinal design. -->
-<!-- However, note that in all these analyses,  -->
-<!-- Hence, the aforementioned relations cannot be explained by the fact that for example females are more concerned about their privacy while communicating less online. -->
-
-<!-- Although I did not find significant effects of like and dislike buttons in this study, they could still affect the privacy calculus in other contexts and settings. -->
-<!-- All findings are limited to the context I analyzed and should not be overly generalized. -->
-<!-- Null-findings pose the *Duhème-Quinn Problem* [@dienesUnderstandingPsychologyScience2008]. -->
-<!-- They can either result from an actual non-existence of effects or, instead, from a poor operationalization of the research question.  -->
-<!-- In this case, it was not possible to send participants notifications when their comments were liked or disliked, which significantly decreased the popularity cues' salience. -->
-
-<!-- The self-reported measures were collected _after_ the field phase in which the dependent variable was measured.  -->
-<!-- As a result, the coefficients might overestimate the actual relations, because demand effects might have led participants to artificially align their theoretical answers with their practical behavior.
--->
+Although the effects were controlled for age, gender, and education, other variables not included here could potentially bias the causal estimates [@coenenIndirectEffectOmitted2022].
+In addition, in order not to reveal the study intention the self-reported measures were collected after the field phase. 
+Demand effects might have led participants to align their answers to their prior behavior.
+As a result, the coefficients might overestimate the actual effects.
 
 In experiments only the treatment variable should be manipulated, while all others should be held constant [assumption of stable unit treatment, @klinePrinciplesPracticeStructural2016]. 
-<!-- In this study, I explicitly manipulated the popularity cues.  -->
 Being a field experiment, several variables could not be held constant, such as the content of communication by other users, the unfolding communication dynamics, and the characteristics of other users.
 Future research should repeat the design, preferably using several runs of the same experiment, to further assess generalizability and robustness.
-<!-- As a result, the assumption of stable unit treatment was violated. -->
 
@@
 This study provides further support for the privacy calculus model and against the privacy paradox approach.
-Expected benefits, privacy concerns, comparing benefits and drawbacks, trust, and self-efficacy all affected communication.
-<!-- People who were more concerned about their privacy communicated less actively online, whereas people who received more gratifications communicated more. -->
-<!-- The more people compared pros and cons, they less they communicated. -->
-<!-- Trust and self-efficacy were also major drivers of communication.  -->
+Expected benefits, privacy concerns, comparing benefits and risks, trust, and self-efficacy all affected communication.
 Like and dislike buttons reduced communication significantly.
-<!-- In conclusion, the results provide further evidence against the privacy paradox. -->
 Users can be considered proactive and reasonable.

### 2023-05-12 manuscript_with-deletions.RmD
- major updates before submission - language, analyses, commenting

--- 2023-04-12 manuscript.RmD
@@
 abstract: |
-    According to the privacy calculus model, online communication is determined by two factors, privacy concerns and expected benefits.
-How is the privacy calculus affected by external affordances, for example popularity cues such as like and dislike buttons?
-And should the privacy calculus model be extended by integrating more socio-psychological measures such as trust, self-efficacy, and privacy deliberation?
-To this end, a preregistered one-week field experiment with 590 participants was conducted.
-Participants were randomly distributed to three different websites, on which they discussed a current political topic.
-The websites included either (a) like buttons, (b) both like and dislike buttons, or (c) no like or dislike buttons.
-Because of multicollinearity and non-normal distribution of the outcome, the preregistered analyses needed to be updated.
-The results revealed that implementing both like and dislike buttons decreased online communication by 44%.
-As predicted by the privacy calculus model, expected benefits and perceived privacy concerns substantially affected communcation.
-Actively deliberating about privacy by comparing benefits and drawbacks decreased communication, while experiencing self-efficacy and trust strongly increased communication.
+    The privacy calculus model states that people weigh risks and benefits before communicating online.
+This paper analyzes three open questions.
+How robust is the privacy calculus, can it be confirmed with actual behavior in realistic online setting?
+Do we need to extend the model by integrating more socio-psychological measures including trust, self-efficacy, and privacy deliberation?
+Can the privacy calculus be be manipulated by external factors such as like and dislike buttons?
+A preregistered one-week field experiment with 590 participants was conducted.
+Participants discussed a current political topic on an online website, which included either (a) like buttons, (b) both like and dislike buttons, or (c) no like or dislike buttons.
+The privacy calculus model was confirmed: Benefits and concerns affected communication.
+Deliberating about privacy by comparing benefits and drawbacks decreased communication, while experiencing self-efficacy and trust increased communication.
+Implementing both like and dislike buttons reduced online communication by 44%.
 
@@
 <!-- Rather than further pursuing the privacy paradox,  -->
-Research is therefore increasingly building on the privacy calculus model, which states that communication online can be explained successfully by perceived risks and expected benefits [@bolUnderstandingEffectsPersonalization2018b; @krasnovaOnlineSocialNetworks2010; @meierPrivacyCalculusRevisited2022].
+Research is therefore increasingly building on the privacy calculus model, which states that communication online can be explained by perceived risks and expected benefits [@bolUnderstandingEffectsPersonalization2018b; @krasnovaOnlineSocialNetworks2010; @meierPrivacyCalculusRevisited2022].
 <!-- Several studies have shown that experiencing more privacy risks or concerns is related to sharing less information online [@bolUnderstandingEffectsPersonalization2018b; @meierPrivacyCalculusRevisited2022], while expecting more benefits is related to sharing more information online [@heirmanPredictingAdolescentsDisclosure2013; @koohikamaliInvestigationDynamicModel2019].
@@
 Although the privacy calculus has gained momentum in academic research, several important questions remain unanswered. 
-First, we still know little about how the privacy calculus and online communication can be affected by external affordances [@bazarovaIntegrationIndividualisticNetworked2020; @braunlichLinkingLooseEnds2020].
-For example, do popularity cues such as like and dislike buttons affect the privacy calculus and online communication?
+First, the privacy calculus' empirical foundation needs to be improved [@knijnenburgDeathPrivacyCalculus2017]. 
+To date, much research on the privacy calculus builds on (a) self-reports of behavior [@krasnovaOnlineSocialNetworks2010], (b) vignette approaches [@bolUnderstandingEffectsPersonalization2018b], or (c) one-shot experiments in the lab [@treptePrivacyCalculusContextualized2020].
+Self-reports are often unreliable measures of online behavior [@parrySystematicReviewMetaanalysis2021], vignette approaches have limited external validity, and one-shot experiments cannot analyze compound effects of sustained use.
+The first aim is therefore to replicate the privacy calculus model in a more authentic and long-term setting using actual behavioral data.
+Doing so will show its robustness, and it will help understand if behavior is better explained by the privacy paradox approach or by the privacy calculus model.
+
 <!-- I therefore analyze whether the privacy calculus is affected by the affordances of a website.  -->
 <!-- Specifically, I investigate whether *popularity cues* such as like and dislike buttons affect the privacy calculus and whether they foster communication online. -->
-Second, the privacy calculus' empirical foundation needs to be improved [@knijnenburgDeathPrivacyCalculus2017]. 
-To date, much research on the privacy calculus builds on (a) self-reports of behavior [@krasnovaOnlineSocialNetworks2010], (b) vignette approaches [@bolUnderstandingEffectsPersonalization2018b], or (c) one-shot experiments in the lab [@treptePrivacyCalculusContextualized2020].
-Can the privacy calculus be replicated in more authentic and long-term settings using actual behavioral data?
-Third, research on the privacy calculus so far did not measure the actual process of weighing pros and cons [@knijnenburgDeathPrivacyCalculus2017], 
-<!-- According to critics , showing that both concerns and gratifications correlate with communication behavior online is not sufficient evidence for an explicit weighing process.  -->
-<!-- In this study I will thus focus on the explicit process of comparing pros and cons  -->
-which I do in this study by elaborating on what I will call the the privacy deliberation process. 
-Fourth, the privacy calculus model is criticized for over-emphasizing rationality [@knijnenburgDeathPrivacyCalculus2017].
-Hence, I extend the privacy calculus in analyzing how trust and self-efficacy, two more socio-psychological variables, affect communication.
+Second, the privacy calculus model is criticized for neglecting the actual process of weighing pros and for over-emphasizing rationality  [@knijnenburgDeathPrivacyCalculus2017].
+Simply showing that both concerns and gratifications correlate with communication online does not prove that an explicit weighing process took place.
+Instead, we need to find out if people deliberately compared costs and benefits before communicating online. 
+Therefore, I will also analyze the explicit process of comparing pros and cons, by elaborating on what I will call the the privacy deliberation process. 
+Next, focusing exclusively on costs and benefits does not sufficiently represent how and why users engage online.
+Hence, I extend the privacy calculus in analyzing how online communication is affected by trust and self-efficacy, two variables less focused on rationality and more on socio-psychological aspects [@metzgerPrivacyTrustDisclosure2004].
+
+Online behavior is determined by the person itself and their external circumstances [@bazarovaIntegrationIndividualisticNetworked2020; @treptePrivacyCalculusContextualized2020; @spottswoodShouldShareThat2017].
+The privacy calculus upholds that much of behavior is rational and self-determined, but how easily can this process be manipulated by external circumstances?
+Online contexts are optimized to elicit as much interaction as possible, for example via low threshold communication features such as likes, shares, replies, or reactions  [@carrPredictingThresholdPerceived2018].
+Implicit and explicit cues on how others use a website can increase self-disclosure [@spottswoodShouldShareThat2017; @treptePrivacyCalculusContextualized2020].
+<!-- The third and last question of this study is therefore as follows:  -->
+How large are the effects of external popularity cues such as like and dislike buttons compared to the internal weighing of pros and cons?
+And can the privacy calculus be manipulated by popularity cues?
 <!-- Third, in this study I approach the privacy calculus from the theoretical perspective of _bounded rationality_.  -->
@@
 <!-- I therefore extend the privacy calculus model theoretically by investigating the role and interplay of trust and self-efficacy. -->
-
 <!-- To answer these research questions, a representative sample of the German population was collected in a preregistered online field experiment. -->
@@
 
-## The Privacy Calculus
+## Replicating the Privacy Calculus
 
@@
 -->
-
 <!-- I therefore hypothesize that people who experience more privacy concerns engage in less communication online. -->
@@
 People are happy to trade in parts of their privacy when they can receive something more valuable in return [@lauferPrivacyConceptSocial1977].
-In online communication, the most important benefits include social support [@krasnovaOnlineSocialNetworks2010], social capital [@ellisonNegotiatingPrivacyConcerns2011], entertainment [@dhirUnderstandingRelationshipIntensity2017], information-seeking [@whitingWhyPeopleUse2013], and self-presentation [@minHowArePeople2015].
+In online communication, the most important benefits include social support [@krasnovaOnlineSocialNetworks2010], social capital [@ellisonBenefitsFacebookFriends2007], entertainment [@dhirUnderstandingRelationshipIntensity2017], information-seeking [@whitingWhyPeopleUse2013], and self-presentation [@minHowArePeople2015].
 <!-- As a result, we expect a moderate relationship. -->
@@
 
-Although privacy calculus implies that people explicitly compare benefits and drawbacks before communicating online, research has neglected this aspect [@knijnenburgDeathPrivacyCalculus2017].
+## Extending the Privacy Calculus
+
+Although privacy calculus implies that people explicitly compare benefits and drawbacks before communicating online, prior research has neglected this aspect [@knijnenburgDeathPrivacyCalculus2017].
 Only observing that privacy concerns or expected gratifications and communication online are related does not prove that an explicit weighing process took place [@knijnenburgDeathPrivacyCalculus2017].
@@
 <!-- Accordingly, privacy calculus would assume that people, when it comes to disclosing, engage in a central processing.  -->
-Self-disclosure theory [@omarzuDisclosureDecisionModel2000;  @altmanPrivacyConceptualAnalysis1976] suggests that if the benefits to be attained from communication are attractive, deciding whether or not to communicate is a "conscious and deliberative process"  [@omarzuDisclosureDecisionModel2000, p.
+Self-disclosure theory [@omarzuDisclosureDecisionModel2000;  @altmanPrivacyConceptualAnalysis1976] suggests that if the benefits of communication are attractive, deciding whether or not to communicate is a "conscious and deliberative process"  [@omarzuDisclosureDecisionModel2000, p.
 183].
@@
 On the other hand, deliberating about privacy might also increase communication.
-In light of the benefits mentioned above, would it not make sense to conclude that participation is beneficial, thereby fostering communication [@krasnovaOnlineSocialNetworks2010]?
+In light of the benefits mentioned above, it can make much sense to conclude that participation is beneficial, thereby fostering communication [@krasnovaOnlineSocialNetworks2010]?
 <!-- I therefore formulate the following research question: -->
@@
 1303].
-Although human behavior is partly irrational, bounded rationality does not state that it is completely irrational [@gigerenzerBoundedRationalityAdaptive2002].
+Importantly, although human behavior is _partly_ irrational, bounded rationality does not state that it is _completely_ irrational [@gigerenzerBoundedRationalityAdaptive2002].
 Rationality is a continuum. 
@@
 <!-- It is only that their capacity to do so is bounded. -->
-In the context of online privacy, for example, rationality is impeded by information asymmetries, presence bias, intangibility, illusory control, or herding [@acquistiSecretsLikesDrive2020].
+In the context of online privacy, rationality is impeded by information asymmetries, presence bias, intangibility, illusory control, or herding [@acquistiSecretsLikesDrive2020].
 It follows that to provide a more complete picture, additional factors next to gratifications and concerns should also explain communication.
@@
 
+Prior research suggests that two factors are most important to understand online communication: self-efficacy and trust [correaParticipationDivideOnline2010; hossainICTEnabledVirtual2004; @metzgerPrivacyTrustDisclosure2004].
 For example, if users are more familiar, experienced, and knowledgeable in a given online context, they are more likely to navigate that online contexts successfully and to communicate actively [@baruhOnlinePrivacyConcerns2017; @kramerMasteringChallengeBalancing2020].
@@
 
-In situations where people lack experience or competence, a relevant variable to understand behavior is _trust_.
-Especially in online contexts, users often cannot control the environment or the way their information is handled [@acquistiSecretsLikesDrive2020; @braunlichLinkingLooseEnds2020].
-Trust plays a key role in online communication [@metzgerPrivacyTrustDisclosure2004]. 
+In all situations where people lack experience, control, or competence, a central variable to understand behavior is _trust_ [@gefenTrustTAMOnline2003].
+Especially in online contexts, trust plays a key role [@metzgerPrivacyTrustDisclosure2004], as users often cannot control the environment or the way their information is handled [@acquistiSecretsLikesDrive2020; @braunlichLinkingLooseEnds2020].
 Trust either captures "_specific_ beliefs dealing primarily with the integrity, benevolence, and ability of another party" [@gefenTrustTAMOnline2003, p.
@@
 
-## The Effects of Popularity Cues
+## Analyzing the Impact of Popularity Cues
 
 How are the privacy calculus and communication affected by the context, the digital infrastructure? 
-In analyzing this question, it makes sense not to focus on specific features of particular websites, which change and become obsolete [@foxDistinguishingTechnologiesSocial2017]. 
-Instead, it is recommended focusing on the underlying latent structures by analyzing so-called _affordances_ [@ellisonSocialNetworkSite2015; @foxDistinguishingTechnologiesSocial2017].
+How easily can the calculus be affected externally?
+One of the central tools to afford and govern online behavior are so-called popularity cues such as like and dislike buttons [@stsiampkouskayaNotExperimentalStudy2023].
+Popularity cues have been shown to affect behavior [@kramerMasteringChallengeBalancing2020; @masurBehavioralContagionSocial2021; @treptePrivacyCalculusContextualized2020].
+Online comments that already have several dislikes are more likely to receive further dislikes [@muchnikSocialInfluenceBias2013]. 
+When users disagree with a post, they are more likely to click on a button labeled _respect_ compared to a button labeled _like_ [@stroudRecommendRespectAltering2017].
+
+How and why might popularity cues affect the privacy calculus?
+In analyzing this question, it makes sense to analyze the cues' underlying _affordances_ [@ellisonSocialNetworkSite2015; @foxDistinguishingTechnologiesSocial2017].
 Affordances are mental representations of how objects might be used.
@@
 <!-- The privacy calculus states that both benefits and costs determine behavior. -->
-Popularity cues such as like and dislike buttons, which are of interest here, are categorized as "paralinguistic digital affordances" [@carrPredictingThresholdPerceived2018, p. 142].
-
+Popularity cues such as like and dislike buttons are understood as "paralinguistic digital affordances" [@carrPredictingThresholdPerceived2018, p. 142].
 <!-- Both can be linked to the two sides of the privacy calculus.  -->
@@
 <!-- It expresses criticism and a way to downgrade content.  -->
-
-Paralinguistic digital affordances and specifically popularity cues have been shown to affect behavior [@kramerMasteringChallengeBalancing2020; @masurBehavioralContagionSocial2021; @treptePrivacyCalculusContextualized2020].
-Online comments that already have several dislikes are more likely to receive further dislikes [@muchnikSocialInfluenceBias2013]. 
-When users disagree with a post, they are more likely to click on a button labeled _respect_ compared to a button labeled _like_ [@stroudRecommendRespectAltering2017].
 <!-- In light of their potentially strong negative effects, most major social networking sites did not implement dislike buttons.  -->
 <!-- At the time of writing, only a handful of websites have (partially) implemented it (e.g., youtube, stackexchange, or reddit). -->
+
 Popularity cues likely impact the privacy calculus via two underlying theoretical mechanisms [@kramerMasteringChallengeBalancing2020]:
 First, the _mere presence_ of popularity cues might affect whether people are willing to disclose. 
-Being able to attract likes might motivate users to communicate, while the mere option to receive dislikes might intimidate others.
-Second, _actually receiving_ likes or dislikes might additionally affect subsequent behavior, thereby reinforcing the process [@skinnerScienceHumanBehavior2014].
-
-Likes are affirmative and represent the positivity bias of social media [@schreursExposurePositivityBias2022]. 
+Being able to attract likes might afford active communication. 
+The mere option to receive dislikes, conversely, might inhibit communication.
+Second, _actually receiving_ likes or dislikes might affect behavior, by means of positive reinforcement (likes) or punishment (dislikes) [@skinnerScienceHumanBehavior2014].
+To illustrate, likes are affirmative and represent the positivity bias of social media [@schreursExposurePositivityBias2022]. 
 Receiving a like online is similar to receiving a compliment offline [@carrPredictingThresholdPerceived2018; @sumnerFunctionalApproachFacebook2017].
@@
 Participants had to be above the age of 18 and had to live in Germany. 
-In a first step, the company sent its panel members an invitation to participate in the study (_invitation_). 
+In a first step, the company sent its panel members an invitation to participate in the study. 
 In this invitation, panel members were asked to participate in a study analyzing the current threat posed by terrorist attacks in Germany.
@@
 Afterward, participants were randomly assigned to one of the three websites. 
-After registration was completed, participants were invited (but not obliged) to visit the website and to discuss the topic of the terrorism threat in Germany (_field_). 
+After registration was completed, participants were invited (but not obliged) to visit the website and to discuss the topic of the terrorism threat in Germany. 
 Participants could use the website and write comments over the course of one week.
@@
 
-```{r website, echo=FALSE, out.width="49%", fig.cap="Screenshot of the landing page and of communication taking place", fig.show='hold', fig.align='center'}
+```{r website, echo=FALSE, out.width="49%", fig.cap="Screenshot of the landing page and of communication taking place. Translated into English.", fig.show='hold', fig.align='center'}
 knitr::include_graphics(c("figures/website/website_translated.png","figures/website/comments_translated.png"))
@@
 Sample size was determined using a priori power analyses.
-The power analyses were based on a smallest effect size of interest approach [SESOI, @lakensEquivalenceTestingPsychological2018]. 
+The power analyses were based on estimates from the literature.
 <!-- Namely, I defined a minimum effect size considered sufficiently large to support the hypotheses.  -->
 When researching aspects of privacy online [e.g., @baruhOnlinePrivacyConcerns2017], effects are often small [i.e., _r_ = .10, @cohenPowerPrimer1992].
-Hence, the SESOI was set to be _r_ = `r r_sesoi %>% my_round("std")`. 
+Hence, the minimum effect size was set to be _r_ = `r r_sesoi %>% my_round("std")`. 
 The aim was to be able to detect this SESOI with a probability of at least 95% (i.e., power = 95%).
@@
 One item was deleted due to poor psychometric properties.
+The mean was _m_ = `r facval_tab["Privacy concerns", "m"]`. This value is below the scale's midpoint of 4, showing that on average people were not strongly concerned about their privacy.
 
@@
 "learn things I would not have noticed otherwise" (information), "react to a subject that is important to me" (relevance), "engage politically" (political participation), "try to improve society" (idealism), and "soothe my guilty consciences" (extrinsic benefits).
+The means for both dimensions were _m_ = `r facval_tab["General gratifications", "m"]` (general gratifications) and _m_ = `r facval_tab["Specific gratifications", "m"]` (specific gratifications), which were above the scales midpoint.
+This shows that on average people considered the website to be beneficial.
 
@@
 One example item was "While using the participation platform I have weighed the advantages and disadvantages of writing a comment."
+The mean lay on the scale's neutral midpoint (_m_ = `r facval_tab["Privacy deliberation", "m"]`). For an interpretation, see below.
 
@@
 Two inverted items were deleted due to poor psychometric properties.
+People felt self-efficacious to use the website (_m_ = `r facval_tab["Self-efficacy", "m"]`).
 
@@
 Example items were "The operators of the participation platform have done a good job" (ability), "The other users had good intentions" (benevolence/integrity), "The website worked well" (reliability).
-Because they were closely related, the two targets "provider" and "website" were combined into one dimension. 
+Participants placed a lot of trust in the website, the providers and the other users (trust general: _m_ = `r facval_tab["Trust general", "m"]`; trust specific: _m_ = `r facval_tab["Trust specific", "m"]`.
+<!-- Because they were closely related, the two targets "provider" and "website" were combined into one dimension.  -->
 <!-- , as was evidenced by a Heywood case (i.e., standardized coefficient greater than 1).  -->
 <!-- I hence adapted the scale to combine these two targets.  -->
-The updated scale showed adequate fit.
+<!-- The updated scale showed adequate fit.  -->
 
 _Communication_ was calculated by counting the number of words each participant wrote in a comment.
-Communication was zero-inflated and heavily skewed.
-While `r round(no_words_perc * 100, 0)` percent did not communicate at all, some communicated a lot.
+Communication was zero-inflated and heavily skewed:
+While `r round(no_words_perc * 100, 0)` percent did not communicate at all, the maximum number of words communicated by a single user was `r d %$% words %>% max()` words.
 On average, participants wrote `r words_m %>% round(0)` words.
 
-## Data analysis
+## Data Analysis
 
@@
 Although it is possible to analyze non-normal data with structural equation modeling, it is recommended to use analyses that model the variables' distribution, which can be achieved with Bayesian hurdle models [@mcelreathStatisticalRethinkingBayesian2016].
-I conclusion, in the exploratory analyses I ran Bayesian hurdle regression models, modeling the outcome as a zero-inflated gamma distribution.
+I conclusion, in the exploratory analyses I ran Bayesian hurdle regression models, modeling the outcome as a zero-inflated gamma distribution using default (flat) priors [chains = 4, iterations = 2,000, warm-up = 1,000, @R-brms_a].
 Second, in the preregistered analyses several variables were combined that are theoretically and empirically closely related, leading to multicollinearity [@vanhoveCollinearityIsnDisease2021].
 As a remedy, I adopted a causal modeling perspective, controlling only for confounders---in this case, age, gender, and education---but not for mediators [@rohrerThinkingClearlyCorrelations2018]. 
-To assess the effects, I tested whether or not the 95% credibility intervals of the average marginal effects excluded zero.
+To assess the effects, I tested whether or not the 95% highest density intervals of the average marginal effects excluded zero.
 If they excluded zero, effects can be considered "significant" [@mcelreathStatisticalRethinkingBayesian2016]. 
 I also plotted the distribution of the effects.
-For more information, see [online companion website](https://XMtRa.github.io/like_dislike).
+For more information on the fitted models, see [online companion website](https://XMtRa.github.io/like_dislike).
 
@@
 
-## Exploratory analyses
+## Exploratory Analyses
 
@@
 If participants expected more gratifications from participation, they communicated more actively: 
-If their expected gratifications increased by one point, on average they also wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(Estimate) %>% round(0)` words more (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(UL) %>% round(0)`).
+If their expected gratifications increased by one point, on average they also wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(Estimate) %>% round(0)` words more (95% HDI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(UL) %>% round(0)`).
 If participants were more concerned about their privacy, they communicated less: 
-With each one-point increase in privacy concerns, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(Estimate) %>% round(0) %>% abs()` words fewer (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(UL) %>% round(0)`).
+With each one-point increase in privacy concerns, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(Estimate) %>% round(0) %>% abs()` words fewer (95% HDI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(UL) %>% round(0)`).
 If participants felt more self-efficacious, they also communicated much more:
-If their self-efficacy increased by one point, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Self-efficacy") %>%  select(Estimate) %>% round(0)` words more (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Self-efficacy") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Self-efficacy") %>%  select(UL) %>% round(0)`).
+If their self-efficacy increased by one point, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Self-efficacy") %>%  select(Estimate) %>% round(0)` words more (95% HDI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Self-efficacy") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Self-efficacy") %>%  select(UL) %>% round(0)`).
 The relationship was curvilinear, almost exponential: 
@@
 The more people deliberated about their privacy, the less they communicated.
-If privacy deliberation increased by one point, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy deliberation") %>%  select(Estimate) %>% round(0) %>% abs()` words less (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy deliberation") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy deliberation") %>%  select(UL) %>% round(0)`).
+If privacy deliberation increased by one point, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy deliberation") %>%  select(Estimate) %>% round(0) %>% abs()` words less (95% HDI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy deliberation") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy deliberation") %>%  select(UL) %>% round(0)`).
 
@@
 Compared to the control condition without popularity cues, implementing like buttons did not significantly affect communication, _b_ = `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like vs.
-control") %>%  select(Estimate) %>% round(0)` (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like vs.
+control") %>%  select(Estimate) %>% round(0)` (95% HDI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like vs.
 control") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like vs.
@@
 If both popularity cues were present, participants on average wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like & dislike vs.
-control") %>%  select(Estimate) %>% round(0) %>% abs()` words less (95% CI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like & dislike vs.
+control") %>%  select(Estimate) %>% round(0) %>% abs()` words less (95% HDI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like & dislike vs.
 control") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Like & dislike vs.
@@
 Plotted are the average marginal effects of the Bayesian hurdle models.
-The difference between the control group and like \\& disklike is significant.", fig.height=8, fig.width=8, out.width=".9\\textwidth", fig.align='center', fig.pos = "!h", warning=F}
+The difference between the control and the like \\& disklike group is significant.", fig.height=8, fig.width=8, out.width=".9\\textwidth", fig.align='center', fig.pos = "!h", warning=F}
 knitr::include_graphics("figures/results/effects.png")
@@
           , caption = "Effects of the privacy calculus variables and the popularity cues on communication. Credibility intervals exluding zero are considered significant."
-          , note = "CI = credibility interval, LL = lower level; UL = upper level. Reported are average marginal effects."
+          , note = "HDI = highest density interval, LL = lower level; UL = upper level. Reported are average marginal effects."
           , align = c("p{6cm}", rep("r", 3))
@@
 
-To address these shortcomings, in several exploratory analyses I conducted Bayesian hurdle-gamma models (see Data analysis).
+To address these shortcomings, in several exploratory analyses I conducted Bayesian hurdle-gamma models (see section Data analysis).
 <!-- To account for the data's distribution, I now ran Bayesian hurdle-gamma models,  -->
@@
 Although the effects were controlled for age, gender, and education, other variables not included could potentially bias the causal estimates presented here [@coenenIndirectEffectOmitted2022].
+In addition, not to reveal the study intention the self-reported measures were collected after the field phase. 
+<!-- , in which the dependent variable was measured. -->
+Demand effects might have led participants to align their answers to their prior behavior.
+As a result, the coefficients might overestimate the actual effects.
+
 <!-- The results do not allow for causal interpretation.  -->
@@
 <!-- In this case, it was not possible to send participants notifications when their comments were liked or disliked, which significantly decreased the popularity cues' salience. -->
-
-<!-- The self-reported measures were collected _after_ the field phase in which the dependent variable was measured.  -->
-<!-- As a result, the coefficients might overestimate the actual relations, because demand effects might have led participants to artificially align their theoretical answers with their practical behavior.
--->
 

### 2023-05-12 manuscript.RmD
- minor typos

@@
     The privacy calculus model states that people weigh risks and benefits before communicating online.
-This paper analyzes three open questions.
-How robust is the privacy calculus, can it be replicated with actual behavior in realistic online setting?
+This paper analyzes three questions.
+How robust is the privacy calculus, can it be replicated with actual behavior in realistic online settings?
 Do we need to extend the model by integrating more socio-psychological measures such as trust, self-efficacy, and privacy deliberation?
-How easily can the privacy calculus be be manipulated by external factors such as like and dislike buttons?
+How easily can the privacy calculus be manipulated by external factors such as like and dislike buttons?
 In a preregistered one-week field experiment (N = 590), participants discussed a current political topic on an online website, which included either (a) like buttons, (b) both like and dislike buttons, or (c) no buttons.
@@
 Experiencing self-efficacy and trust increased communication.
-Implementing both like and dislike buttons had a strong effect on behavior: It reduced online communication by 45 percent.
+Like and dislike buttons had a strong effect on behavior: They reduced communication by 45 percent.
 
@@
 classoption       : "man"
-# output            : papaja::apa6_pdf
-# header-includes:
-#   - \setlength{\parskip}{0em}
-#   - \raggedbottom
-#   - \note{\clearpage}
+output            : papaja::apa6_pdf
+header-includes:
+  - \setlength{\parskip}{0em}
+  - \raggedbottom
+  - \note{\clearpage}
 # output            : papaja::apa6_docx
-output:
-  html_document:
-    toc: TRUE
-    toc_float:
-      collapsed: FALSE
-    toc_depth: 2
+# output:
+#   html_document:
+#     toc: TRUE
+#     toc_float:
+#       collapsed: FALSE
+#     toc_depth: 2
 ---
@@
   note = "omega = Raykov's composite reliability coefficient omega; avevar = average variance extracted."
-  # , align = c("l", rep("r", 11))
+  , align = c("l", rep("r", 11))
   )
@@
           , note = "HDI = highest density interval, LL = lower level; UL = upper level. Reported are average marginal effects."
-          # , align = c("p{6cm}", rep("r", 3))
+          , align = c("p{6cm}", rep("r", 3))
           , digits = 0

### 2023-05-12 index.Rmd
minor updates re. formatting

@@
 On this website, you can find the companion material for the paper _Likes or Dislikes, Gratifications or Concerns?
-Analyzing the Effects of Popularity Cues on the Privacy Calculus in Online Communication_.
+A One-Week Field Experiment Analyzing the Effects of Popularity Cues on the Privacy Calculus in Online Communication_.
 
@@
 
-This website is produced directly from the project's [github repository](https://github.com/tdienlin/privacy_calc_exp).
+This website is produced directly from the project's [github repository](https://github.com/XMtRa/like_dislike/tree/main).
 You can download the material and the data, file an issue, or submit a pull request.

### 2023-05-12 manuscript.RmD
minor updates re. formatting

@@
 
-abstract: |
-    The privacy calculus model states that people weigh risks and benefits before communicating online.
+abstract          : "The privacy calculus model states that people weigh risks and benefits before communicating online.
 This paper analyzes three questions.
@@
 Experiencing self-efficacy and trust increased communication.
-Like and dislike buttons had a strong effect on behavior: They reduced communication by 45 percent.
+Like and dislike buttons had a strong effect on behavior: They reduced communication by 45 percent."
 
@@
 linenumbers       : yes
-mask              : yes
+mask              : no
 wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
 draft             : no
-documentclass     : "apa6"
+# output            : papaja::apa6_pdf
+# documentclass     : "apa6"
+documentclass     : "apa7"
 classoption       : "man"
-output            : papaja::apa6_pdf
-header-includes:
-  - \setlength{\parskip}{0em}
-  - \raggedbottom
-  - \note{\clearpage}
+# header-includes:
+#   - \setlength{\parskip}{0em}
+#   - \raggedbottom
+#   - \note{\clearpage}
+# header-includes:
+#   - |
+#     \makeatletter
+#     \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+#       {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+#       {-1em}%
+#       {\normalfont\normalsize\bfseries\typesectitle}}
+# 
+#     \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+#       {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+#       {-\z@\relax}%
+#       {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+#     \makeatother
+#     \usepackage{endnotes}
+#     \setlength{\parskip}{0em}
+#     \raggedbottom
+#     \note{\clearpage}
+# 
+# csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
 # output            : papaja::apa6_docx
-# output:
-#   html_document:
-#     toc: TRUE
-#     toc_float:
-#       collapsed: FALSE
-#     toc_depth: 2
+output:
+  html_document:
+    toc: TRUE
+    toc_float:
+      collapsed: FALSE
+    toc_depth: 2
 ---
@@
           , note = "HDI = highest density interval, LL = lower level; UL = upper level. Reported are average marginal effects."
-          , align = c("p{6cm}", rep("r", 3))
+          , align = c("l", rep("r", 3))
           , digits = 0

### 2023-06-05 manuscript.RmD
- small updates to theory and lit

--- 2023-05-12 manuscript.RmD
@@
 linenumbers       : yes
-mask              : yes
+mask              : no
 wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
 draft             : no
-documentclass     : "apa6"
-classoption       : "man"
-output            : papaja::apa6_pdf
-header-includes:
-  - \setlength{\parskip}{0em}
-  - \raggedbottom
-  - \note{\clearpage}
+# output            : papaja::apa6_pdf
+# documentclass     : "apa6"
+# header-includes:
+#   - \setlength{\parskip}{0em}
+#   - \raggedbottom
+#   - \note{\clearpage}
+# output            : papaja::apa6_pdf
+# documentclass     : "apa7"
+# classoption       : "man"
+# header-includes:
+#   - |
+#     \makeatletter
+#     \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+#       {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+#       {-1em}%
+#       {\normalfont\normalsize\bfseries\typesectitle}}
+# 
+#     \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+#       {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+#       {-\z@\relax}%
+#       {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+#     \makeatother
+#     \usepackage{endnotes}
+#     \setlength{\parskip}{0em}
+#     \raggedbottom
+#     \note{\clearpage}
+# 
+# csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
 # output            : papaja::apa6_docx
@@
 However, despite its popularity in both academic research [@dienlinPrivacyParadoxAus2019] and the public press [@newyorkpublicradioPrivacyParadox2018], empirical support for the privacy paradox is tenuous [@baruhOnlinePrivacyConcerns2017; @dienlinDoesPrivacyParadox2021].
-Research is increasingly building on the privacy calculus model, which states that communication online can be explained by perceived risks and expected benefits [@bolUnderstandingEffectsPersonalization2018b; @krasnovaOnlineSocialNetworks2010; @meierPrivacyCalculusRevisited2022].
+Research is increasingly building on the privacy calculus model, which states that communication online can be explained by perceived risks and expected benefits [@bolUnderstandingEffectsPersonalization2018; @krasnovaOnlineSocialNetworks2010; @meierPrivacyCalculusRevisited2022].
 
@@
 First, the privacy calculus' empirical foundation needs to be improved [@knijnenburgDeathPrivacyCalculus2017]. 
-To date, much research on the privacy calculus builds on (a) self-reports of behavior [@krasnovaOnlineSocialNetworks2010], (b) vignette approaches [@bolUnderstandingEffectsPersonalization2018b], or (c) one-shot experiments in the lab [@treptePrivacyCalculusContextualized2020].
+To date, much research on the privacy calculus builds on (a) self-reports of behavior [@krasnovaOnlineSocialNetworks2010], (b) vignette approaches [@bolUnderstandingEffectsPersonalization2018], or (c) one-shot experiments in the lab [@treptePrivacyCalculusContextualized2020].
 Self-reports are often unreliable measures of online behavior [@parrySystematicReviewMetaanalysis2021], vignette approaches have limited external validity, and one-shot experiments cannot analyze compound effects of sustained use.
@@
 People regulate their privacy by deciding what and what not to communicate [@dienlinPrivacyProcessModel2014].
-Disclosing information can be risky, and if people are more concerned about their privacy 
-they are less likely to communicate online [@baruhOnlinePrivacyConcerns2017; @krasnovaOnlineSocialNetworks2010; @masurUnderstandingEffectsConceptual2023; @meierPrivacyCalculusRevisited2022].
+Disclosing information can be risky, and if people with higher privacy needs and privacy concerns are less likely to communicate online [@baruhOnlinePrivacyConcerns2017; @krasnovaOnlineSocialNetworks2010; masurTransformativeNotHow2021; @meierPrivacyCalculusRevisited2022].
 According to a meta-analysis by @baruhOnlinePrivacyConcerns2017, the effect is small but significant (*r* = -.13).
 
-Outweighing concerns, the most relevant drivers of online communication are expected gratifications [@dienlinExtendedPrivacyCalculus2016a; @bolUnderstandingEffectsPersonalization2018b; @kezerGettingPrivacyCalculus2022].
+Outweighing concerns, the most relevant drivers of online communication are expected gratifications [@dienlinExtendedPrivacyCalculus2016; @bolUnderstandingEffectsPersonalization2018; @kezerGettingPrivacyCalculus2022].
 People are happy to trade in parts of their privacy when they can receive something more valuable in return [@lauferPrivacyConceptSocial1977].
-In online communication, the most important benefits include social support [@krasnovaOnlineSocialNetworks2010], social capital [@ellisonBenefitsFacebookFriends2007], entertainment [@dhirUnderstandingRelationshipIntensity2017], information-seeking [@whitingWhyPeopleUse2013], and self-presentation [@minHowArePeople2015].
+In online communication, the most important benefits include social support, social capital, entertainment, information-seeking, and self-presentation [@dhirUnderstandingRelationshipIntensity2017; @ellisonBenefitsFacebookFriends2007; @krasnovaOnlineSocialNetworks2010; whitingWhyPeopleUse2013].
 
@@
 
-Prior research suggests that perhaps the following two factors are most important when it comes to understanding online communication: self-efficacy and trust [@correaParticipationDivideOnline2010; @hossainICTEnabledVirtual2004; @metzgerPrivacyTrustDisclosure2004].
-For example, if users are more familiar, experienced, and knowledgeable in a given online context, they are more likely to navigate that online contexts successfully and to communicate actively [@baruhOnlinePrivacyConcerns2017; @kramerMasteringChallengeBalancing2020].
-People with more privacy self-efficacy also engage more successfully in self-withdrawal [@dienlinExtendedPrivacyCalculus2016a].
+The two factor perhaps most important when it comes to understanding online communication are self-efficacy and trust [@hossainICTEnabledVirtual2004; @metzgerPrivacyTrustDisclosure2004].
+Privacy violations create psychological distress [@ledbetterParentchildPrivacyBoundary2019], experiencing online contexts as a safe space that users can sufficiently control is important for engaging in online communication.
+If users are more familiar, experienced, and knowledgeable in a given online context, they are more likely to navigate that online contexts successfully and to communicate actively [@baruhOnlinePrivacyConcerns2017; @kramerMasteringChallengeBalancing2020].
+People with more privacy self-efficacy also engage more successfully in self-withdrawal [@dienlinExtendedPrivacyCalculus2016].
 Hence, if users possess more self-efficacy to participate, they should also communicate more.
@@
 They emphasize that it is not the _objective features_ that determine behavior, but rather our _subjective perceptions_ [@gibsonEcologicalApproachVisual2015].
-There is an ongoing debate on how to best understand and operationalize affordances [@evansExplicatingAffordancesConceptual2017].
-Whereas @evansExplicatingAffordancesConceptual2017 propose three affordances for mediated communication (i.e., anonymity, persistence, and visibility), @foxDistinguishingTechnologiesSocial2017 suggest 10 affordances for SNSs alone (i.e., accessibility, bandwidth, social presence, privacy, network association, personalization, persistence, editability, conversation control, and anonymity).
 Popularity cues such as like and dislike buttons, which are of primary interest in this study, are understood as "paralinguistic digital affordances" [@carrPredictingThresholdPerceived2018, p. 142].
@@
 As recommended by @klinePrinciplesPracticeStructural2016, to assess global fit I report the model's $\chi^2$, RMSEA (90% CI), CFI, and SRMR. 
-To exclude confounding influences, I controlled all variables for age, gender, and education, which have been shown to affect both privacy concerns and online communication [@masurUnderstandingEffectsConceptual2023; @tifferetGenderDifferencesPrivacy2019a].
+To exclude confounding influences, I controlled all variables for age, gender, and education, which have been shown to affect both privacy concerns and online communication [@tifferetGenderDifferencesPrivacy2019a].
 The preregistered hypotheses were tested with a one-sided significance level of 5%; the research questions were tested with a two-sided 5% significance level using family-wise Bonferroni-Holm correction.
@@
           , note = "HDI = highest density interval, LL = lower level; UL = upper level. Reported are average marginal effects."
-          , align = c("p{6cm}", rep("r", 3))
+          # , align = c("m{10cm}", rep("r", 3)) # use this for compiling pdfs
+          , align = c("l", rep("r", 3)) # use this for compiling htmls
           , digits = 0

### 2023-06-05 analyses_explorations.R
- small updates to website

@@ -1,241 +1,0 @@
-#### Preregistered
-
-```{r}
-fit_brms_hrdl_prereg <- 
-  brm(
-    bf(
-      COMM ~ 
-        1 + 
-        pri_con_fs + 
-        grats_spec_fs + 
-        pri_del_fs + 
-        trust_gen_fs +
-        self_eff_fs +
-        age + 
-        male + 
-        edu, 
-      hu ~ 
-        1 + 
-        pri_con_fs + 
-        grats_spec_fs + 
-        pri_del_fs + 
-        trust_gen_fs +
-        self_eff_fs +
-        age + 
-        male + 
-        edu
-    ), 
-    data = d, 
-    family = hurdle_gamma()
-  )
-
-```
-
-
-```{r}
-plot(fit_brms_hrdl_prereg, ask = FALSE)
-```
-
-```{r}
-model_diagnostics(fit_brms_hrdl_prereg)
-```
-
-```{r}
-summary(fit_brms_hrdl_prereg)
-```
-
-```{r}
-conditional_effects(fit_brms_hrdl_prereg, ask = FALSE)
-```
-
-#### Adapted
-
-```{r}
-fit_brms_hrdl_adapted <- 
-  brm(
-    bf(
-      COMM ~ 
-        1 + 
-        pri_con_fs + 
-        grats_spec_fs + 
-        pri_del_fs + 
-        self_eff_fs +
-        age + 
-        male + 
-        edu, 
-      hu ~ 
-        1 + 
-        pri_con_fs + 
-        grats_spec_fs + 
-        pri_del_fs + 
-        self_eff_fs +
-        age + 
-        male + 
-        edu
-    ), 
-    data = d, 
-    family = hurdle_gamma()
-  )
-
-```
-
-
-```{r}
-plot(fit_brms_hrdl_adapted, ask = FALSE)
-```
-
-```{r}
-model_diagnostics(fit_brms_hrdl_adapted)
-```
-
-```{r}
-summary(fit_brms_hrdl_adapted)
-```
-
-```{r}
-conditional_effects(fit_brms_hrdl_adapted, ask = FALSE)
-```
-
-#### 3-way Interaction
-
-```{r}
-fit_brms_hrdl_inter <- 
-  brm(
-    bf(
-      COMM ~ 
-        1 + 
-        pri_con_fs_c * 
-        grats_spec_fs_c * 
-        pri_del_fs_c + 
-        self_eff_fs_c +
-        age_c + 
[…]

### 2023-06-07 manuscript.RmD
- updated lit

@@
 linenumbers       : yes
-mask              : no
+mask              : yes
 wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
@@
 # output            : papaja::apa6_docx
-# output:
-#   html_document:
-#     toc: TRUE
-#     toc_float:
-#       collapsed: FALSE
-#     toc_depth: 2
+output:
+  html_document:
+    toc: TRUE
+    toc_float:
+      collapsed: FALSE
+      toc_depth: 2
 ---
@@
 People communicate much personal information online, although being strongly concerned about their privacy [@taddickenUsesPrivacyOnline2011].
-However, despite its popularity in both academic research [@dienlinPrivacyParadoxAus2019] and the public press [@newyorkpublicradioPrivacyParadox2018], empirical support for the privacy paradox is tenuous [@baruhOnlinePrivacyConcerns2017; @dienlinDoesPrivacyParadox2021].
-Research is increasingly building on the privacy calculus model, which states that communication online can be explained by perceived risks and expected benefits [@bolUnderstandingEffectsPersonalization2018; @krasnovaOnlineSocialNetworks2010; @meierPrivacyCalculusRevisited2022].
+However, despite its popularity in both academic research [@masurUnderstandingEffectsConceptual2023] and the public press [@newyorkpublicradioPrivacyParadox2018], empirical support for the privacy paradox is tenuous [@baruhOnlinePrivacyConcerns2017; @dienlinDoesPrivacyParadox2021].
+Research is increasingly building on the privacy calculus model, which states that communication online can be explained by perceived risks and expected benefits [@bolUnderstandingEffectsPersonalization2018; @krasnovaOnlineSocialNetworks2010].
 
@@
 People regulate their privacy by deciding what and what not to communicate [@dienlinPrivacyProcessModel2014].
-Disclosing information can be risky, and if people with higher privacy needs and privacy concerns are less likely to communicate online [@baruhOnlinePrivacyConcerns2017; @krasnovaOnlineSocialNetworks2010; masurTransformativeNotHow2021; @meierPrivacyCalculusRevisited2022].
+Disclosing information can be risky, and if people with higher privacy needs and privacy concerns are less likely to communicate online [@baruhOnlinePrivacyConcerns2017; @krasnovaOnlineSocialNetworks2010; @masurTransformativeNotHow2021; @masurUnderstandingEffectsConceptual2023].
 According to a meta-analysis by @baruhOnlinePrivacyConcerns2017, the effect is small but significant (*r* = -.13).
+Similarly, people who are more concerned about their privacy also engage in more privacy protection behaviors [@baruhOnlinePrivacyConcerns2017; @stubenvollLivingEasyEyes2022].
 
@@
 People are happy to trade in parts of their privacy when they can receive something more valuable in return [@lauferPrivacyConceptSocial1977].
-In online communication, the most important benefits include social support, social capital, entertainment, information-seeking, and self-presentation [@dhirUnderstandingRelationshipIntensity2017; @ellisonBenefitsFacebookFriends2007; @krasnovaOnlineSocialNetworks2010; whitingWhyPeopleUse2013].
+In online communication, the most important benefits include social support, social capital, entertainment, information-seeking, and self-presentation [@dhirUnderstandingRelationshipIntensity2017; @ellisonBenefitsFacebookFriends2007; @krasnovaOnlineSocialNetworks2010; @whitingWhyPeopleUse2013].
 
@@
 1303].
-Importantly, although human behavior is _partly_ irrational, bounded rationality does not state that it is _completely_ irrational [@gigerenzerBoundedRationalityAdaptive2002].
-Rationality is a continuum. 
+Although human behavior is considered partly irrational, bounded rationality does not state that it is completely irrational [@gigerenzerBoundedRationalityAdaptive2002].
+Rationality can hence be understood to exist on a continuum. 
 In the context of online privacy, rationality is impeded by information asymmetries, presence bias, intangibility, illusory control, or herding [@acquistiSecretsLikesDrive2020].
@@
 Privacy violations create psychological distress [@ledbetterParentchildPrivacyBoundary2019], experiencing online contexts as a safe space that users can sufficiently control is important for engaging in online communication.
-If users are more familiar, experienced, and knowledgeable in a given online context, they are more likely to navigate that online contexts successfully and to communicate actively [@baruhOnlinePrivacyConcerns2017; @kramerMasteringChallengeBalancing2020].
-People with more privacy self-efficacy also engage more successfully in self-withdrawal [@dienlinExtendedPrivacyCalculus2016].
-Hence, if users possess more self-efficacy to participate, they should also communicate more.
+If users are more familiar, experienced, and knowledgeable in a given online context, they are more likely to navigate that online contexts successfully and to communicate actively [@baruhOnlinePrivacyConcerns2017; @kramerMasteringChallengeBalancing2020; @parkDigitalLiteracyPrivacy2013a].
+People with more privacy self-efficacy engage more successfully in self-withdrawal [@dienlinExtendedPrivacyCalculus2016] and protective online behavior [@boermanExploringMotivationsOnline2021a; @vanooijenPrivacyCynicismIts2022].
+Hence, if users possess more self-efficacy to participate, they should also communicate more, and to more fully capture online behavior self-efficacy should hence be included.
 
@@
 In all situations where people lack experience, control, or competence, a central variable to understand behavior is trust [@gefenTrustTAMOnline2003].
-Especially in online contexts, trust plays a key role [@metzgerPrivacyTrustDisclosure2004].
+Especially in online contexts, trust plays a key role [@metzgerPrivacyTrustDisclosure2004; @metzgerEffectsSiteVendor2006a].
 Users often cannot control the environment or the way their information is handled [@acquistiSecretsLikesDrive2020; @braunlichLinkingLooseEnds2020].
@@
 People who put more trust in the providers of networks, for example, disclose more personal information [@liEmpiricalStudiesOnline2011]. 
+To comprehensively capture and understand online communication, trust should hence be included.
 
@@
 As recommended by @klinePrinciplesPracticeStructural2016, to assess global fit I report the model's $\chi^2$, RMSEA (90% CI), CFI, and SRMR. 
-To exclude confounding influences, I controlled all variables for age, gender, and education, which have been shown to affect both privacy concerns and online communication [@tifferetGenderDifferencesPrivacy2019a].
+To exclude confounding influences, I controlled all variables for age, gender, and education, which have been shown to affect both privacy concerns and online communication [@masurUnderstandingEffectsConceptual2023; @tifferetGenderDifferencesPrivacy2019a].
 The preregistered hypotheses were tested with a one-sided significance level of 5%; the research questions were tested with a two-sided 5% significance level using family-wise Bonferroni-Holm correction.
@@
 Attaining benefits online is hence a strong predictor of online communication.
-Together, the results provide further support for the privacy calculus and against the privacy paradox [@baruhOnlinePrivacyConcerns2017; @dienlinPrivacyParadoxAus2019].
+Together, the results provide further support for the privacy calculus and against the privacy paradox [@baruhOnlinePrivacyConcerns2017].
 Communication online does not seem to be overly illogical. 

### 2023-11-07 analyses.Rmd
- integrated reviewer feedback

@@
           silent = TRUE,
-          refresh = 0
+          refresh = 0,
+          iter = 1000,
+          backend = "cmdstanr"
           )
@@
   "Privacy concerns", 
-  "General gratifications", 
-  "Specific gratifications",
+  "Gratifications general", 
+  "Gratifications specific",
   "Privacy deliberation", 
   "Self-efficacy", 
-  "General trust", 
-  "Specific trust",
+  "Trust general", 
+  "Trust specific",
   "Words log"
@@
   "Privacy\nconcerns", 
-  "General\ngratifications", 
-  "Specific\ngratifications",
+  "Gratifications\ngeneral", 
+  "Gratifications\nspecific",
   "Privacy\ndeliberation", 
   "Self-\nefficacy", 
-  "General\ntrust", 
-  "Specific\ntrust",
+  "Trust\ngeneral", 
+  "Trust\nspecific",
   "Words (log)"
@@
 
-```{r}
+```{r words}
 run_hurdles(
@@
 
-```{r}
+```{r words-lkdslk}
 run_hurdles(
@@
 
-```{r}
+```{r pricon-ctrl}
 run_hurdles(
@@
 
-#### Expected Gratifications
+#### Gratifications General
 
@@
   predictor = "version",
-  y_lab = "Gratifications",
+  y_lab = "Gratifications general",
   x_lab = "Experimental conditions"
@@
 
-#### Trust
+#### Trust general
 
@@
   predictor = "version",
-  y_lab = "Trust",
+  y_lab = "Trust general",
   x_lab = "Experimental conditions"
@@
   predictor = "version_lkdslk",
-  y_lab = "Trust",
+  y_lab = "Trust general",
   x_lab = "Experimental conditions"
@@
   y_lab = "Words",
-  x_lab = "Expected gratifications"
+  x_lab = "Gratifications general"
   )
@@
 
-#### Trust
+#### Trust General
 
@@
   y_lab = "Words",
-  x_lab = "Trust"
+  x_lab = "Trust general"
   )
@@
   y_lab = "Words",
-  x_lab = "Self-Efficacy"
+  x_lab = "Self-efficacy"
   )
@@
 
+# Save visualizations
 ggsave("figures/results/effects.pdf")

### 2023-11-07 manuscript.RmD
- integrated reviewer feedback

@@
 mask              : yes
-wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
+wordcount         : "8,187"
 draft             : no
@@
 People regulate their privacy by deciding what and what not to communicate [@dienlinPrivacyProcessModel2014].
-Disclosing information can be risky, and if people with higher privacy needs and privacy concerns are less likely to communicate online [@baruhOnlinePrivacyConcerns2017; @krasnovaOnlineSocialNetworks2010; @masurTransformativeNotHow2021; @masurUnderstandingEffectsConceptual2023].
-According to a meta-analysis by @baruhOnlinePrivacyConcerns2017, the effect is small but significant (*r* = -.13).
+Sharing information carries risks, as recipients may reuse it in different contexts, potentially harming the original sender [@masurBehavioralContagionSocial2021].
+As a result, people who aim to avoid risks should be included to share less information, especially in online contexts where audiences are much larger [@vitakImpactContextCollapse2012].
+Indeed, empirical research confirms that people with higher privacy needs and privacy concerns are less likely to communicate online [@krasnovaOnlineSocialNetworks2010; @masurTransformativeNotHow2021; @masurUnderstandingEffectsConceptual2023].
+This finding is now confirmed by several meta-analyses and reviews [@baruhOnlinePrivacyConcerns2017; @dienlinDoesPrivacyParadox2021; @gerberExplainingPrivacyParadox2018].
 Similarly, people who are more concerned about their privacy also engage in more privacy protection behaviors [@baruhOnlinePrivacyConcerns2017; @stubenvollLivingEasyEyes2022].
@@
 Only observing that privacy concerns or expected gratifications and communication online are related does not prove that an explicit weighing process took place [@knijnenburgDeathPrivacyCalculus2017].
-Instead, we need to analyze if, and if so by how much, people actively deliberate about their privacy, and whether doing so influences their decision to communicate.
+Instead, we need to analyze if, and if so by how much, people actively deliberate about their privacy, and whether doing so influences their willingness to communicate.
 Self-disclosure theory [@omarzuDisclosureDecisionModel2000;  @altmanPrivacyConceptualAnalysis1976] suggests that if the benefits of communication are attractive, deciding whether or not to communicate is a "conscious and deliberative process"  [@omarzuDisclosureDecisionModel2000, p.
@@
 Actively thinking about whether communicating is worthwhile might be the first step not to participate.
+In addition, actively reflecting about one's behavior represents a central and Type 2 approach toward decision making, which is often associated with more critical and cautious behavior [@kahnemanThinkingFastSlow2011; @pettyCommunicationPersuasionCentral1986].
+
 On the other hand, deliberating about privacy might also increase communication. 
+The default behavior in online contexts is passively browsing the content, but not actively engaging in communication [@ozimekActivePassiveBehavior2023]. 
+Especially in new contexts without prior experience, actively pondering one's options might trigger users to leave their default state of passiveness and to become active and involved.
 In light of the numerous benefits mentioned above, it might make sense to conclude that participation is beneficial, thereby fostering communication [@krasnovaOnlineSocialNetworks2010].
@@
 
-The aforementioned weighing process is not flawless or perfect.
+<!-- The aforementioned weighing process is not flawless or perfect. -->
 It is useful to understand the privacy calculus from the perspective of _bounded rationality_ [@simonBoundedRationality1990].
@@
 
-The two factor perhaps most important when it comes to understanding online communication are self-efficacy and trust [@hossainICTEnabledVirtual2004; @metzgerPrivacyTrustDisclosure2004].
+The two factors perhaps most important when it comes to understanding online communication are self-efficacy and trust [@hossainICTEnabledVirtual2004; @metzgerPrivacyTrustDisclosure2004].
 Privacy violations create psychological distress [@ledbetterParentchildPrivacyBoundary2019], experiencing online contexts as a safe space that users can sufficiently control is important for engaging in online communication.
@@
 These gains can be garnered only through active participation. 
+In situations where people can gain immediate positive outcomes, concerns and risks that are more vague and in the future often become less relevant [@ainslieHyperbolicDiscounting1992].
 Because like buttons emphasize positive outcomes, it is likely that concerns decrease. 
@@
 
-H5.	People who use a website with like buttons (a) communicate more, (b) obtain more gratifications, (c) are less concerned about their privacy, and (d) deliberate more about whether they should communicate online.
+H5.	Compared to a control group with no like and dislike buttons, people who use a website with like buttons (a) communicate more; (b) obtain more gratifications; (c) are less concerned about their privacy; and (d) deliberate more about whether they should communicate online.
 
-H6.	People who use a website with like _and_ dislike buttons (a) communicate more, (b) obtain more gratifications, and (c) deliberate more about whether they should communicate online.
+H6.	Compared to a control group with no like and dislike buttons, people who use a website with like _and_ dislike buttons (a) communicate more; (b) obtain more gratifications; and (c) deliberate more about whether they should communicate online.
 
@@
 The final sample included _N_ = `r n_final` participants.
-The sample characteristics at T1 and T2 were as follows: 
+The sample characteristics at T1 and T2 were as follows.
 T1: age = `r round(age_t1_m, 0)` years, gender = `r round(male_t1_m, 2)*100`% male, college degree = `r round(college_t1_m, 2)*100`%.
@@
 "learn things I would not have noticed otherwise" (information), "react to a subject that is important to me" (relevance), "engage politically" (political participation), "try to improve society" (idealism), and "soothe my guilty consciences" (extrinsic benefits).
-The means for both dimensions were _m_ = `r facval_tab["General gratifications", "m"]` (general gratifications) and _m_ = `r facval_tab["Specific gratifications", "m"]` (specific gratifications), which were above the scales' midpoint.
+The means for both dimensions were _m_ = `r facval_tab["Gratifications general", "m"]` (general gratifications) and _m_ = `r facval_tab["Gratifications specific", "m"]` (specific gratifications), which were above the scales' midpoint.
 This shows that on average people considered the website to be beneficial.
@@
 Example items were "The operators of the participation platform have done a good job" (ability), "The other users had good intentions" (benevolence/integrity), "The website worked well" (reliability).
-Participants placed a lot of trust in the website, the providers and the other users (trust general: _m_ = `r facval_tab["General trust", "m"]`; trust specific: _m_ = `r facval_tab["Specific trust", "m"]`).
+Participants placed a lot of trust in the website, the providers and the other users (trust general: _m_ = `r facval_tab["Trust general", "m"]`; trust specific: _m_ = `r facval_tab["Trust specific", "m"]`).
 
@@
 Although it is possible to analyze non-normal data with structural equation modeling, it is recommended to use analyses that model the variables' distribution, which can be achieved with Bayesian hurdle models [@mcelreathStatisticalRethinkingBayesian2016].
-I conclusion, in the exploratory analyses I ran Bayesian hurdle regression models, modeling the outcome as a zero-inflated gamma distribution using default (flat) priors [chains = 4, iterations = 2,000, warm-up = 1,000, @R-brms_a].
+In conclusion, in the exploratory analyses I ran (unstandardized) Bayesian hurdle regression models, modeling the outcome as a zero-inflated gamma distribution using default (flat) priors [chains = 4, iterations = 2,000, warm-up = 1,000, @R-brms_a].
 Second, in the preregistered analyses several variables were combined that are theoretically and empirically closely related, leading to multicollinearity [@vanhoveCollinearityIsnDisease2021].
@@
 The bivariate results showed three large correlations: 
-specific trust and general gratifications (_r_ = `r d_fs %>% select("Specific\ntrust", "General\ngratifications") %>% cor %>% .[2, 1] %>% my_round("std")`), 
+specific trust and general gratifications (_r_ = `r d_fs %>% select("Trust\nspecific", "Gratifications\ngeneral") %>% cor %>% .[2, 1] %>% my_round("std")`), 
 privacy concerns and privacy deliberation (_r_ = `r d_fs %>% select("Privacy\nconcerns", "Privacy\ndeliberation") %>% cor %>% .[2, 1] %>% my_round("std")`),
-and specific gratifications and self-efficacy (_r_ = `r d_fs %>% select("Specific\ngratifications", "Self-\nefficacy") %>% cor %>% .[2, 1] %>% my_round("std")`). 
+and specific gratifications and self-efficacy (_r_ = `r d_fs %>% select("Gratifications\nspecific", "Self-\nefficacy") %>% cor %>% .[2, 1] %>% my_round("std")`). 
 As all six variables were later analyzed within a single multiple regression, problems of multicollinearity might occur.
@@
 
-```{r popularitycues, fig.cap="Overview of the model-predicted values for each variable, separated for the three websites.
+```{r popularitycues, fig.cap="Distributions and means with 95% CIs of the model-predicted values for each variable, separated for the three websites.
 Control: Website without buttons.
@@
 I hence updated the analyses, using Bayesian hurdle models controlling only for confounders but not mediators.
+In predicting communication, I opted for general trust over specific trust, as it exhibited lower levels of empirical and theoretical overlap with gratifications.
 The updated exploratory analyses showed different results.
@@
           , col_spanners = list(
-            "HDI" = c(3, 4)
+            "95\\% HDI" = c(3, 4)
           )
           , font_size = "footnotesize"
-          , caption = "Effects of the privacy calculus variables and the popularity cues on communication. Credibility intervals exluding zero are considered significant."
+          , caption = "Unstandardized effects of the privacy calculus variables and the popularity cues on communication. Credibility intervals excluding zero are considered significant."
           , note = "HDI = highest density interval, LL = lower level; UL = upper level. Reported are average marginal effects."
           # , align = c("m{10cm}", rep("r", 3)) # use this for compiling pdfs
-          , align = c("l", rep("r", 3)) # use this for compiling htmls
+          # , align = c("l", rep("r", 3)) # use this for compiling htmls
           , digits = 0
@@
 The preregistered analyses showed that the popularity cues did not affect communication. 
-Only trust emerged as a significant predictor of online communication.
+Only self-efficacy emerged as a significant predictor of online communication.
 All other variables remained insignificant.
@@
 Demand effects might have led participants to align their answers to their prior behavior.
+To illustrate, users who communicated more actively might have experienced more self-efficacy afterward.
 As a result, the coefficients might overestimate the actual effects.
@@
 This study provides further support for the privacy calculus model and against the privacy paradox approach.
-Expected benefits, privacy concerns, comparing benefits and risks, trust, and self-efficacy all affected communication.
+Expected benefits, privacy concerns, deliberating about benefits and risks, trust, and self-efficacy all affected communication.
 Like and dislike buttons reduced communication significantly.

### 2024-07-10 analyses.Rmd
- updated manuscript - removed typos - extended theory

@@
 # install github packages
-# devtools::install_github("tdienlin/td@v.0.0.2.3")  # uncomment to install
+# devtools::install_github("tdienlin/td@v0.0.2.6")  # uncomment to install
 # devtools::install_github("yrosseel/lavaan")
@@
 lapply(
-  packages, 
-  library, 
-  character.only = TRUE, 
-  quietly = TRUE
+  packages
+  # , install.packages
+  , library
+  , character.only = TRUE
+  , quietly = TRUE
   )
@@
     fit, 
-    reliability = TRUE, 
-    scaled = TRUE
+    # reliability = TRUE, 
+    # scaled = TRUE
     ) %T>%
   print()
-
-# export factor validity
-assign(
-  paste0(
-    name, 
-    "_facval"
-    ), 
-  facval
-  )
 ```
@@
     fit, 
-    reliability = TRUE, 
-    scaled = TRUE
+    # reliability = TRUE, 
+    # scaled = TRUE
     ) %T>% 
@@
     fit, 
-    reliability = TRUE, 
-    scaled = TRUE
+    # reliability = TRUE, 
+    # scaled = TRUE
     ) %T>%
@@
     grats_gen_fs = rowMeans(select(., starts_with("GR02"))),
-    grats_spec_fs = rowMeans(select(., starts_with("GR01"))), 
+    # grats_spec_fs = rowMeans(select(., starts_with("GR01"))), 
     pri_con_fs = rowMeans(select(., starts_with("PC01"))),
@@
     grats_gen_fs, 
-    grats_spec_fs, 
+    # grats_spec_fs, 
     pri_del_fs, 
@@
     des_gratsgen,
-    des_gratsspec,
+    # des_gratsspec,
     des_pridel,
@@
     gratsgen_facval,
-    gratsspec_facval,
+    # gratsspec_facval,
     pridel_facval,
@@
   set_rownames(
-    var_names[-c(8)]
+    var_names[-c(7)]
     )
@@
   kable() %>% 
-  kable_styling("striped") %>% 
-  scroll_box(width = "100%")
+  kableExtra::kable_styling("striped") %>% 
+  kableExtra::scroll_box(width = "100%")
 ```

### 2024-07-10 manuscript.RmD
- updated manuscript - removed typos - extended theory

@@
 abstract          : "The privacy calculus model states that people weigh risks and benefits before communicating online.
-This paper analyzes three questions.
-How robust is the privacy calculus, can it be replicated with actual behavior in realistic online settings?
+This paper analyzes three questions: How robust is the privacy calculus, can it be replicated with actual behavior in realistic online settings?
 Do we need to extend the model by integrating more socio-psychological measures such as trust, self-efficacy, and privacy deliberation?
-How easily can the privacy calculus be manipulated by external factors such as like and dislike buttons?
+How strongly is the privacy calculus affected by affordances such as like and dislike buttons?
 In a preregistered one-week field experiment (N = 590), participants discussed a current political topic on an online website, which included either (a) like buttons, (b) both like and dislike buttons, or (c) no buttons.
 The privacy calculus model was confirmed: Benefits and concerns affected communication.
-Deliberating about privacy by comparing benefits and risks decreased communication.
-Experiencing self-efficacy and trust increased communication.
-Like and dislike buttons had a strong effect on behavior: They reduced communication by 45 percent."
+Deliberating about privacy by comparing benefits and risks decreased communication, whereas experiencing self-efficacy and trust increased communication.
+Although like and dislike buttons did not affect concerns, experiences, trust, efficacy, and deliberation, they had a strong effect on behavior: They reduced communication by 45 percent."
 
@@
 footnotelist      : no
-linenumbers       : yes
+linenumbers       : no
 mask              : yes
-wordcount         : "8,187"
+wordcount         : "8,204"
 draft             : no
-# output            : papaja::apa6_pdf
-# documentclass     : "apa6"
-# header-includes:
-#   - \setlength{\parskip}{0em}
-#   - \raggedbottom
-#   - \note{\clearpage}
-# output            : papaja::apa6_pdf
-# documentclass     : "apa7"
-# classoption       : "man"
-# header-includes:
-#   - |
-#     \makeatletter
-#     \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-#       {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-#       {-1em}%
-#       {\normalfont\normalsize\bfseries\typesectitle}}
-# 
-#     \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
-#       {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-#       {-\z@\relax}%
-#       {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
-#     \makeatother
-#     \usepackage{endnotes}
-#     \setlength{\parskip}{0em}
-#     \raggedbottom
-#     \note{\clearpage}
-# 
-# csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
-# output            : papaja::apa6_docx
-output:
-  html_document:
-    toc: TRUE
-    toc_float:
-      collapsed: FALSE
-      toc_depth: 2
+output            : papaja::apa6_pdf
+documentclass     : "apa7"
+classoption       : "man"
+header-includes:
+  - |
+    \makeatletter
+    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-1em}%
+      {\normalfont\normalsize\bfseries\typesectitle}}
+
+    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-\z@\relax}%
+      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+    \makeatother
+    \usepackage{endnotes}
+    \setlength{\parskip}{0em}
+    \raggedbottom
+    \note{\clearpage}
+
+csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
+# output:
+#   html_document:
+#     toc: TRUE
+#     toc_float:
+#       collapsed: FALSE
+#       toc_depth: 2
 ---
@@
   lapply(
-    pcks, 
-    library, 
-    character.only = TRUE
+    pcks 
+    # , install.packages
+    , library
+    , character.only = TRUE
     )
@@
 According to the privacy paradox, the way users share information online is erratic [@barnesPrivacyParadoxSocial2006]:
-People communicate much personal information online, although being strongly concerned about their privacy [@taddickenUsesPrivacyOnline2011].
-However, despite its popularity in both academic research [@masurUnderstandingEffectsConceptual2023] and the public press [@newyorkpublicradioPrivacyParadox2018], empirical support for the privacy paradox is tenuous [@baruhOnlinePrivacyConcerns2017; @dienlinDoesPrivacyParadox2021].
-Research is increasingly building on the privacy calculus model, which states that communication online can be explained by perceived risks and expected benefits [@bolUnderstandingEffectsPersonalization2018; @krasnovaOnlineSocialNetworks2010].
+Although being strongly concerned about their privacy, people communicate much personal information online  [@taddickenUsesPrivacyOnline2011].
+However, despite its popularity in both academic research [@masurUnderstandingEffectsConceptual2023] and the public press [@newyorkpublicradioPrivacyParadox2018], empirical support for the privacy paradox is tenuous [@baruhOnlinePrivacyConcerns2017].
+Research is increasingly building on the privacy calculus model [@dienlinPrivacyCalculusTheories2023], which states that communication online can be explained by perceived risks and expected benefits [@bolUnderstandingEffectsPersonalization2018; @krasnovaOnlineSocialNetworks2010].
 
@@
 To date, much research on the privacy calculus builds on (a) self-reports of behavior [@krasnovaOnlineSocialNetworks2010], (b) vignette approaches [@bolUnderstandingEffectsPersonalization2018], or (c) one-shot experiments in the lab [@treptePrivacyCalculusContextualized2020].
-Self-reports are often unreliable measures of online behavior [@parrySystematicReviewMetaanalysis2021], vignette approaches have limited external validity, and one-shot experiments cannot analyze compound effects of sustained use.
+Self-reports are often unreliable measures of online behavior [@parrySystematicReviewMetaanalysis2021], vignette approaches have limited external validity, and one-shot experiments cannot analyze effects of sustained use.
 The first aim is therefore to replicate the privacy calculus model in a more authentic and long-term setting using actual behavioral data.
@@
 Second, the privacy calculus model is criticized for neglecting the actual process of weighing pros and cons, and for over-emphasizing rationality  [@knijnenburgDeathPrivacyCalculus2017].
-Simply showing that both concerns and gratifications correlate with communication online does not prove that an explicit weighing process took place.
-Instead, we need to find out if people deliberately compare costs and benefits before communicating online. 
+According to critics, simply showing that both concerns and gratifications correlate with communication online does not prove that an explicit weighing process took place.
+Instead, we would need to find out if people deliberately compare costs and benefits before communicating online. 
 Therefore, I will also analyze the process of comparing pros and cons explicitly, by elaborating on what I will call the the privacy deliberation process [@omarzuDisclosureDecisionModel2000]. 
-Next, focusing exclusively on costs and benefits does not fully capture how and why users engage online.
-I, hence, extend the privacy calculus by analyzing how online communication is affected by trust and self-efficacy, two variables less focused on rationality and more oriented toward socio-psychological aspects [@metzgerPrivacyTrustDisclosure2004].
+Next, focusing exclusively on costs and benefits might not fully capture how and why users engage online.
+I, hence, extend the privacy calculus by analyzing how online communication is affected by trust and self-efficacy, two variables less focused on rationality and more oriented toward socio-psychological aspects critical in online contexts [@metzgerPrivacyTrustDisclosure2004].
 
 Online behavior is determined by the person itself and their external circumstances [@bazarovaIntegrationIndividualisticNetworked2020; @treptePrivacyCalculusContextualized2020; @spottswoodShouldShareThat2017].
-The privacy calculus upholds that much of behavior is rational and self-determined, but how easily can this process be manipulated by external circumstances?
-Online contexts are optimized to elicit as much interaction as possible [@ellisonSocialNetworkSite2015; @masurBehavioralContagionSocial2021], for example via low threshold communication features such as likes, shares, replies, or reactions  [@carrPredictingThresholdPerceived2018].
-Implicit and explicit cues on how a website is used can increase self-disclosure [@spottswoodShouldShareThat2017; @treptePrivacyCalculusContextualized2020].
+The privacy calculus upholds that much of behavior is rational and self-determined, but how strongly does this process depend on online affordances?
+It is well known that the affordances of many online services are optimized to elicit as much interaction as possible [@ellisonSocialNetworkSite2015; @masurBehavioralContagionSocial2021], for example via low threshold communication features such as likes, shares, replies, or reactions  [@carrPredictingThresholdPerceived2018].
+Implicit and explicit cues on how a website is used can increase communication [@spottswoodShouldShareThat2017; @treptePrivacyCalculusContextualized2020].
 How large are the effects of external popularity cues such as like and dislike buttons compared to the internal weighing of pros and cons?
-And how easily can the privacy calculus be manipulated by popularity cues?
+And how easily can the mechanisms of the privacy calculus be affected by means of popularity cues?
+
+In conclusion, in this paper we contribute to communication theory by means of (a) replication, (b) falsification, (c) extending the range of existing theory, (d) elucidating mechanisms, and (e) theory comparison [@deandreaIncreasingClarityWhere2017].
 
@@
 When are we willing to engage in a conversation?
-It builds on the calculus of behavior [@lauferPrivacyConceptSocial1977] and states that people are weighing risks and benefits before engaging in communication.
+It builds on the calculus of behavior [@lauferPrivacyConceptSocial1977] and states that people are weighing risks and benefits before actively communicating.
 Communication is closely related to privacy, which is defined as a "voluntary and temporary withdrawal of a person from the general society" [@westinPrivacyFreedom1967, p. 7].
 People regulate their privacy by deciding what and what not to communicate [@dienlinPrivacyProcessModel2014].
+Communication is therefore also closely related to self-disclosure.
+Just as it is impossible to not communicate, communication inherently promotes self-disclosure. 
+In a recent study, communication quantity and the frequency of expressing one's political opinion was almost indistinguishable (_r_ = .91; AUTHORS).
+Next to breadth and depth, communication quantity is hence often considered a central dimension of self-disclosure [@omarzuDisclosureDecisionModel2000].
+
 Sharing information carries risks, as recipients may reuse it in different contexts, potentially harming the original sender [@masurBehavioralContagionSocial2021].
-As a result, people who aim to avoid risks should be included to share less information, especially in online contexts where audiences are much larger [@vitakImpactContextCollapse2012].
+As a result, people who aim to avoid risks should be inclined to share less information, especially in online contexts where audiences are much larger [@vitakImpactContextCollapse2012].
 Indeed, empirical research confirms that people with higher privacy needs and privacy concerns are less likely to communicate online [@krasnovaOnlineSocialNetworks2010; @masurTransformativeNotHow2021; @masurUnderstandingEffectsConceptual2023].
@@
 
-Outweighing concerns, the most relevant drivers of online communication are expected gratifications [@dienlinExtendedPrivacyCalculus2016; @bolUnderstandingEffectsPersonalization2018; @kezerGettingPrivacyCalculus2022].
-People are happy to trade in parts of their privacy when they can receive something more valuable in return [@lauferPrivacyConceptSocial1977].
+Even outweighing concerns, the most relevant drivers of online communication are expected gratifications [@dienlinExtendedPrivacyCalculus2016; @bolUnderstandingEffectsPersonalization2018; @kezerGettingPrivacyCalculus2022].
+On average, people are happy to trade in parts of their privacy to receive something more valuable in return [@lauferPrivacyConceptSocial1977].
 In online communication, the most important benefits include social support, social capital, entertainment, information-seeking, and self-presentation [@dhirUnderstandingRelationshipIntensity2017; @ellisonBenefitsFacebookFriends2007; @krasnovaOnlineSocialNetworks2010; @whitingWhyPeopleUse2013].
@@
 Only observing that privacy concerns or expected gratifications and communication online are related does not prove that an explicit weighing process took place [@knijnenburgDeathPrivacyCalculus2017].
-Instead, we need to analyze if, and if so by how much, people actively deliberate about their privacy, and whether doing so influences their willingness to communicate.
+Instead, we need to analyze if, and if so by how much, people actively deliberate about their privacy by comparing benefits and risks, and whether doing so influences their willingness to communicate.
 Self-disclosure theory [@omarzuDisclosureDecisionModel2000;  @altmanPrivacyConceptualAnalysis1976] suggests that if the benefits of communication are attractive, deciding whether or not to communicate is a "conscious and deliberative process"  [@omarzuDisclosureDecisionModel2000, p.
@@
 1303].
-Although human behavior is considered partly irrational, bounded rationality does not state that it is completely irrational [@gigerenzerBoundedRationalityAdaptive2002].
-Rationality can hence be understood to exist on a continuum. 
-In the context of online privacy, rationality is impeded by information asymmetries, presence bias, intangibility, illusory control, or herding [@acquistiSecretsLikesDrive2020].
-It follows that to provide a more complete picture, additional factors next to gratifications and concerns should also explain communication.
-Factors less focused on rationality, but more on socio-psychological aspects.
+It is important to emphasize that although human behavior is considered _partly_ irrational, bounded rationality does not state that it is _completely_ irrational [@gigerenzerBoundedRationalityAdaptive2002].
+Instead, rationality needs to be understood as a continuum. 
+And in the context of online privacy, rationality is impeded by information asymmetries, presence bias, intangibility, illusory control, or herding [@acquistiSecretsLikesDrive2020].
+It follows that to provide a more complete picture, additional factors less focused on rationality but more on socio-psychological aspects should also explain communication.
 
-The two factors perhaps most important when it comes to understanding online communication are self-efficacy and trust [@hossainICTEnabledVirtual2004; @metzgerPrivacyTrustDisclosure2004].
-Privacy violations create psychological distress [@ledbetterParentchildPrivacyBoundary2019], experiencing online contexts as a safe space that users can sufficiently control is important for engaging in online communication.
+Two central factors that help us understand online communication are self-efficacy and trust [@hossainICTEnabledVirtual2004; @metzgerPrivacyTrustDisclosure2004].
+Privacy violations create psychological distress [@ledbetterParentchildPrivacyBoundary2019].
+Experiencing online contexts as a safe space that users can sufficiently control is important for engaging in online communication. 
 If users are more familiar, experienced, and knowledgeable in a given online context, they are more likely to navigate that online contexts successfully and to communicate actively [@baruhOnlinePrivacyConcerns2017; @kramerMasteringChallengeBalancing2020; @parkDigitalLiteracyPrivacy2013a].
 People with more privacy self-efficacy engage more successfully in self-withdrawal [@dienlinExtendedPrivacyCalculus2016] and protective online behavior [@boermanExploringMotivationsOnline2021a; @vanooijenPrivacyCynicismIts2022].
-Hence, if users possess more self-efficacy to participate, they should also communicate more, and to more fully capture online behavior self-efficacy should hence be included.
+Hence, if users possess more self-efficacy to participate, they should also communicate more.
 
@@
 In all situations where people lack experience, control, or competence, a central variable to understand behavior is trust [@gefenTrustTAMOnline2003].
-Especially in online contexts, trust plays a key role [@metzgerPrivacyTrustDisclosure2004; @metzgerEffectsSiteVendor2006a].
+Trust plays a key role especially in online contexts [@metzgerPrivacyTrustDisclosure2004; @metzgerEffectsSiteVendor2006a].
 Users often cannot control the environment or the way their information is handled [@acquistiSecretsLikesDrive2020; @braunlichLinkingLooseEnds2020].
@@
 One of the central tools to afford and govern online behavior are popularity cues such as like and dislike buttons [@stsiampkouskayaNotExperimentalStudy2023].
-Popularity cues have been shown to affect behavior [@kramerMasteringChallengeBalancing2020; @masurBehavioralContagionSocial2021; @treptePrivacyCalculusContextualized2020]:
-Online comments that already have several dislikes are more likely to receive further dislikes [@muchnikSocialInfluenceBias2013]. 
+Popularity cues have been shown to affect behavior [@kramerMasteringChallengeBalancing2020; @masurBehavioralContagionSocial2021; @treptePrivacyCalculusContextualized2020].
+For example, online comments that already have several dislikes are more likely to receive further dislikes [@muchnikSocialInfluenceBias2013]. 
 When users disagree with a post, they are more likely to click on a button labeled _respect_ compared to a button labeled _like_ [@stroudRecommendRespectAltering2017].
@@
 They emphasize that it is not the _objective features_ that determine behavior, but rather our _subjective perceptions_ [@gibsonEcologicalApproachVisual2015].
-Popularity cues such as like and dislike buttons, which are of primary interest in this study, are understood as "paralinguistic digital affordances" [@carrPredictingThresholdPerceived2018, p. 142].
-
-```{r model, fig.cap="Overview of analyzed model.", fig.align='center', out.width=".8\\textwidth"}
-# knitr::include_graphics("figures/design/model_simplified.pdf")
-knitr::include_graphics("figures/design/model_simplified.png")
-```
+Popularity cues such as like and dislike buttons, which are of primary interest in this study, are understood as "paralinguistic digital affordances" [@carrPredictingThresholdPerceived2018, p.
+142], lowering thresholds to partake in online communication.
 
@@
 Receiving a like online is similar to receiving a compliment offline [@carrPredictingThresholdPerceived2018; @sumnerFunctionalApproachFacebook2017].
-Like-buttons afford and emphasize a _gain frame_ [@rosoffHeuristicsBiasesCyber2013].
+Like buttons afford and emphasize a _gain frame_ [@rosoffHeuristicsBiasesCyber2013].
 These gains can be garnered only through active participation. 
-In situations where people can gain immediate positive outcomes, concerns and risks that are more vague and in the future often become less relevant [@ainslieHyperbolicDiscounting1992].
+In situations where people can gain immediate positive outcomes, concerns and risks that are more vague and in the future often become less relevant [presence bias, @ainslieHyperbolicDiscounting1992].
 Because like buttons emphasize positive outcomes, it is likely that concerns decrease. 
 In situations where there is more to win, people might also more actively deliberate about whether or not to communicate.
+
 Dislikes, instead, represent a punishment, introducing a _loss frame_. 
-Websites featuring both like _and_ dislike buttons should therefore be more ambivalent compared to websites without popularity cues.
+Websites featuring both like _and_ dislike buttons should therefore be more ambivalent compared to websites without popularity cues, fostering privacy deliberation.
 Privacy concerns should not be reduced anymore:
-People who are more concerned about their privacy are also more shy and risk averse [@dienlinPsychologyPrivacyAnalyzing2017].
+People who need more privacy are also more shy and risk averse [@dienlinWhoNeedsPrivacy2024].
 Implementing the dislike button might therefore increase privacy concerns, canceling out the positive effects of the like button.
+At the same time, communication and benefits might still be increased compared to a website without like and dislikes buttons, as online benefits are often considered to outweigh risks [positivity bias, @schreursExposurePositivityBias2022].
 
@@
 
-For a simplified overview of the analyzed model, see Figure \@ref(fig:model).
+In conclusion, this leads to an updated and extended model of the privacy calculus, in which the affordances of online contexts affect communication mediated via experienced privacy concerns, expected gratifications, privacy deliberation, self-efficacy, and trust.
+For an overview of the theoretical model, see Figure \@ref(fig:model).
+
+```{r model, fig.cap="Overview of the extended privacy calculus model.", fig.align='center', out.width=".8\\textwidth"}
+# knitr::include_graphics("figures/design/model_simplified.pdf")
+knitr::include_graphics("figures/design/model_simplified.png")
+```
 
@@
 As incentive, participants were awarded digital points, to receive special offers from online retailers. 
-Participants had to be above the age of 18 and had to live in Germany. 
+Participants had to be over 18 years old and reside in Germany.
 In a first step, the company sent its panel members an invitation to participate in the study. 
-In this invitation, panel members were asked to participate in a study analyzing the current threat posed by terrorist attacks in Germany.
+In this invitation, panel members were asked to participate in a study analyzing the current threat posed by terrorist attacks.
 Members who agreed to participate were sent the first questionnaire (_T1_).
@@
     select(-alpha) %>% 
+    filter(rownames(.) != "Gratifications specific") %>% 
     rename(`p-value` = pvalue) %>% 
@@
 
-Two types of gratifications were collected.
 _General gratifications_ were measured with five items based on @sunLocationInformationDisclosure2015.
 One example item was "Using the participation platform has paid off for me". 
-Based on @schererGratifikationMinuteZeitnahe2002, _specific gratifications_ were measured on five dimensions with three items each. 
-Example items were: "Using the participation platform made it possible for me to" ...
-"learn things I would not have noticed otherwise" (information), "react to a subject that is important to me" (relevance), "engage politically" (political participation), "try to improve society" (idealism), and "soothe my guilty consciences" (extrinsic benefits).
-The means for both dimensions were _m_ = `r facval_tab["Gratifications general", "m"]` (general gratifications) and _m_ = `r facval_tab["Gratifications specific", "m"]` (specific gratifications), which were above the scales' midpoint.
+The mean was _m_ = `r facval_tab["Gratifications", "m"]`, which was above the scale's midpoint.
 This shows that on average people considered the website to be beneficial.
+For exploratory analyses, we also collected a scale measuring specific gratifications, not included here.
 
@@
 For example, people who were more concerned about their privacy disclosed less information (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "pri_con" & rhs == "Words_log") %>% select(std.all) %>%  my_round("std_txt")`).
-Specific gratifications predicted communication better than general gratifications (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_spec" & rhs == "Words_log") %>% select(std.all) %>%  my_round("std_txt")` vs.
-_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_gen" & rhs == "Words_log") %>% select(std.all) %>%  my_round("std_txt")`).
 The mean of privacy deliberation was _m_ = `r des_pridel$m %>% round(2)`. 
@@
 
-The bivariate results showed three large correlations: 
-specific trust and general gratifications (_r_ = `r d_fs %>% select("Trust\nspecific", "Gratifications\ngeneral") %>% cor %>% .[2, 1] %>% my_round("std")`), 
-privacy concerns and privacy deliberation (_r_ = `r d_fs %>% select("Privacy\nconcerns", "Privacy\ndeliberation") %>% cor %>% .[2, 1] %>% my_round("std")`),
-and specific gratifications and self-efficacy (_r_ = `r d_fs %>% select("Gratifications\nspecific", "Self-\nefficacy") %>% cor %>% .[2, 1] %>% my_round("std")`). 
+The bivariate results showed two large correlations: 
+specific trust and gratifications (_r_ = `r d_fs %>% select("Trust\nspecific", "Gratifications") %>% cor %>% .[2, 1] %>% my_round("std")`), and
+privacy concerns and privacy deliberation (_r_ = `r d_fs %>% select("Privacy\nconcerns", "Privacy\ndeliberation") %>% cor %>% .[2, 1] %>% my_round("std")`). 
 As all six variables were later analyzed within a single multiple regression, problems of multicollinearity might occur.
@@
 The model fit the data okay, `r fit_txt(fit_prereg, scaled = TRUE)`. 
-Regarding H1, results showed that gratifications did not predict communication (`r coeffs_txt(fit_prereg, "a1", one_sided=T)`; one-sided). 
-With regard to H2, privacy concerns did not significantly predict communication (`r coeffs_txt(fit_prereg, "b1", one_sided=T)`; one-sided). 
+With regard to H1, privacy concerns did not significantly predict communication (`r coeffs_txt(fit_prereg, "b1", one_sided=T)`; one-sided). 
+Regarding H2, results showed that gratifications did not predict communication (`r coeffs_txt(fit_prereg, "a1", one_sided=T)`; one-sided). 
 RQ1 similarly revealed that privacy deliberation did not predict communication (`r coeffs_txt(fit_prereg, "c1")`; two-sided). 
@@
 The results showed that the popularity cues had no effects on communication and on the privacy calculus variables.
+
 For an illustration, see Figure \@ref(fig:popularitycues). 
@@
 
-```{r popularitycues, fig.cap="Distributions and means with 95% CIs of the model-predicted values for each variable, separated for the three websites.
+```{r popularitycues, fig.cap="Distributions and means with 95\\% CIs of the model-predicted values for each variable, separated for the three websites.
 Control: Website without buttons.
@@
 Hypotheses 1, 2, 3, and 4 were all confirmed:
+If participants were more concerned about their privacy, they communicated less: 
+With each one-point increase in privacy concerns, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(Estimate) %>% round(0) %>% abs()` words less (95% HDI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(UL) %>% round(0)`).
 If participants expected more gratifications from participation, they communicated more actively: 
 If their expected gratifications increased by one point, on average they also wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(Estimate) %>% round(0)` words more (95% HDI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Expected gratifications") %>%  select(UL) %>% round(0)`).
-If participants were more concerned about their privacy, they communicated less: 
-With each one-point increase in privacy concerns, on average they wrote `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(Estimate) %>% round(0) %>% abs()` words less (95% HDI: `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(LL) %>% round(0)`, `r tab_slopes %>% filter(Outcome == "words" & Predictor == "Privacy concerns") %>%  select(UL) %>% round(0)`).
 If participants felt more self-efficacious, they communicated much more:
@@
           , font_size = "footnotesize"
-          , caption = "Unstandardized effects of the privacy calculus variables and the popularity cues on communication. Credibility intervals excluding zero are considered significant."
+          , caption = "Unstandardized average marginal effects of the privacy calculus variables and the popularity cues on communication.
+Credibility intervals excluding zero are considered significant."
           , note = "HDI = highest density interval, LL = lower level; UL = upper level. Reported are average marginal effects."
-          # , align = c("m{10cm}", rep("r", 3)) # use this for compiling pdfs
+          , align = c("m{10cm}", rep("r", 3)) # use this for compiling pdfs
           # , align = c("l", rep("r", 3)) # use this for compiling htmls
@@
 Results showed that this was not the case. 
-The popularity cues only affected behavior, but not the predictors of the privacy calculus model (see [online companion website](https://XMtRa.github.io/like_dislike)).
+The popularity cues only affected behavior but not the predictors of the privacy calculus model (see [online companion website](https://XMtRa.github.io/like_dislike)).
 The results suggest that the effect was either direct or mediated by other variables not included here [@coenenIndirectEffectOmitted2022].
@@
 
-This study analyzed whether the privacy calculus can be replicated with behavioral data in an authentic setting; if the model needs to be extended theoretically; and whether like and dislike buttons affect online communication and the privacy calculus.
+This study analyzed three questions: Can the privacy calculus can be replicated with behavioral data in an authentic setting?
+Should the privacy calculus model be extended theoretically?
+Do like and dislike buttons affect online communication and the privacy calculus?
 To this end, a preregistered field experiment was conducted, which lasted one week.
@@
 Although more rational aspects such as costs and benefits influence behavior, behavior is also determined by more socio-psychological variables such as trust and self-efficacy.
-The findings are also aligned with the technology acceptance model, which states that online behavior is most strongly determined by usefulness and ease of use [@venkateshUserAcceptanceInformation2003]---two variables closely related to gratifications and self-efficacy.
+The findings are therefore closely aligned with existing theory. 
+For example, the technology acceptance model states that online behavior is most strongly determined by usefulness and ease of use [@venkateshUserAcceptanceInformation2003]---two variables closely related to gratifications and self-efficacy.
 
@@
 The results showed that only one third of all participants agreed to have actively weighed the benefits and risks before communicating on the platform.
-This figure is comparatively low.
-Even in new online contexts, the majority of users does not seem to actively deliberate about their online communication, suggesting that online use is to large extents implicit [@acquistiSecretsLikesDrive2020].
+This figure seems comparatively low.
+Even in new online contexts, the majority of users does not actively deliberate about their online communication, suggesting that online use is to large extents implicit [@acquistiSecretsLikesDrive2020].
 
 Interestingly, and perhaps also somewhat surprisingly, privacy deliberation and privacy concerns were strongly correlated (_r_ = .61). 
-If we are concerned, we also think and deliberate more about our privacy. 
-And if we are not concerned, we do not deliberate.
+If we are concerned we also think and deliberate more actively about our privacy. 
+And if we are not concerned we do not deliberate.
 This finding can be aligned with decision theory [@elsbachEffectsMoodIndividuals1999]:
@@
 This was an unexpected and interesting finding.
-It suggests that negative feedback, or even only risks of negative feedback, stifles communication. 
+It suggests that negative feedback, or perhaps even only risks of negative feedback, can stifle communication. 
 The effect was strong: Implementing both like and dislikes cues led to a `r effect_lkdlk_prcnt %>% as.integer()`% decrease in number of written words.
@@
 The main implications and results discussed above rest on exploratory analyses not registered a priori.
-Exploratory analyses are part of the research process, compatible with preregistration, and important for scientific progress [@dienlinAgendaOpenScience2021].
+Exploratory analyses are part of the research process, compatible with preregistration, and important for scientific progress.
 The updated analyses represent and document a learning process, which arguably led to an improved analysis.
